### 2021-02-15 text/draft.tex
tex structure

Machine indexing of institutional repositories: indexing Edoc with Annif
and BARTOC FAST as proof of concept

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{outline}{%
\subsection{Outline}\label{outline}}

\hypertarget{method}{%
\subsection{Method}\label{method}}

!! Say something to the effect that all data and code are available on
GitHub.

\hypertarget{tools-and-configuration}{%
\subsection{Tools and configuration}\label{tools-and-configuration}}

\hypertarget{openrefine}{%
\subsubsection{OpenRefine}\label{openrefine}}

For data refinement I use OpenRefine version 3.4.1
(https://openrefine.org/). Data manipulation in OpenRefine is tracked:
the manipulation history of some data can be exported as JSON file and
then reproduced (on the same data on a different machine or on different
data) by loading said file. I will supply a corresponding manipulation
history whenever appropriate. Note that when using OpenRefine with
larger files (and there are many such files in this project), the memory
allocation to OpenRefine must be manually increased (see
https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation
for details).

\hypertarget{prototype}{%
\section{Prototype}\label{prototype}}

In this chapter, the prototype for a machine indexing of Edoc is
presented. The focus is primarily on practical implementation although
care is taken to spell out design decisions in as much detail as is
needed.

\hypertarget{aim}{%
\subsection{Aim}\label{aim}}

Let us start by stating the aim of the prototype. From a functional
perspective, the prototype takes a subset of the data from Edoc as input
and provides index terms for each item in this subset as output. In
order to fulfill this aim we can distinguish a number of steps that need
to be taken:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Understand the Edoc data.\\
\item
  Select and construct a sample data set.
\item
  Use Annif to index the items in the sample data set.
\item
  Construct a gold standard from the keywords.
\item
  Assess the quality of the output based on the gold standard.
\end{enumerate}

In the sections below, these steps will be discussed in detail.

\hypertarget{edoc-data}{%
\subsection{Edoc data}\label{edoc-data}}

\hypertarget{edoc}{%
\subsubsection{Edoc}\label{edoc}}

Edoc is the institutional repository of the University of Basel. It was
conceived in 2009 as repository for electronic dissertations and grew in
scope when the University of Basel adapted its first open access policy
in 2013. As per today Edoc contains roughly 68'000 items.

Edoc runs on the EPrints 3 document management system
(https://github.com/eprints/eprints).\\
!! Add technical description of Edoc.\\
!! Perhaps add description of how files are added to Edoc, see PDF in
\texttt{/todo}.

\hypertarget{data-extraction}{%
\subsubsection{Data extraction}\label{data-extraction}}

Even though Edoc is a public server, its database does not have a
web-ready API. In addition, since Edoc is a production server, its
underlying database cannot be used directly on pain of disturbing the
provided services. The data hence needs to be extracted from Edoc in
order to work with it. This could for example be achieved by cloning the
database of the server and running it on a local machine. However, this
route was not available due to the limited resources of the responsible
co-workers. I thus employed a workaround: Edoc has a built-in advanced
search tool where the results can be exported. Even though it is not
possible to extract all database items by default, only one of the many
available search fields has to be filled in. The complete database can
hence be extracted by only filling in the \texttt{Date} field and using
a sufficiently permissive time period such as 1940 to 2020 since the
oldest record in the database was published in 1942. On January 21 2021,
this query yielded 68'345 results. These results were then exported as a
326 MB JSON file called \texttt{1942-2020.json}. \texttt{1942-2020.json}
has two drawbacks. First, the maximum file size on GitHub is 100 MB. And
second, \texttt{1942-2020.json} is too big to be handled by standard
editors requiring special editors such as Oxygen. For these reasons
\texttt{1942-2020.json} was split into smaller files that are easier
handled and can be uploaded to GitHub. For this
\texttt{\_Utility.split\_json} was used yielding 14 files of size 20 MB
or less containing 5000 or fewer entries each. These files are called
\texttt{raw\_master\_x-y.json} (where x and y indicate the entries as
given by \texttt{1942-2020.json}) and saved under \texttt{/edoc/raw}.

\hypertarget{data-description-and-analysis}{%
\subsubsection{Data description and
analysis}\label{data-description-and-analysis}}

!! Explain the Edoc data fields. Say perhaps something about the
granularity of the relevant fields. Say something about how the fields
are filled in (and by whom).

\hypertarget{sample-data-set}{%
\subsection{Sample data set}\label{sample-data-set}}

In this section, I will explain how the sample data set is selected and
constructed. ``Selection'' means the task of specifying a subset of the
Edoc data and ``construction'' means the task of implementing this
selection.

\hypertarget{selection}{%
\subsubsection{Selection}\label{selection}}

There are a number of constraints for selecting the sample data set
pertaining to an items's text, evaluability and the data set's scope.

The first constraint stems from Annif, the machine indexing framework
that will be used. Put simply, machine indexing assigns index terms to a
text based on training data. The training data consists of a set of
texts, a vocabulary, and function from vocabulary to texts. In this
context we mean by ``text'' a sequence of words in a natural language
and by ``vocabulary'' a set of words. Intuitively, the training data
consists of pairs of text and subject terms that meet some standard. The
training data and the vocabulary are already supplied by Annif, we only
need to provide a text for each item that we want to be assigned index
terms. Therefore, we only select items with text.

The second constraint is that we must be able to evaluate the quality of
the index terms assigned by Annif to any item in the sample data set.

The third and final constraint takes into account the possibility of
having to extend the prototype to the complete Edoc data. On the one
hand, the sample data set should be small enough to allow for easy
handling and rapid iteration. On the other hand, the sample data set
should not be trivial but reflect the quirks and inadequacies of the
complete dataset. In other words, we are looking for an abstraction
rather than an idealization in the sense of @Stokhof.2011.

\hypertarget{construction}{%
\subsubsection{Construction}\label{construction}}

The first constraint is that each item in the sample data set needs to
have a text. Intuitively, this text could consist of a title, an
abstract, or even a full text, or any combination of the above. Similar
to manual indexing, having more information (that is, longer texts)
usually implies a higher indexing quality in machine indexing. However,
this assumption needs to be confirmed empirically for the given machine
indexing framework and data set. If indeed confirmed, it might be
advisable only to index items that have a certain minimal text length.
Therefore, in order to construct the sample data set, we require each
item to have a non-empty value in the data fields \texttt{title},
\texttt{abstract}, and \texttt{id\_number} as proxy to retrieve a full
text remotely. Note that even more context could be provided by taking
into account other data fields such as \texttt{type},
\texttt{publication} or \texttt{department}. Especially the latter might
be valuable when disambiguating homonymous or polysemous words. For
example, consider the item
\texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
``Blacking Out''. Without further context, this title could refer
(amongst others) to a physiological phenomenon, a sudden loss of
electricity, or a measure taken in wartime. Knowing that the item was
published by a researcher employed by the Faculty of Business and
Economics (and not, say, by the Faculty of Medicine) gives us reason to
exclude the first meaning. However, this idea cannot be implemented with
the out of the box instance of Annif employed in this chapter (see
\protect\hyperlink{machine-indexing}{subsection ``Machine indexing''}).

The second constraint is that the index terms assigned to each item in
the sample data set must be assessable. How the assessment is conducted
in detail is discussed in \protect\hyperlink{assessment}{section
``Assessment''}. For now, it is sufficient to say that we require a
standard against which we can evaluate the assigned index terms. By
``standard'' I mean that given a vocabulary of index terms and our
sample data set, for every item in the sample data set, there is an
approved subset of the vocabulary. The production of a standard from
scratch is of course is very costly since a person, usually highly
skilled in a certain academic domain, must assign and/or approve each
item's index terms (!!source). For this reason we try to avoid having to
produce a standard. One way of doing so is by requiring items in the
sample data set to have non-empty \texttt{keywords} data field. The
caveats of this approach are discussed in
\protect\hyperlink{assessment}{section ``Assessment''}.

Taking into account the third constraint simply means that we do not
employ any further restrictions. We can hence construct the sample data
set by choosing exactly those items from \texttt{/edoc/raw} which have
non-empty data fields \texttt{title}, \texttt{abstract},
\texttt{id\_number}, and \texttt{keywords}. We do so by calling
\texttt{\_Data.select\_from\_file} iteratively for all files in
\texttt{/edoc/raw}. The resulting file is saved in
\texttt{/edoc/selected} as \texttt{selected\_master.json}.

\hypertarget{analysis}{%
\subsubsection{Analysis}\label{analysis}}

Of the 68'345 items in \texttt{/edoc/raw}, all have a title (non-empty
\texttt{title} data field), a little more than half of the items have an
abstract (37'381 items with non-empty \texttt{abstract} data field),
roughly half of the items have an ID (35'355 items with non-empty
\texttt{id\_number} data field),\footnote{Note that when using the facet
  by blank on \texttt{id\_number} in OpenRefine, there are 57'153
  matches; this is due to the fact that many items with an ID such as
  DOI have secondary or tertiary IDs such as ISI or PMID.} and less than
10\% of the items have keywords (6'660 items with non-empty
\texttt{keywords} data field). The sample data set as requires all the
above data fields to be non-empty;
\texttt{/edoc/sample/sample\_master.json} has 4'111 items and hence
constitutes 6\% of the raw data.

In order to determine how well the sample data set represents the raw
Edoc data, a one-sample chi-square test was conducted on each selection
data field {[}see @Parke.2013, chapter 1{]}. The results indicate that
the sample data proportions of items are significantly different from
the raw Edoc data per department (see Figure 1 for more details).

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data (\(n\) = 68'345) per department. Data field
\texttt{abstract}: \(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data
field \texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285,
\(p < 0.001\); data field \texttt{keywords}: \(\chi^2 (df=9) =\)
2'314.533, \(p < 0.001\). The data foundation is available at
\texttt{/edoc/analysis} and the chi-square statistic can be calculated
by calling \texttt{\_Analysis.chi\_square\_fit}.}
\end{figure}

The sample data set is hence not representative of the raw Edoc data.
This is not surprising since its construction is strongly biased. This
bias has the effect that the sample data set is significantly skewed
towards English journal publications in the sciences, medicine and
economics from the 21st century (see Figure 2 for more details). The
upshot of this analysis is that the humanities are underrepresented in
the sample data set. Therefore, any results with respect to the quality
of machine indexing discussed below might not be applicable to the
humanities.

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276\$, \(p < 0.001\)) from the 21st (data
field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\))
century as compared to the raw Edoc data (\(n\) = 68'345). The data
foundation is available at \texttt{/edoc/analysis} and the chi-square
statistic can be calculated by calling
\texttt{\_Analysis.chi\_square\_fit}.}
\end{figure}

\hypertarget{machine-indexing}{%
\subsection{Machine indexing}\label{machine-indexing}}

\hypertarget{general-overview}{%
\subsubsection{General overview}\label{general-overview}}

!! Give an overview over machine indexing.

\hypertarget{annif}{%
\subsubsection{Annif}\label{annif}}

!! Given an intro to Annif. Explain that we are using the out of the box
version

\hypertarget{implementation}{%
\subsubsection{Implementation}\label{implementation}}

As explained above, for the prototype we will use the out

!! Explain how to implementation works.

In addition to the already used algorithms we should also try
https://ai.finto.fi/?locale=en

!! Somewhere here we talk about indexing based on title and/or abstract
and/or fulltext. Fulltext is not yet implemented. Some observations to
do so: - the link to the fulltext is constructed from the data fields
\texttt{offical\ url} and \texttt{documebts\ -\ main}, e.g.,
\texttt{https\ \ ://edoc.unibas.ch/79633/} + \texttt{1/} +
\texttt{2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}
to get
\texttt{https://edoc.unibas.ch/79633/1/2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}

\hypertarget{assessment}{%
\subsection{Assessment}\label{assessment}}

In this chapter I will construct three distinct gold standards in order
to assess the quality of machine indexing the sample data set with
Annif.\\
!! Say something about assessments of Annif that have already been
carried out.

\hypertarget{gold-standard}{%
\subsubsection{Gold standard}\label{gold-standard}}

The most common approach for assessing the output of machine indexing is
by systematically comparing it with a gold standard (sometimes also
referred to as model or reference). @Golub.2016 {[}p. 10{]} define a
gold standard as ``a collection in which each document is assigned a set
of subjects that is assumed to be complete and correct'' where
``\emph{complete} means that all subjects that should be assigned to a
document are in fact assigned, and \emph{correct} means that there are
no subjects assigned that are irrelevant to the content''. Put
inversely, if an item in the gold standard lacks subject terms
describing its content, the assignment is not complete; and if an item
in the gold standard has been assigned subject terms that are not
relevant to its content, the assignment is not correct.

A gold standard is usually the product of manual indexing by
``information experts, subject experts, or potential or real end users''
{[}@Golub.2016, p. 10{]}. This entails its own host of epistemic
problems relating to objectivity and consistency of the assigned subject
terms. Most importantly, however, the construction of a gold standard
from scratch is very expensive. It is therefore not an option for the
project at hand. Rather, I will construct what could be called
derivative gold standards by reusing indexing data that is already
available. Here we can distinguish two distinct kinds of derivative gold
standards: first, I will construct a derivative gold standard based on
the author keywords available in the sample data set; call this the
``native'' gold standard. Second, I will construct a derivative gold
standard based on indexing metadata available in repositories distinct
from Edoc; call this the ``foreign'' gold standard.

There are other methods for assessing machine indexing quality besides
comparison with a gold standard that are worth mentioning. These include
an evaluation in the context of indexing workflows {[}@Golub.2016, p.
13ff.{]}, the assessment of retrieval performance {[}@Golub.2016, p.
15-23.{]}, and so-called model free assessments {[}@Louis.2013{]}.

\hypertarget{extract-keywords}{%
\paragraph{Extract keywords}\label{extract-keywords}}

\hypertarget{clean-keywords}{%
\paragraph{Clean keywords}\label{clean-keywords}}

\hypertarget{frequency-analysis}{%
\paragraph{Frequency analysis}\label{frequency-analysis}}

\hypertarget{mapping-to-controlled-vocabularies}{%
\paragraph{Mapping to controlled
vocabularies}\label{mapping-to-controlled-vocabularies}}

\hypertarget{precision-recall-f1-score}{%
\subsubsection{Precision, recall,
F1-score}\label{precision-recall-f1-score}}

!! Discussion of metrics

\hypertarget{annif-versus-gold-standard}{%
\subsubsection{Annif versus gold
standard}\label{annif-versus-gold-standard}}

\hypertarget{yso}{%
\paragraph{YSO}\label{yso}}

\hypertarget{wikidata}{%
\paragraph{Wikidata}\label{wikidata}}

\hypertarget{annif-versus-mesh}{%
\subsubsection{Annif versus MeSH}\label{annif-versus-mesh}}

\hypertarget{digression-truth-conditions-for-indexing}{%
\subsubsection{Digression: truth-conditions for
indexing}\label{digression-truth-conditions-for-indexing}}

(Correspondence theory of indexing: subject term T fits text X iff text
X is about T) \#\#\# Targets !! Find out what I meant here.

\hypertarget{analysis-1}{%
\subsubsection{Analysis}\label{analysis-1}}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\hypertarget{outlook}{%
\section{Outlook}\label{outlook}}

\hypertarget{refinement}{%
\subsection{Refinement}\label{refinement}}

\hypertarget{implementation-strategy}{%
\subsection{Implementation strategy}\label{implementation-strategy}}

\hypertarget{other-use-cases}{%
\subsection{Other use cases}\label{other-use-cases}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{bibliography}{%
\section{Bibliography}\label{bibliography}}

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\begin{Shaded}
\begin{Highlighting}[numbers=left,,]
\KeywordTok{def}\NormalTok{ myfunction(var):}
  \CommentTok{""" Oh how awesome this is. """}
  \ControlFlowTok{pass}
\end{Highlighting}
\end{Shaded}

### 2021-02-15 text/main.tex
tex structure

--- 2021-02-15 text/draft.tex
@@
-Machine indexing of institutional repositories: indexing Edoc with Annif
-and BARTOC FAST as proof of concept
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\newenvironment{Shaded}{}{}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+% ORCID
+\usepackage{scalerel}
+\usepackage{tikz}
+\usetikzlibrary{svg.path}
+
+\definecolor{orcidlogocol}{HTML}{A6CE39}
+\tikzset{
+	orcidlogo/.pic={
+		\fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
+		\fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
+		svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
+		svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
+	}
+}
+
+\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
+				\begin{tikzpicture}[yscale=-1,transform shape]
+					\pic{orcidlogo};
+				\end{tikzpicture}
+			}{|}}}}
+
+\author{}
+\date{}
+
+\begin{document}
+
+\input{./titlepage/titlepage}
+\newpage
+
+\input{./abstract/abstract}
+\newpage
+
+{
+\setcounter{tocdepth}{3}
+\tableofcontents
+}
 
@@
 complete dataset. In other words, we are looking for an abstraction
-rather than an idealization in the sense of @Stokhof.2011.
+rather than an idealization in the sense of Stokhof and van Lambalgen
+(2011).
 
@@
 \texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
-``Blacking Out''. Without further context, this title could refer
+``Blacking Out.'' Without further context, this title could refer
 (amongst others) to a physiological phenomenon, a sudden loss of
@@
 Edoc data, a one-sample chi-square test was conducted on each selection
-data field {[}see @Parke.2013, chapter 1{]}. The results indicate that
-the sample data proportions of items are significantly different from
-the raw Edoc data per department (see Figure 1 for more details).
+data field (see Parke 2013, chap. 1). The results indicate that the
+sample data proportions of items are significantly different from the
+raw Edoc data per department (see Figure 1 for more details).
 
@@
 by systematically comparing it with a gold standard (sometimes also
-referred to as model or reference). @Golub.2016 {[}p. 10{]} define a
+referred to as model or reference). Golub et al. (2016, 10) define a
 gold standard as ``a collection in which each document is assigned a set
@@
 document are in fact assigned, and \emph{correct} means that there are
-no subjects assigned that are irrelevant to the content''. Put
+no subjects assigned that are irrelevant to the content.'' Put
 inversely, if an item in the gold standard lacks subject terms
@@
 ``information experts, subject experts, or potential or real end users''
-{[}@Golub.2016, p. 10{]}. This entails its own host of epistemic
-problems relating to objectivity and consistency of the assigned subject
-terms. Most importantly, however, the construction of a gold standard
-from scratch is very expensive. It is therefore not an option for the
-project at hand. Rather, I will construct what could be called
-derivative gold standards by reusing indexing data that is already
-available. Here we can distinguish two distinct kinds of derivative gold
-standards: first, I will construct a derivative gold standard based on
-the author keywords available in the sample data set; call this the
-``native'' gold standard. Second, I will construct a derivative gold
-standard based on indexing metadata available in repositories distinct
-from Edoc; call this the ``foreign'' gold standard.
+(Golub et al. 2016, 10). This entails its own host of epistemic problems
+relating to objectivity and consistency of the assigned subject terms.
+Most importantly, however, the construction of a gold standard from
+scratch is very expensive. It is therefore not an option for the project
+at hand. Rather, I will construct what could be called derivative gold
+standards by reusing indexing data that is already available. Here we
+can distinguish two distinct kinds of derivative gold standards: first,
+I will construct a derivative gold standard based on the author keywords
+available in the sample data set; call this the ``native'' gold
+standard. Second, I will construct a derivative gold standard based on
+indexing metadata available in repositories distinct from Edoc; call
+this the ``foreign'' gold standard.
 
@@
 comparison with a gold standard that are worth mentioning. These include
-an evaluation in the context of indexing workflows {[}@Golub.2016, p.
-13ff.{]}, the assessment of retrieval performance {[}@Golub.2016, p.
-15-23.{]}, and so-called model free assessments {[}@Louis.2013{]}.
+an evaluation in the context of indexing workflows (Golub et al. 2016,
+13ff.), the assessment of retrieval performance (Golub et al. 2016,
+15--23.), and so-called model free assessments (Louis and Nenkova 2013).
 
@@
 \end{Shaded}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Golub.2016}{}%
+Golub, Koraljka, Dagobert Soergel, George Buchanan, Douglas Tudhope,
+Marianne Lykke, and Debra Hiom. 2016. {``A Framework for Evaluating
+Automatic Indexing or Classification in the Context of Retrieval.''}
+\emph{Journal of the Association for Information Science and Technology}
+67 (1): 3--16. \url{https://doi.org/10.1002/asi.23600}.
+
+\leavevmode\hypertarget{ref-Louis.2013}{}%
+Louis, Annie, and Ani Nenkova. 2013. {``Automatically Assessing Machine
+Summary Content Without a Gold Standard.''} \emph{Computational
+Linguistics} 39 (2): 267--300.
+\url{https://doi.org/10.1162/COLI\%7B/textunderscore\%20\%7Da\%7B/textunderscore\%20\%7D00123}.
+
+\leavevmode\hypertarget{ref-Parke.2013}{}%
+Parke, Carol. 2013. \emph{Essential First Steps to Data Analysis:
+Scenario-Based Examples Using SPSS}. Thousand Oaks: {SAGE Publications}.
+\url{https://doi.org/10.4135/9781506335148}.
+
+\leavevmode\hypertarget{ref-Stokhof.2011}{}%
+Stokhof, Martin, and Michiel van Lambalgen. 2011. {``Abstractions and
+Idealisations: The Construction of Modern Linguistics.''}
+\emph{Theoretical Linguistics} 37 (1-2): 1--26.
+\url{https://doi.org/10.1515/thli.2011.001}.
+
+\end{CSLReferences}
+
+\end{document}

### 2021-02-15 text/abstract/abstract.tex
tex structure

\hypertarget{abstract}{%
	\section*{Abstract}\label{abstract}}

bla bla bla

### 2021-02-15 text/titlepage/titlepage.tex
tex structure

\newpage
%\sffamily
\thispagestyle{empty}
\large
\begin{center}
	\includegraphics[width=5cm]{./logo.png}\\[.5cm]
	Universität Zürich, Philosophische Fakultät\\[.25cm]
 	Zentralbibliothek Zürich, MAS Bibliotheks- und Informationswissenschaft\\[1cm]
	\hrule
	\vspace{2cm}
	\flushleft
	\textbf{\LARGE Machine indexing of institutional repositories: indexing Edoc with Annif as proof of concept}\\[2cm]
	\orcidicon{0000-0002-9337-4655} Dr.\ Maximilian G.\ Hindermann\\
	Spalentorweg 46, CH-4051 Basel\\
	+41 79 277 0612\\
	\href{mailto:maximilian.hindermann@gmail.com}{maximilian.hindermann@gmail.com}\\
	\vspace{1cm}
	\flushleft
	\orcidicon{0000-0003-1952-1933} Silke Bellanger, Referentin\\[.25cm]
	\orcidicon{0000-0002-0629-0446} Dr.\ Andreas Ledl, Ko-Referent\\
	%Prof.\ Marco J.\ Nathan\\[.25cm]
	%\begin{minipage}{.4\textwidth}
	%\end{minipage}
	\vfill
	\center
	1.\ April 2021
\end{center}
\normalfont
\normalsize

### 2021-02-16 text/draft.tex
tex structure

@@
 
-\hypertarget{assessment}{%
-\subsection{Assessment}\label{assessment}}
+\hypertarget{gold-standard}{%
+\subsection{Gold standard}\label{gold-standard}}
 
@@
 
-\hypertarget{gold-standard}{%
-\subsubsection{Gold standard}\label{gold-standard}}
+\hypertarget{definition}{%
+\subsubsection{Definition}\label{definition}}
 
@@
 by systematically comparing it with a gold standard (sometimes also
-referred to as model or reference). @Golub.2016 {[}p. 10{]} define a
+referred to as model or reference). Golub et al. (2016, 10) define a
 gold standard as ``a collection in which each document is assigned a set
-of subjects that is assumed to be complete and correct'' where
-``\emph{complete} means that all subjects that should be assigned to a
-document are in fact assigned, and \emph{correct} means that there are
-no subjects assigned that are irrelevant to the content''. Put
+of {[}subject terms{]} that is assumed to be complete and correct''
+where ``\emph{complete} means that all subjects that should be assigned
+to a document are in fact assigned, and \emph{correct} means that there
+are no subjects assigned that are irrelevant to the content.'' Put
 inversely, if an item in the gold standard lacks subject terms
@@
 comparison with a gold standard that are worth mentioning. These include
-an evaluation in the context of indexing workflows {[}@Golub.2016, p.
-13ff.{]}, the assessment of retrieval performance {[}@Golub.2016, p.
-15-23.{]}, and so-called model free assessments {[}@Louis.2013{]}.
+an evaluation in the context of indexing workflows (Golub et al. 2016,
+13ff.), the assessment of retrieval performance (Golub et al. 2016,
+15--23.), and so-called model free assessments (Louis and Nenkova 2013).
+
+\hypertarget{native-gold-standard}{%
+\subsubsection{Native gold standard}\label{native-gold-standard}}
+
+The construction of the native gold standard takes x steps:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Extract the keywords from the sample data set.\\
+\item
+  Clean the extracted keywords.
+\item
+  Reconcile the extracted keywords with\ldots{}
+\end{enumerate}
+
+The intended output of this transformation process is\ldots{}
+
+These steps are explained in more detail in what follows.
 
@@
 
+In a first step, the keywords must be extracted from the sample data set
+\texttt{/sample/sample\_master.json}. Recall that we mandated a
+non-empty \texttt{keywords} data field for an item to be selected from
+the raw Edoc data (see \protect\hyperlink{selection}{subsection
+``Selection''}). We can thus simply copy the information in the
+\texttt{keywords} data field on a per item basis. To do this, we call
+\texttt{\_Keywords.extract\_keywords} with the sample data set as
+argument and save the output as
+\texttt{keywords/keywords\_extracted.json} like so:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{keywords }\OperatorTok{=}\NormalTok{ \_Keywords.extract\_keywords(DIR }\OperatorTok{+} \StringTok{"/sample/sample\_master.json"}\NormalTok{)}
+\NormalTok{\_Utility.save\_json(keywords, DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
 \hypertarget{clean-keywords}{%
@@
 
-\hypertarget{frequency-analysis}{%
-\paragraph{Frequency analysis}\label{frequency-analysis}}
+In second step, a list of all single keywords must be created. In order
+to do so, let us consider now in more detail the exact information
+extracted from the \texttt{keywords} data fields as per
+\texttt{keywords/keywords\_extracted.json}. In Edoc, the
+\texttt{keywords} data field of an item is a non-mandatory free text
+field that is filled in by the user (usually one of the authors) who
+undertakes the data entry of an item to Edoc. Even though the Edoc user
+manual specifies that keywords must be separated by commas (Universität
+Basel, n.d., 8), this requirement is neither validated by the input mask
+nor by an administrator of Edoc. Furthermore, neither the manual nor the
+input mask provide a definition of the term ``keyword.'' A vocabulary or
+a list of vocabularies from which to choose the keywords is also
+lacking. Taken together, these observations are indicative of very
+heterogeneous data in the \texttt{keywords} data field. To wit, the
+items of \texttt{keywords/keywords\_extracted.json} are strings where
+single keywords are individuated by any symbols the user saw fit. So,
+for each item in \texttt{keywords/keywords\_extracted.json}, the user
+input must be parsed into single keywords.
 
-\hypertarget{mapping-to-controlled-vocabularies}{%
-\paragraph{Mapping to controlled
-vocabularies}\label{mapping-to-controlled-vocabularies}}
+Next the so parsed single keywords must be cleaned or normalized: we
+want the keywords to follow a uniform format thereby joining
+morphological duplicates such as ``Gene,'' ``gene,'' " gene``,''/gene``.
+Also, some keywords are in fact keyword chains, for
+example''Dendrites/metabolism/ultrastructure". Keyword chains must be
+broken into their component keywords and then parsed again. The reason
+for this is that Annif only assigns flat keywords and not keyword
+chains.
+
+\texttt{\_Keywords.clean\_keywords} is the implementation the parser and
+the recursive cleaner is implemented by
+\texttt{\_Keywords.clean\_keyword}. To create the desired list of clean
+keywords, saved as \texttt{keywords/keywords\_clean.json}, we call
+\texttt{\_Keywords.clean\_keywords} with the extracted keywords as
+argument:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
+\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \_Keywords.clean\_keywords(keywords\_extracted)}
+\NormalTok{\_Utility.save\_json(keywords\_clean, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{analysis-1}{%
+\paragraph{Analysis}\label{analysis-1}}
+
+!! Frequency
+
+\hypertarget{reconciliation}{%
+\paragraph{Reconciliation}\label{reconciliation}}
+
+!! Mapping to controlled vocabularies; explain why this is necessary.
+
+!! Does the OpenRefine project still exist? Export the list of changes!
+
+\hypertarget{foreign-gold-standard}{%
+\subsubsection{Foreign gold standard}\label{foreign-gold-standard}}
+
+!! Todo: - Explain MeSH\\
+- Explain how to get MeSH for subset of sample data set
+
+\hypertarget{assessment}{%
+\subsection{Assessment}\label{assessment}}
 
@@
 
-\hypertarget{annif-versus-gold-standard}{%
-\subsubsection{Annif versus gold
-standard}\label{annif-versus-gold-standard}}
+\hypertarget{annif-versus-native-gold-standard}{%
+\subsubsection{Annif versus native gold
+standard}\label{annif-versus-native-gold-standard}}
 
@@
 
-\hypertarget{annif-versus-mesh}{%
-\subsubsection{Annif versus MeSH}\label{annif-versus-mesh}}
+\hypertarget{annif-versus-foreign-gold-standard}{%
+\subsubsection{Annif versus foreign gold
+standard}\label{annif-versus-foreign-gold-standard}}
 
@@
 
-\hypertarget{analysis-1}{%
-\subsubsection{Analysis}\label{analysis-1}}
+\hypertarget{analysis-2}{%
+\subsubsection{Analysis}\label{analysis-2}}
 
@@
 
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
 \hypertarget{bibliography}{%
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Golub.2016}{}%
+Golub, Koraljka, Dagobert Soergel, George Buchanan, Douglas Tudhope,
+Marianne Lykke, and Debra Hiom. 2016. {``A Framework for Evaluating
+Automatic Indexing or Classification in the Context of Retrieval.''}
+\emph{Journal of the Association for Information Science and Technology}
+67 (1): 3--16. \url{https://doi.org/10.1002/asi.23600}.
 
-\begin{Shaded}
-\begin{Highlighting}[numbers=left,,]
-\KeywordTok{def}\NormalTok{ myfunction(var):}
-  \CommentTok{""" Oh how awesome this is. """}
-  \ControlFlowTok{pass}
-\end{Highlighting}
-\end{Shaded}
+\leavevmode\hypertarget{ref-Louis.2013}{}%
+Louis, Annie, and Ani Nenkova. 2013. {``Automatically Assessing Machine
+Summary Content Without a Gold Standard.''} \emph{Computational
+Linguistics} 39 (2): 267--300.
+\url{https://doi.org/10.1162/COLI\%7B/textunderscore\%20\%7Da\%7B/textunderscore\%20\%7D00123}.
+
+\leavevmode\hypertarget{ref-Parke.2013}{}%
+Parke, Carol. 2013. \emph{Essential First Steps to Data Analysis:
+Scenario-Based Examples Using SPSS}. Thousand Oaks: {SAGE Publications}.
+\url{https://doi.org/10.4135/9781506335148}.
+
+\leavevmode\hypertarget{ref-Stokhof.2011}{}%
+Stokhof, Martin, and Michiel van Lambalgen. 2011. {``Abstractions and
+Idealisations: The Construction of Modern Linguistics.''}
+\emph{Theoretical Linguistics} 37 (1-2): 1--26.
+\url{https://doi.org/10.1515/thli.2011.001}.
+
+\leavevmode\hypertarget{ref-UniversitatBasel.2021}{}%
+Universität Basel. n.d. {``Research Database of the University of Basel
+User Manual.''} Edited by Universität Basel.
+
+\end{CSLReferences}

### 2021-02-16 text/main.tex
tex structure

@@
 }
+\newpage
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-\hypertarget{outline}{%
-\subsection{Outline}\label{outline}}
-
-\hypertarget{method}{%
-\subsection{Method}\label{method}}
-
-!! Say something to the effect that all data and code are available on
-GitHub.
-
-\hypertarget{tools-and-configuration}{%
-\subsection{Tools and configuration}\label{tools-and-configuration}}
-
-\hypertarget{openrefine}{%
-\subsubsection{OpenRefine}\label{openrefine}}
-
-For data refinement I use OpenRefine version 3.4.1
-(https://openrefine.org/). Data manipulation in OpenRefine is tracked:
-the manipulation history of some data can be exported as JSON file and
-then reproduced (on the same data on a different machine or on different
-data) by loading said file. I will supply a corresponding manipulation
-history whenever appropriate. Note that when using OpenRefine with
-larger files (and there are many such files in this project), the memory
-allocation to OpenRefine must be manually increased (see
-https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation
-for details).
-
-\hypertarget{prototype}{%
-\section{Prototype}\label{prototype}}
-
-In this chapter, the prototype for a machine indexing of Edoc is
-presented. The focus is primarily on practical implementation although
-care is taken to spell out design decisions in as much detail as is
-needed.
-
-\hypertarget{aim}{%
-\subsection{Aim}\label{aim}}
-
-Let us start by stating the aim of the prototype. From a functional
-perspective, the prototype takes a subset of the data from Edoc as input
-and provides index terms for each item in this subset as output. In
-order to fulfill this aim we can distinguish a number of steps that need
-to be taken:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Understand the Edoc data.\\
-\item
-  Select and construct a sample data set.
-\item
-  Use Annif to index the items in the sample data set.
-\item
-  Construct a gold standard from the keywords.
-\item
-  Assess the quality of the output based on the gold standard.
-\end{enumerate}
-
-In the sections below, these steps will be discussed in detail.
-
-\hypertarget{edoc-data}{%
-\subsection{Edoc data}\label{edoc-data}}
-
-\hypertarget{edoc}{%
-\subsubsection{Edoc}\label{edoc}}
-
-Edoc is the institutional repository of the University of Basel. It was
-conceived in 2009 as repository for electronic dissertations and grew in
-scope when the University of Basel adapted its first open access policy
-in 2013. As per today Edoc contains roughly 68'000 items.
-
-Edoc runs on the EPrints 3 document management system
-(https://github.com/eprints/eprints).\\
-!! Add technical description of Edoc.\\
-!! Perhaps add description of how files are added to Edoc, see PDF in
-\texttt{/todo}.
-
-\hypertarget{data-extraction}{%
-\subsubsection{Data extraction}\label{data-extraction}}
-
-Even though Edoc is a public server, its database does not have a
-web-ready API. In addition, since Edoc is a production server, its
-underlying database cannot be used directly on pain of disturbing the
-provided services. The data hence needs to be extracted from Edoc in
-order to work with it. This could for example be achieved by cloning the
-database of the server and running it on a local machine. However, this
-route was not available due to the limited resources of the responsible
-co-workers. I thus employed a workaround: Edoc has a built-in advanced
-search tool where the results can be exported. Even though it is not
-possible to extract all database items by default, only one of the many
-available search fields has to be filled in. The complete database can
-hence be extracted by only filling in the \texttt{Date} field and using
-a sufficiently permissive time period such as 1940 to 2020 since the
-oldest record in the database was published in 1942. On January 21 2021,
-this query yielded 68'345 results. These results were then exported as a
-326 MB JSON file called \texttt{1942-2020.json}. \texttt{1942-2020.json}
-has two drawbacks. First, the maximum file size on GitHub is 100 MB. And
-second, \texttt{1942-2020.json} is too big to be handled by standard
-editors requiring special editors such as Oxygen. For these reasons
-\texttt{1942-2020.json} was split into smaller files that are easier
-handled and can be uploaded to GitHub. For this
-\texttt{\_Utility.split\_json} was used yielding 14 files of size 20 MB
-or less containing 5000 or fewer entries each. These files are called
-\texttt{raw\_master\_x-y.json} (where x and y indicate the entries as
-given by \texttt{1942-2020.json}) and saved under \texttt{/edoc/raw}.
-
-\hypertarget{data-description-and-analysis}{%
-\subsubsection{Data description and
-analysis}\label{data-description-and-analysis}}
-
-!! Explain the Edoc data fields. Say perhaps something about the
-granularity of the relevant fields. Say something about how the fields
-are filled in (and by whom).
-
-\hypertarget{sample-data-set}{%
-\subsection{Sample data set}\label{sample-data-set}}
-
-In this section, I will explain how the sample data set is selected and
-constructed. ``Selection'' means the task of specifying a subset of the
-Edoc data and ``construction'' means the task of implementing this
-selection.
-
-\hypertarget{selection}{%
-\subsubsection{Selection}\label{selection}}
-
-There are a number of constraints for selecting the sample data set
-pertaining to an items's text, evaluability and the data set's scope.
-
-The first constraint stems from Annif, the machine indexing framework
-that will be used. Put simply, machine indexing assigns index terms to a
-text based on training data. The training data consists of a set of
-texts, a vocabulary, and function from vocabulary to texts. In this
-context we mean by ``text'' a sequence of words in a natural language
-and by ``vocabulary'' a set of words. Intuitively, the training data
-consists of pairs of text and subject terms that meet some standard. The
-training data and the vocabulary are already supplied by Annif, we only
-need to provide a text for each item that we want to be assigned index
-terms. Therefore, we only select items with text.
-
-The second constraint is that we must be able to evaluate the quality of
-the index terms assigned by Annif to any item in the sample data set.
-
-The third and final constraint takes into account the possibility of
-having to extend the prototype to the complete Edoc data. On the one
-hand, the sample data set should be small enough to allow for easy
-handling and rapid iteration. On the other hand, the sample data set
-should not be trivial but reflect the quirks and inadequacies of the
-complete dataset. In other words, we are looking for an abstraction
-rather than an idealization in the sense of Stokhof and van Lambalgen
-(2011).
-
-\hypertarget{construction}{%
-\subsubsection{Construction}\label{construction}}
-
-The first constraint is that each item in the sample data set needs to
-have a text. Intuitively, this text could consist of a title, an
-abstract, or even a full text, or any combination of the above. Similar
-to manual indexing, having more information (that is, longer texts)
-usually implies a higher indexing quality in machine indexing. However,
-this assumption needs to be confirmed empirically for the given machine
-indexing framework and data set. If indeed confirmed, it might be
-advisable only to index items that have a certain minimal text length.
-Therefore, in order to construct the sample data set, we require each
-item to have a non-empty value in the data fields \texttt{title},
-\texttt{abstract}, and \texttt{id\_number} as proxy to retrieve a full
-text remotely. Note that even more context could be provided by taking
-into account other data fields such as \texttt{type},
-\texttt{publication} or \texttt{department}. Especially the latter might
-be valuable when disambiguating homonymous or polysemous words. For
-example, consider the item
-\texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
-``Blacking Out.'' Without further context, this title could refer
-(amongst others) to a physiological phenomenon, a sudden loss of
-electricity, or a measure taken in wartime. Knowing that the item was
-published by a researcher employed by the Faculty of Business and
-Economics (and not, say, by the Faculty of Medicine) gives us reason to
-exclude the first meaning. However, this idea cannot be implemented with
-the out of the box instance of Annif employed in this chapter (see
-\protect\hyperlink{machine-indexing}{subsection ``Machine indexing''}).
-
-The second constraint is that the index terms assigned to each item in
-the sample data set must be assessable. How the assessment is conducted
-in detail is discussed in \protect\hyperlink{assessment}{section
-``Assessment''}. For now, it is sufficient to say that we require a
-standard against which we can evaluate the assigned index terms. By
-``standard'' I mean that given a vocabulary of index terms and our
-sample data set, for every item in the sample data set, there is an
-approved subset of the vocabulary. The production of a standard from
-scratch is of course is very costly since a person, usually highly
-skilled in a certain academic domain, must assign and/or approve each
-item's index terms (!!source). For this reason we try to avoid having to
-produce a standard. One way of doing so is by requiring items in the
-sample data set to have non-empty \texttt{keywords} data field. The
-caveats of this approach are discussed in
-\protect\hyperlink{assessment}{section ``Assessment''}.
-
-Taking into account the third constraint simply means that we do not
-employ any further restrictions. We can hence construct the sample data
-set by choosing exactly those items from \texttt{/edoc/raw} which have
-non-empty data fields \texttt{title}, \texttt{abstract},
-\texttt{id\_number}, and \texttt{keywords}. We do so by calling
-\texttt{\_Data.select\_from\_file} iteratively for all files in
-\texttt{/edoc/raw}. The resulting file is saved in
-\texttt{/edoc/selected} as \texttt{selected\_master.json}.
-
-\hypertarget{analysis}{%
-\subsubsection{Analysis}\label{analysis}}
-
-Of the 68'345 items in \texttt{/edoc/raw}, all have a title (non-empty
-\texttt{title} data field), a little more than half of the items have an
-abstract (37'381 items with non-empty \texttt{abstract} data field),
-roughly half of the items have an ID (35'355 items with non-empty
-\texttt{id\_number} data field),\footnote{Note that when using the facet
-  by blank on \texttt{id\_number} in OpenRefine, there are 57'153
-  matches; this is due to the fact that many items with an ID such as
-  DOI have secondary or tertiary IDs such as ISI or PMID.} and less than
-10\% of the items have keywords (6'660 items with non-empty
-\texttt{keywords} data field). The sample data set as requires all the
-above data fields to be non-empty;
-\texttt{/edoc/sample/sample\_master.json} has 4'111 items and hence
-constitutes 6\% of the raw data.
-
-In order to determine how well the sample data set represents the raw
-Edoc data, a one-sample chi-square test was conducted on each selection
-data field (see Parke 2013, chap. 1). The results indicate that the
-sample data proportions of items are significantly different from the
-raw Edoc data per department (see Figure 1 for more details).
-
-\begin{figure}
-\centering
-\includegraphics{images/chi_square_selection_fields.pdf}
-\caption{The sample data set (\(n\) = 4'111) is not representative of
-the raw Edoc data (\(n\) = 68'345) per department. Data field
-\texttt{abstract}: \(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data
-field \texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285,
-\(p < 0.001\); data field \texttt{keywords}: \(\chi^2 (df=9) =\)
-2'314.533, \(p < 0.001\). The data foundation is available at
-\texttt{/edoc/analysis} and the chi-square statistic can be calculated
-by calling \texttt{\_Analysis.chi\_square\_fit}.}
-\end{figure}
-
-The sample data set is hence not representative of the raw Edoc data.
-This is not surprising since its construction is strongly biased. This
-bias has the effect that the sample data set is significantly skewed
-towards English journal publications in the sciences, medicine and
-economics from the 21st century (see Figure 2 for more details). The
-upshot of this analysis is that the humanities are underrepresented in
-the sample data set. Therefore, any results with respect to the quality
-of machine indexing discussed below might not be applicable to the
-humanities.
-
-\begin{figure}
-\centering
-\includegraphics{images/raw_sample_analysis.pdf}
-\caption{The sample data set (\(n\) = 4'111) is significantly skewed
-towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
-1'441.414, \(p < 0.001\)) journal publications (data field
-\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
-sciences, medicine and economics (data field \texttt{department}:
-\(\chi^2 (df=9) =\) 14'447.276\$, \(p < 0.001\)) from the 21st (data
-field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\))
-century as compared to the raw Edoc data (\(n\) = 68'345). The data
-foundation is available at \texttt{/edoc/analysis} and the chi-square
-statistic can be calculated by calling
-\texttt{\_Analysis.chi\_square\_fit}.}
-\end{figure}
-
-\hypertarget{machine-indexing}{%
-\subsection{Machine indexing}\label{machine-indexing}}
-
-\hypertarget{general-overview}{%
-\subsubsection{General overview}\label{general-overview}}
-
-!! Give an overview over machine indexing.
-
-\hypertarget{annif}{%
-\subsubsection{Annif}\label{annif}}
-
-!! Given an intro to Annif. Explain that we are using the out of the box
-version
-
-\hypertarget{implementation}{%
-\subsubsection{Implementation}\label{implementation}}
-
-As explained above, for the prototype we will use the out
-
-!! Explain how to implementation works.
-
-In addition to the already used algorithms we should also try
-https://ai.finto.fi/?locale=en
-
-!! Somewhere here we talk about indexing based on title and/or abstract
-and/or fulltext. Fulltext is not yet implemented. Some observations to
-do so: - the link to the fulltext is constructed from the data fields
-\texttt{offical\ url} and \texttt{documebts\ -\ main}, e.g.,
-\texttt{https\ \ ://edoc.unibas.ch/79633/} + \texttt{1/} +
-\texttt{2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}
-to get
-\texttt{https://edoc.unibas.ch/79633/1/2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}
-
-\hypertarget{assessment}{%
-\subsection{Assessment}\label{assessment}}
-
-In this chapter I will construct three distinct gold standards in order
-to assess the quality of machine indexing the sample data set with
-Annif.\\
-!! Say something about assessments of Annif that have already been
-carried out.
-
-\hypertarget{gold-standard}{%
-\subsubsection{Gold standard}\label{gold-standard}}
-
-The most common approach for assessing the output of machine indexing is
-by systematically comparing it with a gold standard (sometimes also
-referred to as model or reference). Golub et al. (2016, 10) define a
-gold standard as ``a collection in which each document is assigned a set
-of subjects that is assumed to be complete and correct'' where
-``\emph{complete} means that all subjects that should be assigned to a
-document are in fact assigned, and \emph{correct} means that there are
-no subjects assigned that are irrelevant to the content.'' Put
-inversely, if an item in the gold standard lacks subject terms
-describing its content, the assignment is not complete; and if an item
-in the gold standard has been assigned subject terms that are not
-relevant to its content, the assignment is not correct.
-
-A gold standard is usually the product of manual indexing by
-``information experts, subject experts, or potential or real end users''
-(Golub et al. 2016, 10). This entails its own host of epistemic problems
-relating to objectivity and consistency of the assigned subject terms.
-Most importantly, however, the construction of a gold standard from
-scratch is very expensive. It is therefore not an option for the project
-at hand. Rather, I will construct what could be called derivative gold
-standards by reusing indexing data that is already available. Here we
-can distinguish two distinct kinds of derivative gold standards: first,
-I will construct a derivative gold standard based on the author keywords
-available in the sample data set; call this the ``native'' gold
-standard. Second, I will construct a derivative gold standard based on
-indexing metadata available in repositories distinct from Edoc; call
-this the ``foreign'' gold standard.
-
-There are other methods for assessing machine indexing quality besides
-comparison with a gold standard that are worth mentioning. These include
-an evaluation in the context of indexing workflows (Golub et al. 2016,
-13ff.), the assessment of retrieval performance (Golub et al. 2016,
-15--23.), and so-called model free assessments (Louis and Nenkova 2013).
-
-\hypertarget{extract-keywords}{%
-\paragraph{Extract keywords}\label{extract-keywords}}
-
-\hypertarget{clean-keywords}{%
-\paragraph{Clean keywords}\label{clean-keywords}}
-
-\hypertarget{frequency-analysis}{%
-\paragraph{Frequency analysis}\label{frequency-analysis}}
-
-\hypertarget{mapping-to-controlled-vocabularies}{%
-\paragraph{Mapping to controlled
-vocabularies}\label{mapping-to-controlled-vocabularies}}
-
-\hypertarget{precision-recall-f1-score}{%
-\subsubsection{Precision, recall,
-F1-score}\label{precision-recall-f1-score}}
-
-!! Discussion of metrics
-
-\hypertarget{annif-versus-gold-standard}{%
-\subsubsection{Annif versus gold
-standard}\label{annif-versus-gold-standard}}
-
-\hypertarget{yso}{%
-\paragraph{YSO}\label{yso}}
-
-\hypertarget{wikidata}{%
-\paragraph{Wikidata}\label{wikidata}}
-
-\hypertarget{annif-versus-mesh}{%
-\subsubsection{Annif versus MeSH}\label{annif-versus-mesh}}
-
-\hypertarget{digression-truth-conditions-for-indexing}{%
-\subsubsection{Digression: truth-conditions for
-indexing}\label{digression-truth-conditions-for-indexing}}
-
-(Correspondence theory of indexing: subject term T fits text X iff text
-X is about T) \#\#\# Targets !! Find out what I meant here.
-
-\hypertarget{analysis-1}{%
-\subsubsection{Analysis}\label{analysis-1}}
-
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-\hypertarget{outlook}{%
-\section{Outlook}\label{outlook}}
-
-\hypertarget{refinement}{%
-\subsection{Refinement}\label{refinement}}
-
-\hypertarget{implementation-strategy}{%
-\subsection{Implementation strategy}\label{implementation-strategy}}
-
-\hypertarget{other-use-cases}{%
-\subsection{Other use cases}\label{other-use-cases}}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-\hypertarget{bibliography}{%
-\section{Bibliography}\label{bibliography}}
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\begin{Shaded}
-\begin{Highlighting}[numbers=left,,]
-\KeywordTok{def}\NormalTok{ myfunction(var):}
-  \CommentTok{""" Oh how awesome this is. """}
-  \ControlFlowTok{pass}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Golub.2016}{}%
-Golub, Koraljka, Dagobert Soergel, George Buchanan, Douglas Tudhope,
-Marianne Lykke, and Debra Hiom. 2016. {``A Framework for Evaluating
-Automatic Indexing or Classification in the Context of Retrieval.''}
-\emph{Journal of the Association for Information Science and Technology}
-67 (1): 3--16. \url{https://doi.org/10.1002/asi.23600}.
-
-\leavevmode\hypertarget{ref-Louis.2013}{}%
-Louis, Annie, and Ani Nenkova. 2013. {``Automatically Assessing Machine
-Summary Content Without a Gold Standard.''} \emph{Computational
-Linguistics} 39 (2): 267--300.
-\url{https://doi.org/10.1162/COLI\%7B/textunderscore\%20\%7Da\%7B/textunderscore\%20\%7D00123}.
-
-\leavevmode\hypertarget{ref-Parke.2013}{}%
-Parke, Carol. 2013. \emph{Essential First Steps to Data Analysis:
-Scenario-Based Examples Using SPSS}. Thousand Oaks: {SAGE Publications}.
-\url{https://doi.org/10.4135/9781506335148}.
-
-\leavevmode\hypertarget{ref-Stokhof.2011}{}%
-Stokhof, Martin, and Michiel van Lambalgen. 2011. {``Abstractions and
-Idealisations: The Construction of Modern Linguistics.''}
-\emph{Theoretical Linguistics} 37 (1-2): 1--26.
-\url{https://doi.org/10.1515/thli.2011.001}.
-
-\end{CSLReferences}
+\input{./draft}
 

### 2021-02-17 text/draft.tex
histogram

@@
 want the keywords to follow a uniform format thereby joining
-morphological duplicates such as ``Gene,'' ``gene,'' " gene``,''/gene``.
-Also, some keywords are in fact keyword chains, for
-example''Dendrites/metabolism/ultrastructure". Keyword chains must be
-broken into their component keywords and then parsed again. The reason
-for this is that Annif only assigns flat keywords and not keyword
+morphological duplicates such as ``Gene,'' ``gene,'' ``gene\_,''
+``gene/,'' and so on. Also, some keywords are in fact keyword chains,
+for example ``Dendrites/metabolism/ultrastructure.'' Keyword chains must
+be broken into their component keywords and then parsed again. The
+reason for this is that Annif only assigns flat keywords and not keyword
 chains.
@@
 !! Frequency
+
+!! Cumulative sum histogram
+
+\begin{figure}
+\centering
+\includegraphics{images/keywords_clean_histogram_a.pdf}
+\caption{Bla.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{images/keywords_clean_histogram_b.pdf}
+\caption{Bla.}
+\end{figure}
 

### 2021-02-18 text/draft.tex
histogram

@@
 
-\texttt{\_Keywords.clean\_keywords} is the implementation the parser and
-the recursive cleaner is implemented by
+\texttt{\_Keywords.clean\_keywords} is the implementation the parser
+while the recursive cleaner is implemented by
 \texttt{\_Keywords.clean\_keyword}. To create the desired list of clean
@@
 
-!! Frequency
+\texttt{keywords/keywords\_clean.json} has 36'901 entries many of which
+are duplicates. We hence deduplicate and count the number of occurrences
+of each keyword. This is achieved by calling
+\texttt{\_Keywords.make\_histogram} on
+\texttt{keywords/keywords\_clean.json} and saving the output as
+\texttt{keywords/keywords\_clean\_histogram.json}:
 
-!! Cumulative sum histogram
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
+\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ \_Keywords.make\_histogram(keywords\_clean)}
+\NormalTok{\_Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+An analysis of \texttt{keywords/keywords\_clean\_histogram.json} shows
+that the distribution of keywords is strongly skewed right but that (see
+Figure 3 for details).
 
@@
 \centering
-\includegraphics{images/keywords_clean_histogram_a.pdf}
-\caption{Bla.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{images/keywords_clean_histogram_b.pdf}
-\caption{Bla.}
+\includegraphics{images/keywords_clean_histogram_abc.pdf}
+\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
+distribution of keywords is strongly skewed right
+(\(min = Q1 = M = Q3 = 1\) and \(max = 910\)). However, even though
+keywords with only one occurrence constitute over 75\% of the total
+keywords, they constitute less than 35\% of the total occurrences. The
+most common keywords with 50 or more occurrences are extreme outliers
+but make up almost 20\% of the total occurrences.}
 \end{figure}
@@
 \paragraph{Reconciliation}\label{reconciliation}}
+
+As explained in section X, Annif assigns index terms from a controlled
+vocabulary. If we want to assess the quality of the indexing via a gold
+standard, we must therefore ensure that the gold standard makes use of
+the vocabulary used by Annif. As seen in section Y, the relevant
+(English) vocabularies are Wikidata YSO. The next step in constructing
+the native gold standard is hence to reconcile the extracted and cleaned
+keywords with YSO and Wikidata.
+
+The tool of choice for reconciliation is OpenRefine (see
+\protect\hyperlink{openrefine}{section OpenRefine}). We import
+\texttt{keywords/keywords\_clean\_histogram.json} as a new project.
+
+Before we do so, let us briefly look at the data in
+\texttt{keywords/keywords\_clean.json}.
+
+for a given input text, Annif assigns index terms from some controlled
+vocabulary. Any gold standard employed to assess the quality of this
+indexing must therefore make use of the same controlled vocabulary.
 

### 2021-02-18 text/draft.tex
reconciliation

@@
 keywords with only one occurrence constitute over 75\% of the total
-keywords, they constitute less than 35\% of the total occurrences. The
-most common keywords with 50 or more occurrences are extreme outliers
-but make up almost 20\% of the total occurrences.}
+keywords, their occurrences constitute less than 35\% of the total
+occurrences. The most common keywords with 50 or more occurrences are
+extreme outliers but make up almost 20\% of the total occurrences.}
 \end{figure}
@@
 (English) vocabularies are Wikidata YSO. The next step in constructing
-the native gold standard is hence to reconcile the extracted and cleaned
-keywords with YSO and Wikidata.
+the native gold standard is hence to match the extracted and cleaned
+keywords with keywords from YSO and Wikidata. This process is called
+``reconciliation'' (see https://docs.openrefine.org/manual/reconciling)
+and the tool of choice for this task is OpenRefine (see
+\protect\hyperlink{openrefine}{section OpenRefine}).
 
-The tool of choice for reconciliation is OpenRefine (see
-\protect\hyperlink{openrefine}{section OpenRefine}). We import
-\texttt{keywords/keywords\_clean\_histogram.json} as a new project.
+In what follows, I will describe how the cleaned keywords were
+reconciled with Wikidata and YSO, and which additional steps for
+refinement were undertaken. In total, 2'104 data transformation
+operations were performed; the complete operation history is available
+as \texttt{/keywords/operation\_history.json}. First
+\texttt{keywords/keywords\_clean\_histogram.json} was set as a new
+project in OpenRefine. The \texttt{keyword} column was then duplicated
+and reconciled with Wikidata. Here the parameters were chosen as
+follows: reconcile against no particular type, and auto-match candidates
+with high confidence.
 

### 2021-02-19 text/draft.tex
draft writing

@@
 An analysis of \texttt{keywords/keywords\_clean\_histogram.json} shows
-that the distribution of keywords is strongly skewed right but that (see
-Figure 3 for details).
+that the lion's share of keywords has only one occurrence but that the
+total occurrences are predominantly made up of keywords with more than
+one occurrence (see Figure 3 for details).
 
@@
 operations were performed; the complete operation history is available
-as \texttt{/keywords/operation\_history.json}. First
-\texttt{keywords/keywords\_clean\_histogram.json} was set as a new
-project in OpenRefine. The \texttt{keyword} column was then duplicated
-and reconciled with Wikidata. Here the parameters were chosen as
-follows: reconcile against no particular type, and auto-match candidates
-with high confidence.
+as \texttt{/keywords/operation\_history.json}.
+
+A new project in OpenRefine was created and the data from
+\texttt{keywords/keywords\_clean\_histogram.json} was imported. The
+\texttt{keyword} column was then duplicated and reconciled with
+Wikidata. Here the parameters were chosen as follows: reconcile against
+no particular type, and auto-match candidates with high confidence.
+
+There were X automatic matches (call them ``suggestions''). The quality
+of these suggestions was then evaluated by random sampling. A suggestion
+is considered to be correct if and only if the meaning of the keyword
+from \texttt{keywords/keywords\_clean\_histogram.json} corresponds to
+the meaning of the suggested subject term from Wikidata. Note that for
+homonymous or polysemous keywords, it is impossible to confirm a correct
+match without further context; those keywords therefore cannot be
+reconciled (but see \protect\hyperlink{construction}{section
+``Construction''} for a possible solution).
+
+Unfortunately, random sampling showed that the overall quality of the
+suggestions was not satisfactory. A two-pronged strategy was adopted to
+ameliorate the quality of the reonciliation:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  manual matching of the top results
+\item
+  automated processes for the rest
+\end{enumerate}
+
+!! calculate for each of annif yso mesh how many percent of keywords or
+total occurrences are covered by reonciliated data.
 
@@
 !! Does the OpenRefine project still exist? Export the list of changes!
+http://127.0.0.1:3333/project?project=2501403769019\&ui=\%7B\%22facets\%22\%3A\%5B\%7B\%22c\%22\%3A\%7B\%22type\%22\%3A\%22list\%22\%2C\%22name\%22\%3A\%22qid\%22\%2C\%22columnName\%22\%3A\%22qid\%22\%2C\%22expression\%22\%3A\%22isBlank(value)\%22\%2C\%22omitBlank\%22\%3Afalse\%2C\%22omitError\%22\%3Afalse\%2C\%22selectBlank\%22\%3Afalse\%2C\%22selectError\%22\%3Afalse\%2C\%22invert\%22\%3Afalse\%7D\%2C\%22o\%22\%3A\%7B\%22sort\%22\%3A\%22name\%22\%7D\%2C\%22s\%22\%3A\%5B\%5D\%7D\%5D\%7D
 

### 2021-02-19 edoc/edoc_main.py

@@ -540,19 +540,19 @@ OK 3. We select a subset of the entries downloaded from edoc. We use _Data.selec
 items from which to construct a gold standard). The resulting 4111 items are saved as sample_master.json in 
 edoc/sample.
 
-4. We extract the keywords (per entry) from the sample entries with _Keywords.extract_keywords like so:
+ok 4. We extract the keywords (per entry) from the sample entries with _Keywords.extract_keywords like so:
 keywords = _Keywords.extract_keywords(DIR + "/sample/sample_master.json")
 We the save the resulting list under edoc/keywords as keywords_raw.json like so:
 _Utility.save_json(keywords, DIR + "/keywords/keywords_extracted.json")
 
-5. We clean the extracted keywords with _Keywords.clean_keywords. How and why this is done is explained elsewhere. This 
+ok 5. We clean the extracted keywords with _Keywords.clean_keywords. How and why this is done is explained elsewhere. This 
 is done as follows:
 keywords_extracted = _Utility.load_json(DIR + "/keywords/keywords_extracted.json")
 keywords_clean = _Keywords.clean_keywords(keywords_extracted)
 We the save the resulting list under edoc/keywords as keywords_clean.json like so:
 _Utility.save_json(clean, DIR + "keywords/keywords_clean.json")
 
-6. We build a histogram of the cleaned keywords used in the sample data with _Keyword.make_histogram:
+ok 6. We build a histogram of the cleaned keywords used in the sample data with _Keyword.make_histogram:
 keywords_clean = _Utility.load_json(DIR + "/keywords/keywords_clean.json")
 histogram = _Keyword.make_histogram(keywords)
 We the save the resulting histogram under edoc/keywords as keywords_clean_histogram.json like so:
@@ -579,7 +579,7 @@ _Data.enrich_with_mesh(DIR + "/indexed/indexed_master.json", DIR + "/indexed/ind
 10. We enrich the sample items with cleaned author keywords (including, if available, Qid, MeSH ID, YSO ID) based on 
 the reference keywords; the resulting file is indexed_master_mesh_enriched.json. To do so:
 _Data.enrich_author_keywords(DIR + "/indexed/indexed_master_mesh.json", DIR + "/indexed/indexed_master_mesh_enriched")
-NOTE: rerun this whenever we amend the reference keywords!
+NOTE: rerun this whenever we amend the reference keywords! WE MUST DO THIS NOW
 """
 
 #TODO:

### 2021-02-19 text/draft.tex
reconcilement

@@
 https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation
-for details).
+for details). ALso note that OpenRefine always counts the number of
+records by the first column (a fact which caused me many headaches).
 
@@
 
-There were X automatic matches (call them ``suggestions''). The quality
-of these suggestions was then evaluated by random sampling. A suggestion
-is considered to be correct if and only if the meaning of the keyword
-from \texttt{keywords/keywords\_clean\_histogram.json} corresponds to
-the meaning of the suggested subject term from Wikidata. Note that for
-homonymous or polysemous keywords, it is impossible to confirm a correct
-match without further context; those keywords therefore cannot be
-reconciled (but see \protect\hyperlink{construction}{section
-``Construction''} for a possible solution).
+There were X automatic matches (call them ``suggestions''). A suggestion
+is correct if and only if the meaning of the keyword from
+\texttt{keywords/keywords\_clean\_histogram.json} corresponds to the
+meaning of the suggested concept from Wikidata. Note that for homonymous
+or polysemous keywords, it is impossible to confirm a correct match
+without further context; those keywords therefore cannot be reconciled
+(but see \protect\hyperlink{construction}{section ``Construction''} for
+a possible solution). Unfortunately, random sampling showed that the
+overall quality of the reconciliation was not satisfactory, that is,
+there were too many incorrect suggestions. A two-pronged strategy was
+adopted to ameliorate the quality of the reconciliation.
 
-Unfortunately, random sampling showed that the overall quality of the
-suggestions was not satisfactory. A two-pronged strategy was adopted to
-ameliorate the quality of the reonciliation:
+First, the suggestions to the top 500 keywords were manually verified.
+These keywords account for 14'996 occurrences or 40.638\% of the total
+occurrences and are constitute thus an effective lever.
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  manual matching of the top results
-\item
-  automated processes for the rest
-\end{enumerate}
+Second, systematic biases were identified and removed. The most
+prevalent bias was an due to a suggestion's type. As stated above, the
+reconciliation service API was not constrained by type but had access to
+the complete Wikidata database. Since Wikidata is an ontology that
+encompasses everything, it also features types whose concepts cannot
+qualify as subject terms (at least in the present context). The most
+prominent example is the type Q13442814 ``scholarly article.'' Wikidata
+contains the metadata of many scholarly articles. Now, for some of our
+keywords, there is a scholarly article with a title that exactly matches
+the keyword; and since there is no restriction concerning the type, the
+scholarly article is suggested with high confidence (see
+https://github.com/OpenRefine/OpenRefine/wiki/Reconciliation-Service-API
+for details). For example, {[}keyword/article{]}. To generalize,
+suggestions with types whose concepts are proper names are usually
+incorrect. Based on this observation, suggestions with the following
+types were rejected: ``scholarly article,'' ``clinical trial,''
+``scientific journal,'' ``academic journal,'' ``open access journal,''
+``thesis,'' ``doctoral thesis,'' ``natural number.'' Suggestions with
+the following types were manually verified (i.e., checked for
+correctness): ``human,'' ``album,'' ``film,'' ``musical group,''
+``business,'' ``literary work,'' ``television series,''
+``organization,'' ``family name,'' ``written work,'' ``video game,''
+``single, television series episode,'' ``painting,'' ``commune of
+France,'' ``city of the United States,'' ``magazine,'' ``studio album,''
+``year,'' ``nonprofit organization,'' ``border town,'' ``international
+organization,'' ``political party,'' ``software,'' ``song,''
+``website,'' ``article comic strip,'' ``collection,'' ``commune of
+Italy,'' ``fictional human,'' ``film,'' ``government agency,''
+``village,'' ``academic journal article,'' ``female given name,''
+``poem.''
+
+A second bias found was
+
+After completing these steps to ameliorate the quality of the
+reconciliation,
+
+then suggests this scholarly article with high confidence.
+
+However, certain types of concepts cannot qualify as subject terms
+
+!! probabilistic random sampling to assess quality, weighted by
+occurrences
 
 !! calculate for each of annif yso mesh how many percent of keywords or
-total occurrences are covered by reonciliated data.
+total occurrences are covered by reonciliated data: - Qid: 28789
+occurrences, 9635 keywords - Yso: 14557 occurrences, 3185 keywords -
+Mesh: 19775 occurrences, 4619 keywords
 

### 2021-02-19 text/draft.tex
reconcilement

@@
 \caption{The sample data set (\(n\) = 4'111) is not representative of
-the raw Edoc data (\(n\) = 68'345) per department. Data field
+the raw Edoc data (\(N\) = 68'345) per department. Data field
 \texttt{abstract}: \(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data
@@
 field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\))
-century as compared to the raw Edoc data (\(n\) = 68'345). The data
+century as compared to the raw Edoc data (\(N\) = 68'345). The data
 foundation is available at \texttt{/edoc/analysis} and the chi-square
@@
 
-In what follows, I will describe how the cleaned keywords were
+In this section, I will describe how the cleaned keywords were
 reconciled with Wikidata and YSO, and which additional steps for
@@
 
-A new project in OpenRefine was created and the data from
-\texttt{keywords/keywords\_clean\_histogram.json} was imported. The
-\texttt{keyword} column was then duplicated and reconciled with
-Wikidata. Here the parameters were chosen as follows: reconcile against
-no particular type, and auto-match candidates with high confidence.
+The data from \texttt{keywords/keywords\_clean\_histogram.json} was
+imported into OpenRefine. The \texttt{keyword} column was then
+duplicated and reconciled with Wikidata. Here the parameters were chosen
+as follows: reconcile against no particular type, and auto-match
+candidates with high confidence.
 
@@
 These keywords account for 14'996 occurrences or 40.638\% of the total
-occurrences and are constitute thus an effective lever.
+occurrences and thus constitute an effective lever.
 
@@
 
-A second bias found was
+With these improvements in place, each keyword with a suggestion was
+assigned a QID via the ``Add cloumns from reconciled values''-function
+(and similar for YSO and MeSH identifiers). The data was then exported
+and saved as \texttt{/keywords/keywords\_reference.json}. Keywords with
+a QID now constitute 69\% of all keywords and 78\% of their total
+occurrences in the sample data set, but these numbers are much lower for
+YSO and MeSH identifiers (see Figure 4 for details).
 
-After completing these steps to ameliorate the quality of the
-reconciliation,
+\begin{figure}
+\centering
+\includegraphics{images/native_gold_standard.pdf}
+\caption{The coverage of \texttt{/keywords/keywords\_reference.json} by
+the controlled vocabularies of Wikidata (QID), Medical Subject Headings
+(MeSH), and YSO (General Finnish Ontology). Both MeSH and YSO are
+dependent on QID but independent of each other.}
+\end{figure}
 
-then suggests this scholarly article with high confidence.
+Let us now turn to the evaluation of the reconciliation: how many of the
+suggestions were correct? This question was answered via random
+sampling. The random sample (\(n=500\)) was created by calling
+\texttt{\_Analysis.make\_random\_sample} on
+\texttt{/keywords/reference\_keywords.json}; it is available at
+\texttt{analysis/random\_keywords.json}. The sample was then imported
+into OpenRefine and the judgement (1 for correct, 0 for incorrect) of
+the manual verification was recorded in the column
+\texttt{verification}. The data was then exported and is available at
+\texttt{analysis/random\_keywords\_verified.csv}.
 
-However, certain types of concepts cannot qualify as subject terms
+An analysis of this data shows that 53\% of the suggestions in the
+random sample were correct with a 95\% confidence interval of 48.8\% to
+57.3\%. We can therefore conclude that 8'507 \(\pm\) 692.1 of the 16'050
+keywords in \texttt{/keywords/reference\_keywords.json} have correct
+suggestions. Note that of the 235 incorrect suggestions in the random
+sample, 188 were incorrect by default because they were missing a QID;
+the share of non-empty yet incorrect suggestions is only 9.4\% in the
+random sample meaning that the quality of the reconciliation is not as
+disappointing as it might seem at first glance.
 
-!! probabilistic random sampling to assess quality, weighted by
-occurrences
-
-!! calculate for each of annif yso mesh how many percent of keywords or
-total occurrences are covered by reonciliated data: - Qid: 28789
-occurrences, 9635 keywords - Yso: 14557 occurrences, 3185 keywords -
-Mesh: 19775 occurrences, 4619 keywords
-
-Before we do so, let us briefly look at the data in
-\texttt{keywords/keywords\_clean.json}.
-
-for a given input text, Annif assigns index terms from some controlled
-vocabulary. Any gold standard employed to assess the quality of this
-indexing must therefore make use of the same controlled vocabulary.
-
-!! Mapping to controlled vocabularies; explain why this is necessary.
-
-!! Does the OpenRefine project still exist? Export the list of changes!
-http://127.0.0.1:3333/project?project=2501403769019\&ui=\%7B\%22facets\%22\%3A\%5B\%7B\%22c\%22\%3A\%7B\%22type\%22\%3A\%22list\%22\%2C\%22name\%22\%3A\%22qid\%22\%2C\%22columnName\%22\%3A\%22qid\%22\%2C\%22expression\%22\%3A\%22isBlank(value)\%22\%2C\%22omitBlank\%22\%3Afalse\%2C\%22omitError\%22\%3Afalse\%2C\%22selectBlank\%22\%3Afalse\%2C\%22selectError\%22\%3Afalse\%2C\%22invert\%22\%3Afalse\%7D\%2C\%22o\%22\%3A\%7B\%22sort\%22\%3A\%22name\%22\%7D\%2C\%22s\%22\%3A\%5B\%5D\%7D\%5D\%7D
+!! Talk about enrichment with yso and mesh
 

### 2021-02-19 edoc/edoc_main.py

@@ -509,10 +509,29 @@ class _Analysis:
         print(f"Results for {name}")
         print(scipy.stats.chisquare(f_obs=observed, f_exp=expected))
 
+    @classmethod
+    def make_random_sample(cls,
+                           file_path: str,
+                           save_path: str,
+                           size: int) -> None:
+        """ Save a random sample from the population in the file.
+
+        :param file_path: complete path to file including filename and extension
+        :param save_path: complete path to save folder including filename and extension
+        :param size: the sample size
+        """
+
+        population = _Utility.load_json(file_path)
+        import random
+
+        sample = random.sample(population=population, k=size)
+        _Utility.save_json(sample, save_path)
 
 
+_Analysis.make_random_sample(DIR + "/keywords/keywords_reference.json", DIR + "/analysis/random_keywords.json", 500)
 
-_Analysis.chi_square_fit(DIR + "/analysis/chi_square_language.csv")
+
+exit()
 
 #_Keywords.enrich_with_yso(DIR + "/keywords/keywords_reference.json", DIR + "/keywords/keywords_reference_test.json")
 

### 2021-02-22 text/draft.tex
reconcilement

@@
-Machine indexing of institutional repositories: indexing Edoc with Annif
-and BARTOC FAST as proof of concept
-
 \hypertarget{introduction}{%
@@
 extracted from the \texttt{keywords} data fields as per
-\texttt{keywords/keywords\_extracted.json}. In Edoc, the
+\texttt{/keywords/keywords\_extracted.json}. In Edoc, the
 \texttt{keywords} data field of an item is a non-mandatory free text
@@
 heterogeneous data in the \texttt{keywords} data field. To wit, the
-items of \texttt{keywords/keywords\_extracted.json} are strings where
+items of \texttt{/keywords/keywords\_extracted.json} are strings where
 single keywords are individuated by any symbols the user saw fit. So,
-for each item in \texttt{keywords/keywords\_extracted.json}, the user
+for each item in \texttt{/keywords/keywords\_extracted.json}, the user
 input must be parsed into single keywords.
@@
 \texttt{\_Keywords.clean\_keyword}. To create the desired list of clean
-keywords, saved as \texttt{keywords/keywords\_clean.json}, we call
+keywords, saved as \texttt{/keywords/keywords\_clean.json}, we call
 \texttt{\_Keywords.clean\_keywords} with the extracted keywords as
@@
 
-\texttt{keywords/keywords\_clean.json} has 36'901 entries many of which
+\texttt{/keywords/keywords\_clean.json} has 36'901 entries many of which
 are duplicates. We hence deduplicate and count the number of occurrences
@@
 \texttt{\_Keywords.make\_histogram} on
-\texttt{keywords/keywords\_clean.json} and saving the output as
-\texttt{keywords/keywords\_clean\_histogram.json}:
+\texttt{/keywords/keywords\_clean.json} and saving the output as
+\texttt{/keywords/keywords\_clean\_histogram.json}:
 
@@
 
-An analysis of \texttt{keywords/keywords\_clean\_histogram.json} shows
+An analysis of \texttt{/keywords/keywords\_clean\_histogram.json} shows
 that the lion's share of keywords has only one occurrence but that the
@@
 
-The data from \texttt{keywords/keywords\_clean\_histogram.json} was
+The data from \texttt{/keywords/keywords\_clean\_histogram.json} was
 imported into OpenRefine. The \texttt{keyword} column was then
@@
 is correct if and only if the meaning of the keyword from
-\texttt{keywords/keywords\_clean\_histogram.json} corresponds to the
+\texttt{/keywords/keywords\_clean\_histogram.json} corresponds to the
 meaning of the suggested concept from Wikidata. Note that for homonymous
@@
 a QID now constitute 69\% of all keywords and 78\% of their total
-occurrences in the sample data set, but these numbers are much lower for
-YSO and MeSH identifiers (see Figure 4 for details).
+occurrences in the sample data set, but these numbers are significantly
+lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
+of all occurrences) and especially low for the YSO identifier (X of all
+keywords with Y of all occurrences). In both cases, the problem is due
+to the fact that Wikidata's mapping of MeSH respectively YSO is only
+partial. There can be two reasons for this state of affairs for a given
+entry: either there is no match between Wikidata and YSO or MeSH (after
+all, Wikidata is much larger than MeSH and YSO taken together), or there
+is a match but it has not yet been added to the mapping. In the latter
+case, at least with respect to YSO, there is a solution: Finto provides
+a REST-sytle API to access the YSO vocabulary directly (see
+https://api.finto.fi/). For each keyword in in the list of reference
+keywords that lacks a YSO identifier, the Finto API is queried; if a
+term turns up, it is added to the keyword. The effect of this second
+reconcilement is detailed in Figure 4. It is achieved by calling
+\texttt{\_Keywords.enrich\_with\_yso} on
+\texttt{/keywords/keywords\_reference.json} and saving the output as
+\texttt{/keywords/keywords\_reference\_master.json}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
+\NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ \_Keywords.enrich\_with\_yso(keywords\_reference)}
+\NormalTok{\_Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 \includegraphics{images/native_gold_standard.pdf}
-\caption{The coverage of \texttt{/keywords/keywords\_reference.json} by
-the controlled vocabularies of Wikidata (QID), Medical Subject Headings
-(MeSH), and YSO (General Finnish Ontology). Both MeSH and YSO are
-dependent on QID but independent of each other.}
+\caption{The coverage of
+\texttt{/keywords/keywords\_reference\_master.json} by the controlled
+vocabularies of Wikidata (QID), Medical Subject Headings (MeSH), and YSO
+(General Finnish Ontology). Both MeSH and YSO are dependent on QID but
+independent of each other. YSO enriched is the superset of YSO created
+by reconciling keywords that lack a YSO identifier directly with the YSO
+database provided by the Finto API; it is hence independent of
+Wikidata.}
 \end{figure}
@@
 \texttt{\_Analysis.make\_random\_sample} on
-\texttt{/keywords/reference\_keywords.json}; it is available at
-\texttt{analysis/random\_keywords.json}. The sample was then imported
+\texttt{/keywords/reference\_keywords\_master.json}; it is available at
+\texttt{/analysis/random\_keywords.json}. The sample was then imported
 into OpenRefine and the judgement (1 for correct, 0 for incorrect) of
@@
 \texttt{verification}. The data was then exported and is available at
-\texttt{analysis/random\_keywords\_verified.csv}.
+\texttt{/analysis/random\_keywords\_verified.csv}.
 
@@
 
-!! Talk about enrichment with yso and mesh
-
 \hypertarget{foreign-gold-standard}{%
@@
 
-!! Todo: - Explain MeSH\\
-- Explain how to get MeSH for subset of sample data set
+\begin{itemize}
+\tightlist
+\item
+  !! Explain MeSH
+\item
+  !! Explain how to get MeSH for subset of sample data set
+\end{itemize}
 

### 2021-02-22 edoc/edoc_main.py

@@ -533,7 +533,7 @@ _Analysis.make_random_sample(DIR + "/keywords/keywords_reference.json", DIR + "/
 
 exit()
 
-#_Keywords.enrich_with_yso(DIR + "/keywords/keywords_reference.json", DIR + "/keywords/keywords_reference_test.json")
+#_Keywords.enrich_with_yso(DIR + "/keywords/keywords_reference.json", DIR + "/keywords/keywords_reference_master.json")
 
 #print(_Keywords.fetch_yso("drug"))
 

### 2021-02-23 text/draft.tex
metrics

@@
 
-In this chapter I will construct three distinct gold standards in order
-to assess the quality of machine indexing the sample data set with
-Annif.\\
+In this chapter I will construct two distinct gold standards in order to
+assess the quality of machine indexing the sample data set with Annif.\\
 !! Say something about assessments of Annif that have already been
@@
 
+In this chapter I will assess the quality of the sample data set's
+indexing with Annif based on the native and foreign gold standards.
+
 \hypertarget{precision-recall-f1-score}{%
@@
 
-!! Discussion of metrics
+The metrics used for the assessment are precision, recall and F1 score.
+Precision and recall are standard metrics for indexing quality (e.g.,
+Gantert 2016, 197) whereby the F1 score plays are more prominent role in
+the assessment of machine indexing (e.g., Suominen 2018, 11--14; Toepfer
+and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
+(such as indexing consistency, transparency, reproducability) that are
+neglected here.
+
+Let us briefly look at the definitions and motivations of the chosen
+metrics. Recall that a suggestion of a subject term is correct if and
+only if the subject term is in the native gold standard. The possible
+outcomes are summarized in Table 1.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lllll}
+ &                       & \multicolumn{2}{l}{Suggested by Annif?}            &  \\ \cline{3-4}
+ & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{Yes} &  \\ \cline{2-4}
+\multicolumn{1}{l|}{\multirow{2}{*}{In gold standard?}} & \multicolumn{1}{l|}{No}  & \multicolumn{1}{l|}{True negative}  & \multicolumn{1}{l|}{False positive} &  \\ \cline{2-4}
+\multicolumn{1}{l|}{}                                   & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{False negative} & \multicolumn{1}{l|}{True positive}  &  \\ \cline{2-4}
+\end{tabular}
+\caption{Annif confusion matrix.}
+\label{tab:confusion-matrix}
+\end{table}
+
+\hypertarget{precision}{%
+\paragraph{Precision}\label{precision}}
+
+``Precision'' is the fraction of the correctly suggested subject terms;
+a suggestion is correct if and only if it is in the native gold
+standard:
+
+\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False positive}}\)
+
+Or put as question: what fraction of the subject terms suggested by
+Annif are also in the native gold standard?
+
+\hypertarget{recall}{%
+\paragraph{Recall}\label{recall}}
+
+``Recall'' is the fraction of correct subject terms out of all correct
+subject terms:
+
+\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{False negative} + \text{False positive}}\)
+
+Put as question: what fraction of the subject terms in the gold standard
+were suggested by Annif?
+
+\hypertarget{f1-score}{%
+\paragraph{F1-score}\label{f1-score}}
+
+The F1-score is the harmonic mean between precision and recall:
+
+\(\text{F1} = \displaystyle 2 * \frac{\text{Precision} * \text{Recall}}{\text{Precision} + \text{Recall}}\)
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Gantert.2016}{}%
+Gantert, Klaus. 2016. \emph{Bibliothekarisches Grundwissen}. 9.,
+vollst{ä}ndig neu bearbeitete und erweiterte Auflage. Berlin: {De
+Gruyter Saur}. \url{https://doi.org/10.1515/9783110321500}.
+
 \leavevmode\hypertarget{ref-Golub.2016}{}%
@@
 
+\leavevmode\hypertarget{ref-Suominen.2018}{}%
+Suominen, Osma. 2018. {``Annif: DIY Automated Subject Indexing Using
+Multiple Algorithms.''} \emph{LIBER Quarterly} 29 (1): 1--25.
+\url{https://doi.org/10.18352/lq.10285}.
+
+\leavevmode\hypertarget{ref-Toepfer.2016}{}%
+Toepfer, Martin, and Andreas Oskar Kempf. 2016. {``Automatische
+Indexierung Auf Basis von Titeln Und Autoren-Keywords -- Ein
+Werkstattbericht.''} \emph{027.7 Zeitschrift f{ü}r Bibliothekskultur /
+Journal for Library Culture} 4 (2): 84--97.
+\url{https://0277.ch/ojs/index.php/cdrs_0277/article/view/156/354}.
+
 \leavevmode\hypertarget{ref-UniversitatBasel.2021}{}%

### 2021-02-23 edoc/edoc_main.py

@@ -180,8 +180,8 @@ class _Data:
         :param keyword: the keyword
         """
 
-        # load reference keywords (for now keywords_clean_histogram_enriched.csv):
-        keywords_reference = _Utility.load_json(DIR + "/keywords/keywords_reference.json")
+        # load reference keywords:
+        keywords_reference = _Utility.load_json(DIR + "/keywords/keywords_reference_master.json")
 
         # enrich keywords
         for entry in keywords_reference:
@@ -577,13 +577,13 @@ histogram = _Keyword.make_histogram(keywords)
 We the save the resulting histogram under edoc/keywords as keywords_clean_histogram.json like so:
 _Utility.save_json(histogram, "/keywords/keywords_clean_histogram.json")
 
-7a. We create a list of reference keywords from the author keywords. To do this we use OpenRefine to match keywords from 
+ok 7a. We create a list of reference keywords from the author keywords. To do this we use OpenRefine to match keywords from 
 keywords_clean_histogram.json to Wikidata and other ontologies. This is explained elsewhere: draft-document OpenRefine 
 methods up to 20210121. The resulting file is exported as keywords_clean_histogram_enriched.csv and then transformed to 
 keywords_reference.json. Problem with exports here: multiple IDs are lost  (e.g., keyword clean ethnology has two mesh 
 ids Q000208 and D005007 but the second is on different line and exported as standing alone...). 
 
-7b. We try to enrich the reference keywords with YSO ids wherever they are missing. Increases YSO coverage from 1759 to
+ok 7b. We try to enrich the reference keywords with YSO ids wherever they are missing. Increases YSO coverage from 1759 to
 3185. To do this:
 _Keywords.enrich_with_yso(DIR + "/keywords/keywords_reference.json", DIR + "/keywords/keywords_reference-test.json")
 
@@ -595,7 +595,7 @@ be indexed with MeSH on PubMed, 1653 items match this requirement); the resultin
 so: 
 _Data.enrich_with_mesh(DIR + "/indexed/indexed_master.json", DIR + "/indexed/indexed_master_mesh")
 
-10. We enrich the sample items with cleaned author keywords (including, if available, Qid, MeSH ID, YSO ID) based on 
+OK 10. We enrich the sample items with cleaned author keywords (including, if available, Qid, MeSH ID, YSO ID) based on 
 the reference keywords; the resulting file is indexed_master_mesh_enriched.json. To do so:
[…]

### 2021-02-23 edoc/edoc_main.py
implement precision

@@ -527,20 +527,94 @@ class _Analysis:
         sample = random.sample(population=population, k=size)
         _Utility.save_json(sample, save_path)
 
+    @classmethod
+    def precision(cls,
+                  file_path: str,
+                  project_id: str,
+                  abstract: bool = False,
+                  fulltext: bool = False,
+                  limit: int = None,
+                  threshold: int = None) -> None:
 
-_Analysis.make_random_sample(DIR + "/keywords/keywords_reference.json", DIR + "/analysis/random_keywords.json", 500)
+        """ Calculate precision for items in file.
+
+        Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
+
+        :param file_path: complete path to file including filename and extension
+        :param project_id: Annif-client project ID
+        :param abstract: toggle use abstract for indexing, defaults to False
+        :param fulltext: toggle use fulltext for indexing, defaults to False
+        :param limit: Annif-client limit, defaults to None
+        :param threshold: Annif-client threshold, defaults to None
+        """
+
+        data = _Utility.load_json(file_path)
+
+        debug_c = 0
+
+        for item in data:
+            if debug_c > 0:
+                break
+            cls.item_precision(item,
+                               project_id,
+                               abstract,
+                               fulltext,
+                               limit,
+                               threshold)
+            debug_c = debug_c + 1
+
+    @classmethod
+    def item_precision(cls,
+                       item: dict,
+                       project_id: str,
+                       abstract: bool = False,
+                       fulltext: bool = False,
+                       limit: int = None,
+                       threshold: int = None) -> None:
+
+        """ Calculate precision for an item.
+
+        Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
+
+        :param item: sample data set item
+        :param project_id: Annif-client project ID
+        :param abstract: toggle use abstract for indexing, defaults to False
+        :param fulltext: toggle use fulltext for indexing, defaults to False
+        :param limit: Annif-client limit, defaults to None
+        :param threshold: Annif-client threshold, defaults to None
+        """
+
+        # construct the correct annif marker:
+        marker = f"{project_id}-{abstract}-{fulltext}-{limit}-{threshold}"
+
[…]

### 2021-02-23 edoc/edoc_main.py
metrics implementation

@@ -9,6 +9,7 @@ import urllib3
 import xmltodict
 import ast
 import scipy.stats
+from sklearn.metrics import recall_score, precision_score
 
 
 DIR = os.path.dirname(__file__)
@@ -587,13 +588,34 @@ class _Analysis:
         # construct the correct annif marker:
         marker = f"{project_id}-{abstract}-{fulltext}-{limit}-{threshold}"
 
-        # get the annif suggestions for marker:
+        # get the annif suggestions for the marker from the item:
         annif_suggestions = item.get("annif").get(marker)
         print(annif_suggestions)
+
+        # get the IDs from the suggestions:
+        annif_suggestions_ids = []
+        for suggestion in annif_suggestions:
+            annif_suggestions_ids.append(suggestion.get("uri"))
 
         # get gold standard:
         gold_standard = item.get("keywords enriched")
         print(gold_standard)
+
+        # get ID type from marker:
+        if project_id == "wikidata-en":
+            id_type = "qid"
+        else:
+            id_type = "yso id"
+
+        # get IDs from the gold standard:
+        gold_standard_ids = []
+        for keyword in gold_standard:
+            if keyword.get(id_type) is "":
+                continue
+            else:
+                gold_standard_ids.append(keyword.get(id_type))
+
+        print(gold_standard_ids)
 
         # transform gold standard (Abgleich der IDs mit annif)
         pass
@@ -601,18 +623,15 @@ class _Analysis:
         # calculate precision
         # https://scikit-learn.org/stable/modules/generated/sklearn.metrics.precision_score.html#sklearn.metrics.precision_score
 
-
-
-
-
-
 _Analysis.precision(DIR + "/indexed/indexed_master_mesh_enriched.json",
                     project_id="wikidata-en",
                     abstract=True)
+exit()
+y_true = [0, 1, 1]
+y_pred = [1, 1, 0]
 
-
-
-
+print(f"recall: {recall_score(y_true, y_pred)}")
+print(f"precision: {precision_score(y_true, y_pred)}")
 
 exit()
 """

### 2021-02-24 edoc/edoc_main.py
implement metrics

@@ -529,15 +529,15 @@ class _Analysis:
         _Utility.save_json(sample, save_path)
 
     @classmethod
-    def precision(cls,
-                  file_path: str,
-                  project_id: str,
-                  abstract: bool = False,
-                  fulltext: bool = False,
-                  limit: int = None,
-                  threshold: int = None) -> None:
+    def metrics(cls,
+                file_path: str,
+                project_id: str,
+                abstract: bool = False,
+                fulltext: bool = False,
+                limit: int = None,
+                threshold: int = None) -> None:
 
-        """ Calculate precision for items in file.
+        """ Get metrics for items in file.
 
         Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
 
@@ -554,26 +554,26 @@ class _Analysis:
         debug_c = 0
 
         for item in data:
-            if debug_c > 0:
+            if debug_c > 10:
                 break
-            cls.item_precision(item,
-                               project_id,
-                               abstract,
-                               fulltext,
-                               limit,
-                               threshold)
+            cls.item_metrics(item,
+                             project_id,
+                             abstract,
+                             fulltext,
+                             limit,
+                             threshold)
             debug_c = debug_c + 1
 
     @classmethod
-    def item_precision(cls,
-                       item: dict,
-                       project_id: str,
-                       abstract: bool = False,
-                       fulltext: bool = False,
-                       limit: int = None,
-                       threshold: int = None) -> None:
+    def item_metrics(cls,
+                     item: dict,
+                     project_id: str,
+                     abstract: bool = False,
+                     fulltext: bool = False,
+                     limit: int = None,
+                     threshold: int = None) -> None:
 
-        """ Calculate precision for an item.
+        """ Get metrics for an item.
 
         Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
 
@@ -588,44 +588,124 @@ class _Analysis:
         # construct the correct annif marker:
         marker = f"{project_id}-{abstract}-{fulltext}-{limit}-{threshold}"
 
-        # get the annif suggestions for the marker from the item:
-        annif_suggestions = item.get("annif").get(marker)
-        print(annif_suggestions)
-
[…]

### 2021-02-24 edoc/edoc_main.py
implement metrics

@@ -588,33 +588,11 @@ class _Analysis:
         # construct the correct annif marker:
         marker = f"{project_id}-{abstract}-{fulltext}-{limit}-{threshold}"
 
-        # get ID type from marker:
-        if project_id == "wikidata-en":
-            id_type = "qid"
-        else:
-            id_type = "yso id"
+        # extract suggestion IDs:
+        suggestions_ids = cls.extract_suggestions(item=item, marker=marker)
 
-        # get the annif suggestions for the marker from the item:
-        suggestions = item.get("annif").get(marker)
-
-        # get the IDs of the suggestions:
-        # TODO: add option for top n suggestions like so: suggestions[:n]. For this we need to calculate which n is best
-        suggestions_ids = []
-        for suggestion in suggestions:
-            uri = suggestion.get("uri")
-            if id_type == "qid":
-                suggestions_ids.append(uri.split("http://www.wikidata.org/entity/")[1])
-
-        # get the gold standard:
-        gold_standard = item.get("keywords enriched")
-
-        # get IDs from the gold standard:
-        gold_standard_ids = []
-        for keyword in gold_standard:
-            if keyword.get(id_type) == "":
-                continue
-            else:
-                gold_standard_ids.append(keyword.get(id_type))
+        # extract gold standard IDs:
+        gold_standard_ids = cls.extract_standard(item=item, marker=marker)
 
         print(suggestions_ids)
         print(gold_standard_ids)
@@ -635,12 +613,59 @@ class _Analysis:
         print("***")
 
     @classmethod
-    def extract_suggestions(cls):
-        pass
+    def get_id_type(cls, marker: str) -> str:
+        """ Get the ID type from the project ID.
+
+        :param marker: project_id-abstract-fulltext-limit-threshold
+        """
+
+        if marker.split("-")[0] == "wikidata":
+            return "qid"
+        else:
+            return "yso id"
 
     @classmethod
-    def extract_standard(cls):
-        pass
+    def extract_suggestions(cls,
+                            item: dict,
+                            marker: str):
+
+        """ Extract Annif suggestion IDs from item.
+
+        :param item: the Edoc item
+        :param marker: project_id-abstract-fulltext-limit-threshold
+        """
+
+        suggestions = item.get("annif").get(marker)
+
+        # TODO: add option for top n suggestions like so: suggestions[:n]. For this we need to calculate which n is best
+        suggestions_ids = []
+        for suggestion in suggestions:
[…]

### 2021-02-24 edoc/edoc_main.py
implement metrics

@@ -556,12 +556,12 @@ class _Analysis:
         for item in data:
             if debug_c > 10:
                 break
-            cls.item_metrics(item,
+            print(cls.item_metrics(item,
                              project_id,
                              abstract,
                              fulltext,
                              limit,
-                             threshold)
+                             threshold))
             debug_c = debug_c + 1
 
     @classmethod
@@ -571,7 +571,7 @@ class _Analysis:
                      abstract: bool = False,
                      fulltext: bool = False,
                      limit: int = None,
-                     threshold: int = None) -> None:
+                     threshold: int = None) -> Union[dict, None]:
 
         """ Get metrics for an item.
 
@@ -594,23 +594,14 @@ class _Analysis:
         # extract gold standard IDs:
         gold_standard_ids = cls.extract_standard(item=item, marker=marker)
 
-        print(suggestions_ids)
-        print(gold_standard_ids)
+        # calculate metrics:
+        if gold_standard_ids is None:
+            return None
+        precision = cls.get_precision(standard=gold_standard_ids, suggestions=suggestions_ids)
+        recall = cls.get_recall(standard=gold_standard_ids, suggestions=suggestions_ids)
+        f1_score = cls.get_f1(standard=gold_standard_ids, suggestions=suggestions_ids)
 
-        # calculate precision:
-        precision = cls.get_precision(standard=gold_standard_ids,
-                                      suggestions=suggestions_ids)
-        print(f"precision: {precision}")
-        # calculate recall:
-        recall = cls.get_recall(standard=gold_standard_ids,
-                                suggestions=suggestions_ids)
-        print(f"recall: {recall}")
-        # calculate recall:
-        f1_score = cls.get_f1(standard=gold_standard_ids,
-                              suggestions=suggestions_ids)
-        print(f"F1-score: {f1_score }")
-
-        print("***")
+        return {"precision": precision, "recall": recall, "f1": f1_score}
 
     @classmethod
     def get_id_type(cls, marker: str) -> str:
@@ -649,7 +640,7 @@ class _Analysis:
     @classmethod
     def extract_standard(cls,
                          item: dict,
-                         marker: str) -> list:
+                         marker: str) -> Union[list, None]:
         """ Extract gold standard IDs from item.
 
         :param item: the Edoc item
@@ -658,14 +649,21 @@ class _Analysis:
 
         id_type = cls.get_id_type(marker)
         gold_standard = item.get("keywords enriched")
-        gold_standard_ids = []
[…]

### 2021-02-25 text/draft.tex
implement metrics
spread of keywords

@@
 \texttt{/edoc/analysis} and the chi-square statistic can be calculated
-by calling \texttt{\_Analysis.chi\_square\_fit}.}
+by calling
+\texttt{\_Analysis.get\_\textasciitilde{}\textasciitilde{}\textasciitilde{}\textasciitilde{}chi\_square\_fit}.}
 \end{figure}
@@
 lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
-of all occurrences) and especially low for the YSO identifier (X of all
-keywords with Y of all occurrences). In both cases, the problem is due
-to the fact that Wikidata's mapping of MeSH respectively YSO is only
-partial. There can be two reasons for this state of affairs for a given
-entry: either there is no match between Wikidata and YSO or MeSH (after
-all, Wikidata is much larger than MeSH and YSO taken together), or there
-is a match but it has not yet been added to the mapping. In the latter
-case, at least with respect to YSO, there is a solution: Finto provides
-a REST-sytle API to access the YSO vocabulary directly (see
-https://api.finto.fi/). For each keyword in in the list of reference
+of all occurrences) and especially low for the YSO identifier (26.9\% of
+all keywords with 11\% of all occurrences). In both cases, the problem
+is due to the fact that Wikidata's mapping of MeSH respectively YSO is
+only partial. There can be two reasons for this state of affairs for a
+given entry: either there is no match between Wikidata and YSO or MeSH
+(after all, Wikidata is much larger than MeSH and YSO taken together),
+or there is a match but it has not yet been added to the mapping. In the
+latter case, at least with respect to YSO, there is a solution: Finto
+provides a REST-sytle API to access the YSO vocabulary directly (see
+https://api.finto.fi/). For each keyword in the list of reference
 keywords that lacks a YSO identifier, the Finto API is queried; if a
@@
 
+\hypertarget{discussion}{%
+\paragraph{Discussion}\label{discussion}}
+
 Let us now turn to the evaluation of the reconciliation: how many of the
@@
 disappointing as it might seem at first glance.
+
+!! How many author keywords per item? !! How many suggestions per item
+are correct?
 
@@
 
-\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{False negative} + \text{False positive}}\)
+\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}\)
 
@@
 standard}\label{annif-versus-native-gold-standard}}
+
+!! number of keywords per item; number of keywords with qid per item
+
+!! how to deal with items that have more than 10 keywords in standard??
 
@@
 
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
 

### 2021-02-25 edoc/edoc_main.py

@@ -481,8 +481,8 @@ class _Analysis:
     """ A collection of data analysis functions. """
 
     @classmethod
-    def chi_square_fit(cls,
-                       file_path: str) -> None:
+    def get_chi_square_fit(cls,
+                           file_path: str) -> None:
 
         """ Print chi square goodness of fit.
 
@@ -535,7 +535,8 @@ class _Analysis:
                 abstract: bool = False,
                 fulltext: bool = False,
                 limit: int = None,
-                threshold: int = None) -> None:
+                threshold: int = None,
+                n: int = 10) -> None:
 
         """ Get metrics for items in file.
 
@@ -547,6 +548,7 @@ class _Analysis:
         :param fulltext: toggle use fulltext for indexing, defaults to False
         :param limit: Annif-client limit, defaults to None
         :param threshold: Annif-client threshold, defaults to None
+        :param n: number of top IDs (by score) to be extracted per item, defaults to 10
         """
 
         data = _Utility.load_json(file_path)
@@ -556,12 +558,13 @@ class _Analysis:
         for item in data:
             if debug_c > 10:
                 break
-            print(cls.item_metrics(item,
-                             project_id,
-                             abstract,
-                             fulltext,
-                             limit,
-                             threshold))
+            print(cls.item_metrics(item=item,
+                                   project_id=project_id,
+                                   abstract=abstract,
+                                   fulltext=fulltext,
+                                   limit=limit,
+                                   threshold=threshold,
+                                   n=n))
             debug_c = debug_c + 1
 
     @classmethod
@@ -571,7 +574,8 @@ class _Analysis:
                      abstract: bool = False,
                      fulltext: bool = False,
                      limit: int = None,
-                     threshold: int = None) -> Union[dict, None]:
+                     threshold: int = None,
+                     n: int = 10) -> Union[dict, None]:
 
         """ Get metrics for an item.
 
@@ -583,13 +587,14 @@ class _Analysis:
         :param fulltext: toggle use fulltext for indexing, defaults to False
         :param limit: Annif-client limit, defaults to None
         :param threshold: Annif-client threshold, defaults to None
+        :param n: number of top IDs (by score) to be extracted, defaults to 10
         """
 
         # construct the correct annif marker:
         marker = f"{project_id}-{abstract}-{fulltext}-{limit}-{threshold}"
 
[…]

### 2021-02-25 text/draft.tex
spread of keywords

@@
 distribution of keywords is strongly skewed right
-(\(min = Q1 = M = Q3 = 1\) and \(max = 910\)). However, even though
+(\(min = Q1 = M = Q3 = 1\), \(max = 910\)). However, even though
 keywords with only one occurrence constitute over 75\% of the total
@@
 \end{figure}
+
+To analyse the spread of keywords in the sample data set, the keywords
+per item are counted. To do so, we call \texttt{\_Keywords.count\_all}
+on \texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
+output as \texttt{/analysis/keywords\_counted.json}:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
+\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ \_Keywords.count\_all(sample\_data\_set)}
+\NormalTok{\_Utility.save\_json(keywords\_counted, DIR }\OperatorTok{+} \StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+The median number of keywords for an item in the sample data set is 6
+with an \(IQR\) of 4 (\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\),
+\(max = 87\)). Of course, items in the sample data set with a number of
+keywords below the first and above the third quartile are highly suspect
+from a qualitative point of view: when it comes to subject indexing,
+some terms are required, but more is usually worse {[}!! source{]}.
+Items with too few or too many keywords will be discussed in more detail
+in section \protect\hyperlink{assessment}{section Assessment}
 
@@
 
-There were X automatic matches (call them ``suggestions''). A suggestion
-is correct if and only if the meaning of the keyword from
-\texttt{/keywords/keywords\_clean\_histogram.json} corresponds to the
-meaning of the suggested concept from Wikidata. Note that for homonymous
-or polysemous keywords, it is impossible to confirm a correct match
-without further context; those keywords therefore cannot be reconciled
-(but see \protect\hyperlink{construction}{section ``Construction''} for
-a possible solution). Unfortunately, random sampling showed that the
-overall quality of the reconciliation was not satisfactory, that is,
-there were too many incorrect suggestions. A two-pronged strategy was
-adopted to ameliorate the quality of the reconciliation.
+The reconciliation service API returns automatic matches (call them
+``suggestions''). A suggestion is correct if and only if the meaning of
+the keyword from \texttt{/keywords/keywords\_clean\_histogram.json}
+corresponds to the meaning of the suggested concept from Wikidata. Note
+that for homonymous or polysemous keywords, it is impossible to confirm
+a correct match without further context; those keywords therefore cannot
+be reconciled (but see \protect\hyperlink{construction}{section
+``Construction''} for a possible solution). Unfortunately, random
+sampling showed that the overall quality of the reconciliation was not
+satisfactory, that is, there were too many incorrect suggestions. A
+two-pronged strategy was adopted to ameliorate the quality of the
+reconciliation.
 
@@
 
+Finally, consider the distribution of the cleaned and reconciled
+keywords per item in the Edoc sample data set. The corresponding data is
+generated with \texttt{\_Keywords.count\_all} as described in
+\protect\hyperlink{analysis}{subsection Analysis} above and available as
+\texttt{/analysis/keywords\_counted.json}. Figure 5 shows that the
+median number of keywords from MeSH or YSO might be too low to be
+adequate. This problem can be amended by imposing further constraints on
+the sample data set and such a solution is discussed in section {[}!!
+section{]}.
+
+\begin{figure}
+\centering
+\includegraphics{images/keywords_counted.pdf}
+\caption{The distribution of keywords per item in the Edoc sample data
+set. The leftmost boxplot shows the distribution of cleaned keywords
+(\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\), \(max = 87\)); the
+other boxplots show the distribution of cleaned keywords with reconciled
+QID (\(min = 0\), \(Q1 = 2\), \(M = 4\), \(Q3 = 6\), \(max = 80\)), MeSH
+ID (\(min = Q1 = 0\), \(M = 2\), \(Q3 = 4\), \(max = 63\)), and YSO ID
+(\(min = Q1 = 0\), \(M = 1\), \(Q3 = 2\), \(max = 46\)). All four
+distributions are equally consistent, but there is a linear shrinkage of
+the center leaving MeSH and YSO with potentially too few descriptors to
+represent an adequate indexing.}
+\end{figure}
+
 \hypertarget{discussion}{%
@@
 disappointing as it might seem at first glance.
-
-!! How many author keywords per item? !! How many suggestions per item
-are correct?
 
@@
 Or put as question: what fraction of the subject terms suggested by
-Annif are also in the native gold standard?
+Annif are also in the native gold standard? The metric of precision is
+implemented by \texttt{\_Analysis.get\_precision}.
 
@@
 Put as question: what fraction of the subject terms in the gold standard
-were suggested by Annif?
+were suggested by Annif? The metric of recall is implemented by
+\texttt{\_Analysis.get\_recall}.
 
@@
 
-!! number of keywords per item; number of keywords with qid per item
-
 !! how to deal with items that have more than 10 keywords in standard??
+just look at data in IQR?
 
@@
 \section{Conclusion}\label{conclusion}}
+
+!! Clean up: rename
+\texttt{/indexed/indexed\_master\_mesh\_enriched.json} to
+\texttt{/indexed/master\_final.json} or something short.
 

### 2021-02-25 edoc/edoc_main.py

@@ -476,6 +476,38 @@ class _Keywords:
         except (IndexError, SyntaxError):
             return None
 
+    @classmethod
+    def count_all(cls,
+                  file_path: str,
+                  save_path: str) -> None:
+        """ Count all keywords and their respective IDs per item in file.
+
+        :param file_path: complete path to file including filename and extension
+        :param save_path: complete path to save folder including filename and extension
+        """
+
+        data = _Utility.load_json(file_path)
+        output = []
+
+        for item in data:
+            gold_standard = item.get("keywords enriched")
+            qid = 0
+            mesh = 0
+            yso = 0
+            try:
+                for keyword in gold_standard:
+                    if keyword.get("qid") != "":
+                        qid = qid + 1
+                    if keyword.get("mesh id") != "":
+                        mesh = mesh + 1
+                    if keyword.get("yso id") != "":
+                        yso = yso + 1
+                output.append({"gold standard": len(gold_standard), "qid": qid, "mesh id": mesh, "yso id": yso})
+            except AttributeError:
+                continue
+
+        _Utility.save_json(output, save_path)
+
 
 class _Analysis:
     """ A collection of data analysis functions. """
@@ -732,40 +764,10 @@ class _Analysis:
         except ZeroDivisionError:
             return 0
 
-    @classmethod
-    def count_all(cls,
-                  file_path: str,
-                  save_path: str) -> None:
-        """ Count all keywords and their respective IDs per item in file.
-
-        :param file_path: complete path to file including filename and extension
-        :param save_path: complete path to save folder including filename and extension
-        """
-
-        data = _Utility.load_json(file_path)
-        output = []
-
-        for item in data:
-            gold_standard = item.get("keywords enriched")
-            qid = 0
-            mesh = 0
-            yso = 0
-            try:
-                for keyword in gold_standard:
-                    if keyword.get("qid") != "":
-                        qid = qid + 1
-                    if keyword.get("mesh id") != "":
-                        mesh = mesh + 1
-                    if keyword.get("yso id") != "":
-                        yso = yso + 1
-                output.append({"gold standard": len(gold_standard), "qid": qid, "mesh id": mesh, "yso id": yso})
-            except AttributeError:
-                continue
-
-        _Utility.save_json(output, save_path)
 
 
[…]

### 2021-02-25 text/draft.tex
clean up

@@
 In order to determine how well the sample data set represents the raw
-Edoc data, a one-sample chi-square test was conducted on each selection
-data field (see Parke 2013, chap. 1). The results indicate that the
-sample data proportions of items are significantly different from the
-raw Edoc data per department (see Figure 1 for more details).
+Edoc data, a one-sample \(\chi^2\) goodnes of fit test was conducted on
+each selection data field (following Parke 2013, chap. 1). The results
+indicate that the sample data proportions of items are significantly
+different from the raw Edoc data per department (see Figure 1 for more
+details).
 
@@
 \caption{The sample data set (\(n\) = 4'111) is not representative of
-the raw Edoc data (\(N\) = 68'345) per department. Data field
-\texttt{abstract}: \(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data
-field \texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285,
-\(p < 0.001\); data field \texttt{keywords}: \(\chi^2 (df=9) =\)
-2'314.533, \(p < 0.001\). The data foundation is available at
-\texttt{/edoc/analysis} and the chi-square statistic can be calculated
-by calling
-\texttt{\_Analysis.get\_\textasciitilde{}\textasciitilde{}\textasciitilde{}\textasciitilde{}chi\_square\_fit}.}
+the raw Edoc data per department. Data field \texttt{abstract}:
+\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
+\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
+field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
+The data foundation is available at
+\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
+be calculated by calling \texttt{\_Analysis.get\_chi\_square\_fit} on
+the data foundation files.}
 \end{figure}
@@
 towards English journal publications in the sciences, medicine and
-economics from the 21st century (see Figure 2 for more details). The
+economics from the 21st century (again, this is shown by a one-sample
+\(\chi^2\) goodness of fit test, see Figure 2 for more details). The
 upshot of this analysis is that the humanities are underrepresented in
@@
 sciences, medicine and economics (data field \texttt{department}:
-\(\chi^2 (df=9) =\) 14'447.276\$, \(p < 0.001\)) from the 21st (data
-field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\))
-century as compared to the raw Edoc data (\(N\) = 68'345). The data
-foundation is available at \texttt{/edoc/analysis} and the chi-square
-statistic can be calculated by calling
-\texttt{\_Analysis.chi\_square\_fit}.}
+\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st (data field
+\texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\)) century as
+compared to the raw Edoc data. The data foundation is available at
+\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
+be calculated by calling \texttt{\_Analysis.get\_chi\_square\_fit} on
+the data foundation files.}
 \end{figure}
@@
 The median number of keywords for an item in the sample data set is 6
-with an \(IQR\) of 4 (\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\),
-\(max = 87\)). Of course, items in the sample data set with a number of
-keywords below the first and above the third quartile are highly suspect
-from a qualitative point of view: when it comes to subject indexing,
-some terms are required, but more is usually worse {[}!! source{]}.
-Items with too few or too many keywords will be discussed in more detail
-in section \protect\hyperlink{assessment}{section Assessment}
+with an IQR of 4 (min = 0, Q1 = 4, M = 6, Q3 = 8, max = 87). Of course,
+items in the sample data set with a number of keywords below the first
+and above the third quartile are highly suspect from a qualitative point
+of view: when it comes to subject indexing, some terms are required, but
+more is usually worse {[}!! source{]}. Items with too few or too many
+keywords will be discussed in more detail in section
+\protect\hyperlink{assessment}{section Assessment}
 
@@
 Let us now turn to the evaluation of the reconciliation: how many of the
-suggestions were correct? This question was answered via random
-sampling. The random sample (\(n=500\)) was created by calling
+suggestions were correct? This question was answered via random sampling
+(following Roth and Heidenreich 1993, 204--25). The random sample
+(\(n=500\)) was created by calling
 \texttt{\_Analysis.make\_random\_sample} on
@@
 
+\leavevmode\hypertarget{ref-Roth.1993}{}%
+Roth, Erwin, and Klaus Heidenreich. 1993. \emph{Sozialwissenschaftliche
+Methoden: Lehr- Und Handbuch f{ü}r Forschung Und Praxis}. 3., v{ö}llig
+{ü}berarbeitete und erweiterte Auflage. M{ü}nchen {[}etc.{]}: {R.
+Oldenbourg Verlag}.
+
 \leavevmode\hypertarget{ref-Stokhof.2011}{}%

### 2021-02-26 text/draft.tex
analysis f1 et al

@@
 sciences, medicine and economics (data field \texttt{department}:
-\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st (data field
-\texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\)) century as
-compared to the raw Edoc data. The data foundation is available at
-\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
-be calculated by calling \texttt{\_Analysis.get\_chi\_square\_fit} on
-the data foundation files.}
+\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st century
+(data field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493,
+\(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
+available at \texttt{/edoc/analysis/chi\_square...} and the
+\(\chi^2\)-statistic can be calculated by calling
+\texttt{\_Analysis.get\_chi\_square\_fit} on the data foundation files.}
 \end{figure}
@@
 \caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
-distribution of keywords is strongly skewed right
-(\(min = Q1 = M = Q3 = 1\), \(max = 910\)). However, even though
-keywords with only one occurrence constitute over 75\% of the total
-keywords, their occurrences constitute less than 35\% of the total
-occurrences. The most common keywords with 50 or more occurrences are
-extreme outliers but make up almost 20\% of the total occurrences.}
+distribution of keywords is strongly skewed right (min = Q1 = M = Q3 =
+1, max = 910). However, even though keywords with only one occurrence
+constitute over 75\% of the total keywords, their occurrences constitute
+less than 35\% of the total occurrences. The most common keywords with
+50 or more occurrences are extreme outliers but make up almost 20\% of
+the total occurrences.}
 \end{figure}
@@
 set. The leftmost boxplot shows the distribution of cleaned keywords
-(\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\), \(max = 87\)); the
-other boxplots show the distribution of cleaned keywords with reconciled
-QID (\(min = 0\), \(Q1 = 2\), \(M = 4\), \(Q3 = 6\), \(max = 80\)), MeSH
-ID (\(min = Q1 = 0\), \(M = 2\), \(Q3 = 4\), \(max = 63\)), and YSO ID
-(\(min = Q1 = 0\), \(M = 1\), \(Q3 = 2\), \(max = 46\)). All four
-distributions are equally consistent, but there is a linear shrinkage of
-the center leaving MeSH and YSO with potentially too few descriptors to
-represent an adequate indexing.}
+(min = 0, Q1 = 4, M = 6, Q3 = 8, max = 87); the other boxplots show the
+distribution of cleaned keywords with reconciled QID (min = 0, Q1 = 2, M
+= 4, Q3 = 6, max = 80), MeSH ID (min = Q1 = 0, M = 2, Q3 = 4, max = 63),
+and YSO ID respectively (min = Q1 = 0, M = 1, Q3 = 2, max = 46). All
+four distributions are similarly consistent, but there is a linear
+shrinkage of the center leaving MeSH and YSO with potentially too few
+descriptors to represent an adequate indexing.}
 \end{figure}
@@
 \(\text{F1} = \displaystyle 2 * \frac{\text{Precision} * \text{Recall}}{\text{Precision} + \text{Recall}}\)
+
+The metric of F1-score is implemented by \texttt{\_Analysis\_get\_f1}
 

### 2021-02-26 edoc/edoc_main.py

@@ -9,7 +9,7 @@ import urllib3
 import xmltodict
 import ast
 import scipy.stats
-from sklearn.metrics import recall_score, precision_score
+import numpy
 
 
 DIR = os.path.dirname(__file__)
@@ -513,8 +513,8 @@ class _Analysis:
     """ A collection of data analysis functions. """
 
     @classmethod
-    def get_chi_square_fit(cls,
-                           file_path: str) -> None:
+    def print_chi_square_fit(cls,
+                             file_path: str) -> None:
 
         """ Print chi square goodness of fit.
 
@@ -561,16 +561,18 @@ class _Analysis:
         _Utility.save_json(sample, save_path)
 
     @classmethod
-    def metrics(cls,
-                file_path: str,
-                project_id: str,
-                abstract: bool = False,
-                fulltext: bool = False,
-                limit: int = None,
-                threshold: int = None,
-                n: int = 10) -> None:
+    def make_metrics(cls,
+                     file_path: str,
+                     project_id: str,
+                     abstract: bool = False,
+                     fulltext: bool = False,
+                     limit: int = None,
+                     threshold: int = None,
+                     n: int = 10) -> None:
 
         """ Get metrics for items in file.
+
+        The output is saved as /assessment/metrics_{marker}.
 
         Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
 
@@ -585,29 +587,30 @@ class _Analysis:
 
         data = _Utility.load_json(file_path)
 
-        debug_c = 0
-
+        metrics = []
         for item in data:
-            if debug_c > 10:
-                break
-            print(cls.item_metrics(item=item,
-                                   project_id=project_id,
-                                   abstract=abstract,
-                                   fulltext=fulltext,
-                                   limit=limit,
-                                   threshold=threshold,
-                                   n=n))
-            debug_c = debug_c + 1
+            metrics.append(cls.get_item_metrics(item=item,
+                                                project_id=project_id,
+                                                abstract=abstract,
+                                                fulltext=fulltext,
+                                                limit=limit,
+                                                threshold=threshold,
+                                                n=n))
+
+        # construct the correct annif marker:
[…]

### 2021-02-26 edoc/edoc_main.py
metrics

@@ -5,6 +5,7 @@ import csv
 from datetime import datetime
 from annif_client import AnnifClient
 import os.path
+from os import listdir
 import urllib3
 import xmltodict
 import ast
@@ -477,9 +478,9 @@ class _Keywords:
             return None
 
     @classmethod
-    def count_all(cls,
-                  file_path: str,
-                  save_path: str) -> None:
+    def make_count(cls,
+                   file_path: str,
+                   save_path: str) -> None:
         """ Count all keywords and their respective IDs per item in file.
 
         :param file_path: complete path to file including filename and extension
@@ -561,6 +562,29 @@ class _Analysis:
         _Utility.save_json(sample, save_path)
 
     @classmethod
+    def super_make_metrics(cls,
+                           file_path: str):
+        """ Make metrics for all combinations of Annif projects and parameters in enriched Edoc file.
+
+        Output files are saved in /metrics.
+
+        :param file_path: complete path to file including filename and extension
+        """
+
+        project_ids = ["yso-en", "yso-maui-en", "yso-bonsai-en", "yso-fasttext-en", "wikidata-en"]
+
+        # only title:
+        for project_id in project_ids:
+            cls.make_metrics(file_path=file_path,
+                             project_id=project_id)
+
+        # title + abstract:
+        for project_id in project_ids:
+            cls.make_metrics(file_path=file_path,
+                             project_id=project_id,
+                             abstract=True)
+
+    @classmethod
     def make_metrics(cls,
                      file_path: str,
                      project_id: str,
@@ -572,7 +596,7 @@ class _Analysis:
 
         """ Get metrics for items in file.
 
-        The output is saved as /assessment/metrics_{marker}.
+        The output is saved as /metrics/metrics_{marker}.json.
 
         Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
 
@@ -600,7 +624,7 @@ class _Analysis:
         # construct the correct annif marker:
         marker = f"{project_id}-{abstract}-{fulltext}-{limit}-{threshold}"
 
-        _Utility.save_json(metrics, DIR + f"/assessment/metrics_{marker}")
+        _Utility.save_json(metrics, DIR + f"/metrics/metrics_{marker}.json")
 
     @classmethod
     def get_item_metrics(cls,
[…]

### 2021-02-26 edoc/edoc_main.py
metrics

@@ -573,16 +573,27 @@ class _Analysis:
 
         project_ids = ["yso-en", "yso-maui-en", "yso-bonsai-en", "yso-fasttext-en", "wikidata-en"]
 
-        # only title:
-        for project_id in project_ids:
-            cls.make_metrics(file_path=file_path,
-                             project_id=project_id)
-
-        # title + abstract:
-        for project_id in project_ids:
-            cls.make_metrics(file_path=file_path,
-                             project_id=project_id,
-                             abstract=True)
+        n = 1
+        while n < 11:
+            for project_id in project_ids:
+                print(f"Working on {project_id}...")
+                # title:
+                cls.make_metrics(file_path=file_path,
+                                 project_id=project_id)
+                # title + abstract:
+                cls.make_metrics(file_path=file_path,
+                                 project_id=project_id,
+                                 abstract=True)
+                # title + limit:
+                cls.make_metrics(file_path=file_path,
+                                 project_id=project_id,
+                                 n=n)
+                # title + limit:
+                cls.make_metrics(file_path=file_path,
+                                 project_id=project_id,
+                                 abstract=True,
+                                 n=n)
+            n = n + 1
 
     @classmethod
     def make_metrics(cls,
@@ -622,7 +633,7 @@ class _Analysis:
                                                 n=n))
 
         # construct the correct annif marker:
-        marker = f"{project_id}-{abstract}-{fulltext}-{limit}-{threshold}"
+        marker = f"{project_id}-{abstract}-{fulltext}-{n}-{threshold}"
 
         _Utility.save_json(metrics, DIR + f"/metrics/metrics_{marker}.json")
 
@@ -811,7 +822,6 @@ class _Analysis:
 
         _Utility.save_json(stats, DIR + "/analysis/metrics_stats.json")
 
-
     @classmethod
     def get_stats(cls,
                   file_path: str) -> dict:
@@ -854,7 +864,6 @@ class _Analysis:
                 "maximum": numpy.quantile(data, 1),
                 "iqr": numpy.quantile(data, 0.75) - numpy.quantile(data, 0.25),
                 "mean": numpy.mean(data)}
-
 
 
 _Analysis.super_make_stats()

### 2021-02-27 text/draft.tex
analysis

@@
 \texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
-be calculated by calling \texttt{\_Analysis.get\_chi\_square\_fit} on
+be calculated by calling \texttt{\_Analysis.print\_chi\_square\_fit} on
 the data foundation files.}
@@
 \(\chi^2\)-statistic can be calculated by calling
-\texttt{\_Analysis.get\_chi\_square\_fit} on the data foundation files.}
+\texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
+files.}
 \end{figure}
@@
 To analyse the spread of keywords in the sample data set, the keywords
-per item are counted. To do so, we call \texttt{\_Keywords.count\_all}
+per item are counted. To do so, we call \texttt{\_Keywords.make\_count}
 on \texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
@@
 \NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
-\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ \_Keywords.count\_all(sample\_data\_set)}
+\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ \_Keywords.make\_count(sample\_data\_set)}
 \NormalTok{\_Utility.save\_json(keywords\_counted, DIR }\OperatorTok{+} \StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
@@
 keywords per item in the Edoc sample data set. The corresponding data is
-generated with \texttt{\_Keywords.count\_all} as described in
+generated with \texttt{\_Keywords.make\_count} as described in
 \protect\hyperlink{analysis}{subsection Analysis} above and available as
@@
 Let us briefly look at the definitions and motivations of the chosen
-metrics. Recall that a suggestion of a subject term is correct if and
+metrics. Remember that a suggestion of a subject term is correct if and
 only if the subject term is in the native gold standard. The possible
@@
 
-\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False positive}}\)
+\begin{center} 
+$\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False positive}}$
+\end{center}
 
@@
 
-\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}\)
+\begin{center} 
+$\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}$
+\end{center}
 
@@
 
-\(\text{F1} = \displaystyle 2 * \frac{\text{Precision} * \text{Recall}}{\text{Precision} + \text{Recall}}\)
+\begin{center} 
+$\text{F1} = \displaystyle 2 * \frac{\text{Precision} * \text{Recall}}{\text{Precision} + \text{Recall}}$
+\end{center}
 
-The metric of F1-score is implemented by \texttt{\_Analysis\_get\_f1}
+The metric of F1-score is implemented by \texttt{\_Analysis\_get\_f1}.
 
@@
 
-!! how to deal with items that have more than 10 keywords in standard??
-just look at data in IQR?
+In this section, I will assess the perfomance of Annif versus the native
+gold standard.
 
-\hypertarget{yso}{%
-\paragraph{YSO}\label{yso}}
+\hypertarget{creating-the-data-foundation}{%
+\paragraph{Creating the data
+foundation}\label{creating-the-data-foundation}}
 
-\hypertarget{wikidata}{%
-\paragraph{Wikidata}\label{wikidata}}
+I will now describe how the data foundation for the assessment was
+created. There are three parameters that need to be distinguished(see
+\protect\hyperlink{annif}{section ``Annif''}):
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  The Annif project (algorithm plus vocabulary) responsible for the
+  indexing of the sample data set. As per the Annif REST API, these are
+  \texttt{yso-en}, \texttt{yso-maui-en}, \texttt{yso-bonsai-en},
+  \texttt{yso-fasttext-en}, and \texttt{wikidata-en}.
+\item
+  The text base per item, namely title versus title and abstract.
+\item
+  The maximum number of suggestions per item. Since we required 10
+  suggestions per item, we can choose between 1-10 suggestions.
+\end{enumerate}
+
+Combining these parameters, we really have 100 Annif configurations
+whose perfomance we want to compare and assess: Annif project \(*\) text
+base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
+
+For each configuration, the F1-score was computed for every item in the
+sample data set. To do so, we call
+\texttt{\_Analysis.super\_make\_metrics} on
+\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
+are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
+specifies the Annif configuration:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{\_Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+Note that if an item had an empty native gold standard, no score was
+computed; this is the case exactly if none of the cleaned keywords had
+been matched to Wikidata or YSO respectively. Configurations with a
+Wikidata vocabulary had a scoring coverage of 94.38\% of the items in
+the sample data set as compared to only 62.84\% for configurations with
+a YSO vocabulary.
+
+Next, in order to be able to compare the F1-scores of the 100
+configurations, a statistic (quartiles, IQR, mean) was computed for each
+configuration by calling \texttt{\_Analysis.super\_make\_stats}, saving
+the output as \texttt{/analysis/metrics\_stats.json}:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{\_Analysis.super\_make\_stats()}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{general-results}{%
+\paragraph{General results}\label{general-results}}
+
+we can then discuss whether the best performance is actually useful;
+perhaps do this by comparing absolute scores with other assessments. if
+results are much lower it is to be suspected that the native gold
+standard is not very good (i.e., that the measure we use to judge annif
+performance is inadequte =\textgreater{} motivation for foreign
+standard)
+
+construct all metrics: \_Analysis.super\_make\_metrics(file\_path=DIR +
+``/indexed/indexed\_master\_mesh\_enriched.json'')
+
+construcht all stats for metrics: \_Analysis.super\_make\_stats()
+
+\hypertarget{yso-configurations}{%
+\paragraph{YSO configurations}\label{yso-configurations}}
+
+\hypertarget{wikidata-configurations}{%
+\paragraph{Wikidata configurations}\label{wikidata-configurations}}
 
@@
 standard}\label{annif-versus-foreign-gold-standard}}
+
+!! but to do this we would first have to map the annif suggested terms
+to mesh\ldots! yes.
 

### 2021-03-03 edoc/edoc_main.py
sklearn metrics test

@@ -865,6 +865,47 @@ class _Analysis:
                 "iqr": numpy.quantile(data, 0.75) - numpy.quantile(data, 0.25),
                 "mean": numpy.mean(data)}
 
+    @classmethod
+    def get_sklearn_metrics(cls,
+                            standard: list,
+                            suggestions: list) -> dict:
+        """ Bla.
+
+        :param standard:
+        :param suggestions:
+        """
+        true_positive = 0
+        for suggestion in suggestions:
+            if suggestion in standard:
+                true_positive = true_positive + 1
+
+        y_true = []
+        for k in range(0, len(standard)):
+            y_true.append(1)
+
+        y_pred = []
+        for k in range(0, true_positive):
+            y_pred.append(1)
+        for k in range(0, len(standard) - true_positive):
+            y_pred.append(0)
+
+        from sklearn.metrics import f1_score
+
+        return {"F1-macro": f1_score(y_true, y_pred, average="macro"),
+                "F1-micro": f1_score(y_true, y_pred, average="micro"),
+                "F1-weighted": f1_score(y_true, y_pred, average="weighted")}
+
+exit()
+from sklearn.metrics import precision_score
+y_true = [1,1,1]
+y_pred = [1,0,0]
+print(precision_score(y_true, y_pred, average='macro'))
+print(precision_score(y_true, y_pred, average='micro'))
+print(precision_score(y_true, y_pred, average='weighted'))
+
+
+
+exit()
 
 _Analysis.super_make_stats()
 exit()

### 2021-03-03 edoc/edoc_main.py
sklearn metrics

@@ -5,12 +5,11 @@ import csv
 from datetime import datetime
 from annif_client import AnnifClient
 import os.path
-from os import listdir
 import urllib3
 import xmltodict
 import ast
 import scipy.stats
-import numpy
+from sklearn.metrics import f1_score, recall_score, precision_score
 
 
 DIR = os.path.dirname(__file__)
@@ -605,11 +604,15 @@ class _Analysis:
                      threshold: int = None,
                      n: int = 10) -> None:
 
-        """ Get metrics for items in file.
+        """ Make Sklearn metrics F1, recall, precision for file.
 
         The output is saved as /metrics/metrics_{marker}.json.
 
         Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
+
+        https://scikit-learn.org/stable/modules/generated/sklearn.metrics.f1_score.html
+        https://scikit-learn.org/stable/modules/generated/sklearn.metrics.recall_score.html
+        https://scikit-learn.org/stable/modules/generated/sklearn.metrics.precision_score.html
 
         :param file_path: complete path to file including filename and extension
         :param project_id: Annif-client project ID
@@ -622,32 +625,53 @@ class _Analysis:
 
         data = _Utility.load_json(file_path)
 
-        metrics = []
+        # construct y_true (=standard) and y_pred (=suggestions) from data:
+        standard = []
+        suggestions = []
         for item in data:
-            metrics.append(cls.get_item_metrics(item=item,
-                                                project_id=project_id,
-                                                abstract=abstract,
-                                                fulltext=fulltext,
-                                                limit=limit,
-                                                threshold=threshold,
-                                                n=n))
+            sklearn_array = cls.get_sklearn_array(item=item,
+                                                  project_id=project_id,
+                                                  abstract=abstract,
+                                                  fulltext=fulltext,
+                                                  limit=limit,
+                                                  threshold=threshold,
+                                                  n=n)
+            if sklearn_array is None:
+                continue
+            standard = standard + sklearn_array.get("y_true")
+            suggestions = suggestions + sklearn_array.get("y_pred")
 
         # construct the correct annif marker:
[…]

### 2021-03-03 text/draft.tex
clean up
sklearn metrics test

@@
 Or put as question: what fraction of the subject terms suggested by
-Annif are also in the native gold standard? The metric of precision is
-implemented by \texttt{\_Analysis.get\_precision}.
+Annif are also in the native gold standard?
 
@@
 \begin{center} 
-$\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}$
+$\text{Recall} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False negative}}$
 \end{center}
@@
 Put as question: what fraction of the subject terms in the gold standard
-were suggested by Annif? The metric of recall is implemented by
-\texttt{\_Analysis.get\_recall}.
+were suggested by Annif?
 
@@
 
-The metric of F1-score is implemented by \texttt{\_Analysis\_get\_f1}.
+\hypertarget{implementation-1}{%
+\paragraph{Implementation}\label{implementation-1}}
+
+The above scoring metrics were implemented using the scikit-learn
+machine learning library (Pedregosa et al. 2011). It is important to
+note that each metric comes in three different flavors dubbed ``macro,''
+``micro,'' and ``weighted'' respectively. In the macro flavor, the
+metric represents simply the mean per class (i.e., correct or incorrect
+suggestion). The weighted metric is the macro metric but each class is
+weighted by its true positives. By contrast, a metric with the micro
+flavor is computed globally over all true positives and false positives
+respectively negatives.
 
@@
 I will now describe how the data foundation for the assessment was
-created. There are three parameters that need to be distinguished(see
+created. There are three parameters that need to be distinguished (see
 \protect\hyperlink{annif}{section ``Annif''}):
@@
 
-For each configuration, the F1-score was computed for every item in the
-sample data set. To do so, we call
-\texttt{\_Analysis.super\_make\_metrics} on
+For each configuration, the F1-score (macro, micro and weighted) was
+computed. To do so, we call \texttt{\_Analysis.super\_make\_metrics} on
 \texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
 are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
-specifies the Annif configuration:
+specifies the Annif configuration; a single file for analysis is saved
+as \texttt{/analysis/metrics.json}:
 
@@
 a YSO vocabulary.
-
-Next, in order to be able to compare the F1-scores of the 100
-configurations, a statistic (quartiles, IQR, mean) was computed for each
-configuration by calling \texttt{\_Analysis.super\_make\_stats}, saving
-the output as \texttt{/analysis/metrics\_stats.json}:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{\_Analysis.super\_make\_stats()}
-\end{Highlighting}
-\end{Shaded}
 
@@
 
+\leavevmode\hypertarget{ref-Pedregosa.2011}{}%
+Pedregosa, F., G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O.
+Grisel, M. Blondel, et al. 2011. {``Scikit-Learn: Machine Learning in
+Python.''} \emph{Journal of Machine Learning Research}, no. 12:
+2825--30.
+\url{https://www.jmlr.org/papers/volume12/pedregosa11a/pedregosa11a.pdf?source=post_page---------------------------}.
+
 \leavevmode\hypertarget{ref-Roth.1993}{}%
@@
 Methoden: Lehr- Und Handbuch f{ü}r Forschung Und Praxis}. 3., v{ö}llig
-{ü}berarbeitete und erweiterte Auflage. M{ü}nchen {[}etc.{]}: {R.
-Oldenbourg Verlag}.
+{ü}berarbeitete und erweiterte Auflage. M{ü}nchen: {R. Oldenbourg
+Verlag}.
 

### 2021-03-03 edoc/edoc_main.py

@@ -565,7 +565,7 @@ class _Analysis:
                            file_path: str):
         """ Make metrics for all combinations of Annif projects and parameters in enriched Edoc file.
 
-        Output files are saved in /metrics.
+        Output files are saved in /metrics/. Joint results are saved in /analysis/metrics.json.
 
         :param file_path: complete path to file including filename and extension
         """
@@ -593,6 +593,8 @@ class _Analysis:
                                  abstract=True,
                                  n=n)
             n = n + 1
+
+        cls.super_make_stats()
 
     @classmethod
     def make_metrics(cls,
@@ -646,6 +648,10 @@ class _Analysis:
 
         # compute the metrics:
         metrics = {
+            "F1-binary": f1_score(standard, suggestions, average='binary'),
+            "Precision-binary": precision_score(standard, suggestions, average='binary', zero_division=0),
+            "Recall-binary": recall_score(standard, suggestions, average='binary', zero_division=0),
+
             "F1-macro": f1_score(standard, suggestions, average='macro'),
             "Precision-macro": precision_score(standard, suggestions, average='macro', zero_division=0),
             "Recall-macro": recall_score(standard, suggestions, average='macro', zero_division=0),
@@ -793,7 +799,7 @@ class _Analysis:
     def super_make_stats(cls) -> None:
         """ Make metrics for files in /metrics.
 
-        Output is saved as /analysis/metrics_stats.json.
+        Output is saved as /analysis/metrics.json.
         """
 
         stats = []
@@ -806,9 +812,10 @@ class _Analysis:
 
             stats.append({"stat": metrics})
 
-        _Utility.save_json(stats, DIR + "/analysis/metrics_stats.json")
+        _Utility.save_json(stats, DIR + "/analysis/metrics.json")
 
 _Analysis.super_make_stats()
+
 
 exit()
 

### 2021-03-04 text/draft.tex
metrics per department

@@
 
-The metrics used for the assessment are precision, recall and F1 score.
+The metrics used for the assessment are precision, recall and F1-score.
 Precision and recall are standard metrics for indexing quality (e.g.,
@@
 The above scoring metrics were implemented using the scikit-learn
-machine learning library (Pedregosa et al. 2011). It is important to
-note that each metric comes in three different flavors dubbed ``macro,''
-``micro,'' and ``weighted'' respectively. In the macro flavor, the
-metric represents simply the mean per class (i.e., correct or incorrect
-suggestion). The weighted metric is the macro metric but each class is
-weighted by its true positives. By contrast, a metric with the micro
-flavor is computed globally over all true positives and false positives
-respectively negatives.
+machine learning library (Pedregosa et al. 2011). For a given Annif
+configuration
+(\protect\hyperlink{annif-versus-native-gold-standard}{section ``Annif
+versus native gold standard''})\ldots{} {[}perhaps explain how it is
+done, important to mention transformation of multilabel to binary{]}.
+Note that while
 
@@
 
-In this section, I will assess the perfomance of Annif versus the native
-gold standard.
+In this section, I will assess the performance of Annif versus the
+native gold standard.
 
@@
 Combining these parameters, we really have 100 Annif configurations
-whose perfomance we want to compare and assess: Annif project \(*\) text
-base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
+whose performance we want to compare and assess: Annif project \(*\)
+text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
 
-For each configuration, the F1-score (macro, micro and weighted) was
-computed. To do so, we call \texttt{\_Analysis.super\_make\_metrics} on
+For each configuration, the F1-score was then computed. It is important
+to note that each metric comes in three different flavors dubbed
+``macro,'' ``micro,'' and ``weighted'' respectively (see Sokolova and
+Lapalme 2009). In the macro flavor, the metric represents simply the
+mean per class (i.e., correct or incorrect suggestion). The weighted
+metric is the macro metric but each class is weighted by its true
+positives. By contrast, a metric with the micro flavor is computed
+globally over all true positives and false positives respectively
+negatives. So the ``macro'' and ``weighted'' flavors are useful for
+assessing the performance of a configuration with respect to individual
+cases of assigning subject terms whereas the ``micro'' flavor is most
+suitable to assess the overall performance of a configuration with
+respect to assigning subject terms.
+
+To compute the F1-score, we call
+\texttt{\_Analysis.super\_make\_metrics} on
 \texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
@@
 2825--30.
-\url{https://www.jmlr.org/papers/volume12/pedregosa11a/pedregosa11a.pdf?source=post_page---------------------------}.
+\url{https://www.jmlr.org/papers/volume12/pedregosa11a/pedregosa11a.pdf}.
 
@@
 Verlag}.
+
+\leavevmode\hypertarget{ref-Sokolova.2009}{}%
+Sokolova, Marina, and Guy Lapalme. 2009. {``A Systematic Analysis of
+Performance Measures for Classification Tasks.''} \emph{Information
+Processing {\&} Management} 45 (4): 427--37.
+\url{https://doi.org/10.1016/j.ipm.2009.03.002}.
 

### 2021-03-04 edoc/edoc_main.py

@@ -328,6 +328,21 @@ class _Data:
 
         _Data.enrich_with_annif(file_path=file_path, save_path=save_path, project_ids=project_ids, abstract=abstract)
 
+    @classmethod
+    def get_departments(cls) -> List[str]:
+        """ Get all Edoc departments. """
+
+        return ["Associated_Institutions",
+                "Central_University_Services",
+                "Faculty_of_Business_and_Economics",
+                "Faculty_of_Humanities",
+                "Faculty_of_Law",
+                "Faculty_of_Medicine",
+                "Faculty_of_Psychology",
+                "Faculty_of_Science",
+                "Faculty_of_Theology",
+                "Interdisciplinary_Institutions"]
+
 
 class _Keywords:
     """ A collection of functions for manipulating edoc author keywords. """
@@ -562,12 +577,14 @@ class _Analysis:
 
     @classmethod
     def super_make_metrics(cls,
-                           file_path: str):
+                           file_path: str,
+                           department: str = None):
         """ Make metrics for all combinations of Annif projects and parameters in enriched Edoc file.
 
         Output files are saved in /metrics/. Joint results are saved in /analysis/metrics.json.
 
         :param file_path: complete path to file including filename and extension
+        :param department: restrict to items from department
         """
 
         project_ids = ["yso-en", "yso-maui-en", "yso-bonsai-en", "yso-fasttext-en", "wikidata-en"]
@@ -575,23 +592,26 @@ class _Analysis:
         n = 1
         while n < 11:
             for project_id in project_ids:
-                print(f"Working on {project_id}...")
                 # title:
                 cls.make_metrics(file_path=file_path,
-                                 project_id=project_id)
+                                 project_id=project_id,
+                                 department=department)
                 # title + abstract:
                 cls.make_metrics(file_path=file_path,
                                  project_id=project_id,
-                                 abstract=True)
+                                 abstract=True,
+                                 department=department)
                 # title + limit:
                 cls.make_metrics(file_path=file_path,
                                  project_id=project_id,
-                                 n=n)
+                                 n=n,
+                                 department=department)
                 # title + limit:
                 cls.make_metrics(file_path=file_path,
                                  project_id=project_id,
                                  abstract=True,
-                                 n=n)
[…]

### 2021-03-04 edoc/edoc_main.py
metrics per department

@@ -694,12 +694,48 @@ class _Analysis:
             "Sample size": len(standard)
         }
 
+        metrics.update(cls.count_confusion(standard, suggestions))
+
         if department is None:
             _Utility.save_json(metrics, DIR + f"/metrics/metrics_{marker}.json")
         else:
             _Utility.save_json(metrics, DIR + f"/metrics/metrics_{department}_{marker}.json")
 
         print("done.")
+
+    @classmethod
+    def count_confusion(cls,
+                        standard: list,
+                        suggestions: list):
+        """ Count the values in the confusion matrix for standard and suggestions.
+
+        :param standard: the standard
+        :param suggestions: the suggestions
+        """
+
+        true_positive = 0
+        true_negative = 0
+        false_positive = 0
+        false_negative = 0
+
+        c = 0
+        while c < len(standard):
+            if standard[c] == suggestions[c]:
+                true_positive += 1
+            elif standard[c] > suggestions[c]:
+                false_negative += 1
+            elif standard[c] < suggestions[c]:
+                false_positive += 1
+            else:
+                true_negative += 1
+            c += 1
+
+        return {
+            "TP": true_positive,
+            "TN": true_negative,
+            "FP": false_positive,
+            "FN": false_negative
+        }
 
     @classmethod
     def get_sklearn_array(cls,
@@ -848,9 +884,6 @@ class _Analysis:
 
         _Utility.save_json(stats, DIR + "/analysis/metrics.json")
 
-_Analysis.super_make_metrics()
-
-exit()
 
 for dept in _Data.get_departments():
     _Analysis.super_make_metrics(file_path=DIR + "/indexed/indexed_master_mesh_enriched.json", department=dept)

### 2021-03-05 text/draft.tex
metrics per department

@@
 assessing the performance of a configuration with respect to individual
-cases of assigning subject terms whereas the ``micro'' flavor is most
-suitable to assess the overall performance of a configuration with
-respect to assigning subject terms.
+cases of assigning subject terms (call them ``samples'') whereas the
+``micro'' flavor is most suitable to assess the overall performance of a
+configuration with respect to assigning subject terms.
 
@@
 \texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
-are saved as \texttt{/metrics/metrics\_\{marker\}} where \texttt{marker}
-specifies the Annif configuration; a single file for analysis is saved
-as \texttt{/analysis/metrics.json}:
+are saved as \texttt{/metrics/metrics\_\{marker\}.json} where
+\texttt{marker} specifies the Annif configuration; a single file for
+analysis is saved as \texttt{/analysis/metrics.json}:
 
@@
 
-Note that if an item had an empty native gold standard, no score was
-computed; this is the case exactly if none of the cleaned keywords had
-been matched to Wikidata or YSO respectively. Configurations with a
-Wikidata vocabulary had a scoring coverage of 94.38\% of the items in
-the sample data set as compared to only 62.84\% for configurations with
-a YSO vocabulary.
+Note that the data foundation includes additional information, namely
+the sample size and the raw values for the confusion matrix. The sample
+size is a histogram of each instance in which a value in the confusion
+matrix was computed, that is, each case in which either Annif or the
+native gold standard assigned a subject term. Finally, note that if an
+item in the Edoc sample data set had an empty native gold standard, no
+score was computed; this is the case exactly if none of the cleaned
+keywords had been matched to Wikidata or YSO respectively.
+Configurations with a Wikidata vocabulary had a scoring coverage of
+94.38\% of the items in the sample data set as compared to only 62.84\%
+for configurations with a YSO vocabulary.
 
@@
 construcht all stats for metrics: \_Analysis.super\_make\_stats()
+
+\hypertarget{departments}{%
+\paragraph{Departments}\label{departments}}
+
+I had noted in section X as caveat that the performance of Annif might
+vary according to department due to systematic biases in constructing
+the Edoc sample data set. It might therefore be illuminating to assess
+the performance of the various Annif configurations per department.
+Since the Edoc \texttt{department} data field is mandatory, the sample
+data set is partioned into blocks of departments by default. We can thus
+create a data foundation for each such block by calling
+\texttt{\_Analysis.super\_make\_metrics} with a departmental parameter:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ \_Data.get\_departments():}
+\NormalTok{    \_Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{, deparment}\OperatorTok{=}\NormalTok{dept)}
+\end{Highlighting}
+\end{Shaded}
+
+This yields 1000 files in
+\texttt{/metrics/metrics\_\{department\}\_\{marker\}.json} (100
+configurations \(*\) 10 departments) where \texttt{department} specifies
+the department according to the Edoc convention.
+
+\begin{itemize}
+\tightlist
+\item
+  best config for department
+\end{itemize}
 

### 2021-03-05 edoc/edoc_main.py

@@ -885,6 +885,8 @@ class _Analysis:
         _Utility.save_json(stats, DIR + "/analysis/metrics.json")
 
 
+exit()
+
 for dept in _Data.get_departments():
     _Analysis.super_make_metrics(file_path=DIR + "/indexed/indexed_master_mesh_enriched.json", department=dept)
 

### 2021-03-05 text/draft.tex
metrics general

@@
 text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
+Each configuration has a unique ID (called ``marker'' in what follows)
+constructed by the convention:
+\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}}
+where \texttt{project\_id} is the Annif project, \texttt{abstract} and
+\texttt{fulltext} are boolean variables, \texttt{n} is the maximum
+number of suggestions per item, and \texttt{threshold} is a variable for
+a threshold Annif score.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{images/metrics_f1_top20.pdf}
+\caption{Top 20 Annif configurations by F1-score.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{images/metrics_all_n.pdf}
+\caption{Distribution of weighted F1-scores per maximum number of
+suggestions 0 \textless{} n \textless11.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{images/metrics_all_project+abstract.pdf}
+\caption{Distribution of weighted F1-scores per class of algorithm
+(left) and per class of text basis (right).}
+\end{figure}
+
 we can then discuss whether the best performance is actually useful;
@@
 
-\begin{itemize}
-\tightlist
-\item
-  best config for department
-\end{itemize}
+Let us now look at the results. For each department, we are interested
+in the highest weighted F1-score and the corresponding configuration as
+summarized in Figure X.
+
+\begin{figure}
+\centering
+\includegraphics{images/metrics_dept_summary.pdf}
+\caption{Best performing Annif configuration by F1-score weighted per
+department.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{images/metrics_dept_distribution.pdf}
+\caption{Distribution of F1-scores weighted for all Annif configurations
+per department.}
+\end{figure}
 

### 2021-03-05 text/draft.tex
metrics general

@@
 
+In this section I will discuss the general results of assessing the
+performance of the 100 Annif configurations versus the native gold
+standard with respect to the Edoc sample data set.
+
+Let us first consider overall performance. Here the most remarkable
+result is that Wikidata configurations outperformed YSO configurations
+(see Figure X). However, the explanation of this effect is not evident.
+The two main explanatory hypotheses are 1. that the suggestions by the
+Wikidata configurations are more salient, or 2. that the native gold
+standard is biased towards Wikidata due to its higher coverage of QIDs
+as compared to YSO IDs. By contrast, the Wikidata configurations are
+more productive than the YSO configurations, and the reason for this
+effect is the higher coverage of QIDs as compared to YSO IDs (see Figure
+Y). By ``productivity'' I mean that the absolute number of assigned
+subject terms. So Wikidata configurations are not only qualitatively but
+also quantitatively superior to YSO configurations.
+
 \begin{figure}
 \centering
+\includegraphics{images/metrics_all_project+abstract.pdf}
+\caption{Distribution of weighted F1-scores per class of algorithm
+(left) and per class of text basis (right). Figure X.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{images/metrics_all_productivity.pdf}
+\caption{The distribution of cumulative sample size per class of Annif
+configuration. Figure Y}
+\end{figure}
+
+Furthermore, the four YSO configurations are more or less on par: the
+\texttt{yso-bonsai-en}, \texttt{yso-en}, and \texttt{yso-fasttext-en}
+configurations perform very similarily and are slightly outperformed by
+\texttt{yso-maui-en}.
+
+\begin{figure}
+\centering
 \includegraphics{images/metrics_f1_top20.pdf}
-\caption{Top 20 Annif configurations by F1-score.}
+\caption{The top 20 Annif configurations by F1-score.}
 \end{figure}
@@
 suggestions 0 \textless{} n \textless11.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{images/metrics_all_project+abstract.pdf}
-\caption{Distribution of weighted F1-scores per class of algorithm
-(left) and per class of text basis (right).}
 \end{figure}

### 2021-03-05 text/draft.tex
metrics general
refactor text structure

@@
 \hypertarget{aim}{%
-\subsection{Aim}\label{aim}}
+\section{Aim}\label{aim}}
 
@@
 \hypertarget{edoc-data}{%
-\subsection{Edoc data}\label{edoc-data}}
+\section{Edoc data}\label{edoc-data}}
 
 \hypertarget{edoc}{%
-\subsubsection{Edoc}\label{edoc}}
+\subsection{Edoc}\label{edoc}}
 
@@
 \hypertarget{data-extraction}{%
-\subsubsection{Data extraction}\label{data-extraction}}
+\subsection{Data extraction}\label{data-extraction}}
 
@@
 \hypertarget{data-description-and-analysis}{%
-\subsubsection{Data description and
+\subsection{Data description and
 analysis}\label{data-description-and-analysis}}
@@
 \hypertarget{sample-data-set}{%
-\subsection{Sample data set}\label{sample-data-set}}
+\section{Sample data set}\label{sample-data-set}}
 
@@
 \hypertarget{selection}{%
-\subsubsection{Selection}\label{selection}}
+\subsection{Selection}\label{selection}}
 
@@
 \hypertarget{construction}{%
-\subsubsection{Construction}\label{construction}}
+\subsection{Construction}\label{construction}}
 
@@
 \hypertarget{analysis}{%
-\subsubsection{Analysis}\label{analysis}}
+\subsection{Analysis}\label{analysis}}
 
@@
 The data foundation is available at
-\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
-be calculated by calling \texttt{\_Analysis.print\_chi\_square\_fit} on
-the data foundation files.}
+\texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and the
+\(\chi^2\)-statistic can be calculated by calling
+\texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
+files.}
 \end{figure}
@@
 \(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
-available at \texttt{/edoc/analysis/chi\_square...} and the
-\(\chi^2\)-statistic can be calculated by calling
+available at \texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and
+the \(\chi^2\)-statistic can be calculated by calling
 \texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
@@
 \hypertarget{machine-indexing}{%
-\subsection{Machine indexing}\label{machine-indexing}}
+\section{Machine indexing}\label{machine-indexing}}
 
 \hypertarget{general-overview}{%
-\subsubsection{General overview}\label{general-overview}}
+\subsection{General overview}\label{general-overview}}
 
@@
 \hypertarget{annif}{%
-\subsubsection{Annif}\label{annif}}
+\subsection{Annif}\label{annif}}
 
@@
 \hypertarget{implementation}{%
-\subsubsection{Implementation}\label{implementation}}
+\subsection{Implementation}\label{implementation}}
 
@@
 \hypertarget{gold-standard}{%
-\subsection{Gold standard}\label{gold-standard}}
+\section{Gold standard}\label{gold-standard}}
 
@@
 \hypertarget{definition}{%
-\subsubsection{Definition}\label{definition}}
+\subsection{Definition}\label{definition}}
 
@@
 \hypertarget{native-gold-standard}{%
-\subsubsection{Native gold standard}\label{native-gold-standard}}
+\subsection{Native gold standard}\label{native-gold-standard}}
 
@@
 \hypertarget{extract-keywords}{%
-\paragraph{Extract keywords}\label{extract-keywords}}
+\subsubsection{Extract keywords}\label{extract-keywords}}
 
@@
 \hypertarget{clean-keywords}{%
-\paragraph{Clean keywords}\label{clean-keywords}}
+\subsubsection{Clean keywords}\label{clean-keywords}}
 
@@
 \hypertarget{analysis-1}{%
-\paragraph{Analysis}\label{analysis-1}}
+\subsubsection{Analysis}\label{analysis-1}}
 
@@
 \hypertarget{reconciliation}{%
-\paragraph{Reconciliation}\label{reconciliation}}
+\subsubsection{Reconciliation}\label{reconciliation}}
 
@@
 \hypertarget{discussion}{%
-\paragraph{Discussion}\label{discussion}}
+\subsubsection{Discussion}\label{discussion}}
 
@@
 \hypertarget{foreign-gold-standard}{%
-\subsubsection{Foreign gold standard}\label{foreign-gold-standard}}
+\subsection{Foreign gold standard}\label{foreign-gold-standard}}
 
@@
 \hypertarget{assessment}{%
-\subsection{Assessment}\label{assessment}}
+\section{Assessment}\label{assessment}}
 
@@
 \hypertarget{precision-recall-f1-score}{%
-\subsubsection{Precision, recall,
+\subsection{Precision, recall,
 F1-score}\label{precision-recall-f1-score}}
@@
 \hypertarget{precision}{%
-\paragraph{Precision}\label{precision}}
+\subsubsection{Precision}\label{precision}}
 
@@
 \hypertarget{recall}{%
-\paragraph{Recall}\label{recall}}
+\subsubsection{Recall}\label{recall}}
 
@@
 \hypertarget{f1-score}{%
-\paragraph{F1-score}\label{f1-score}}
+\subsubsection{F1-score}\label{f1-score}}
 
@@
 \hypertarget{implementation-1}{%
-\paragraph{Implementation}\label{implementation-1}}
+\subsubsection{Implementation}\label{implementation-1}}
 
@@
 \hypertarget{annif-versus-native-gold-standard}{%
-\subsubsection{Annif versus native gold
+\subsection{Annif versus native gold
 standard}\label{annif-versus-native-gold-standard}}
@@
 \hypertarget{creating-the-data-foundation}{%
-\paragraph{Creating the data
+\subsubsection{Creating the data
 foundation}\label{creating-the-data-foundation}}
@@
 \hypertarget{general-results}{%
-\paragraph{General results}\label{general-results}}
+\subsubsection{General results}\label{general-results}}
 
@@
 \includegraphics{images/metrics_f1_top20.pdf}
-\caption{The top 20 Annif configurations by F1-score.}
+\caption{The top 20 Annif configurations (according to F1-score).}
 \end{figure}
@@
 \hypertarget{departments}{%
-\paragraph{Departments}\label{departments}}
+\subsubsection{Departments}\label{departments}}
 
@@
 \includegraphics{images/metrics_dept_summary.pdf}
-\caption{Best performing Annif configuration by F1-score weighted per
-department.}
+\caption{Best performing Annif configuration (according to weighted
+F1-score) per department.}
 \end{figure}
@@
 \includegraphics{images/metrics_dept_distribution.pdf}
-\caption{Distribution of F1-scores weighted for all Annif configurations
+\caption{Distribution of weighted F1-scores for all Annif configurations
 per department.}
@@
 \hypertarget{yso-configurations}{%
-\paragraph{YSO configurations}\label{yso-configurations}}
+\subsubsection{YSO configurations}\label{yso-configurations}}
 
 \hypertarget{wikidata-configurations}{%
-\paragraph{Wikidata configurations}\label{wikidata-configurations}}
+\subsubsection{Wikidata configurations}\label{wikidata-configurations}}
 
 \hypertarget{annif-versus-foreign-gold-standard}{%
-\subsubsection{Annif versus foreign gold
+\subsection{Annif versus foreign gold
 standard}\label{annif-versus-foreign-gold-standard}}
@@
 \hypertarget{digression-truth-conditions-for-indexing}{%
-\subsubsection{Digression: truth-conditions for
+\subsection{Digression: truth-conditions for
 indexing}\label{digression-truth-conditions-for-indexing}}
@@
 (Correspondence theory of indexing: subject term T fits text X iff text
-X is about T) \#\#\# Targets !! Find out what I meant here.
+X is about T) \#\# Targets !! Find out what I meant here.
 
 \hypertarget{analysis-2}{%
-\subsubsection{Analysis}\label{analysis-2}}
+\subsection{Analysis}\label{analysis-2}}
 
@@
 
-\hypertarget{outlook}{%
-\section{Outlook}\label{outlook}}
+\hypertarget{outlook-and-conclusion}{%
+\section{Outlook and conclusion}\label{outlook-and-conclusion}}
 
@@
 \subsection{Other use cases}\label{other-use-cases}}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
 

### 2021-03-06 text/draft.tex
general results

@@
 
+\begin{figure}
+\centering
+\includegraphics{images/metrics_all_project+abstract.pdf}
+\caption{Distribution of weighted F1-scores per class of project of
+Annif configuration (left) and per class of text basis of Annif
+configuration (right). \texttt{wikidata} (min = 0.239, Q1 = 0.355, M =
+0.415, Q3 = 0.492, max = 0.517) outperforms any YSO configuration.
+\texttt{yso-bonsai-en}, \texttt{yso-en} and \texttt{yso-fasttext-en} are
+on par (min = 0.169, Q1 = 0.218, M = 0.312, Q3 = 0.414, max = 0.496) and
+slightly outperformed by the more consistent \texttt{yso-maui-en} (min =
+0.171, Q1 = 0.250, M = 0.327, Q3 = 0.407, max = 0.496). Surprisingly,
+the performance of configurations based on titles (min = 0.169, Q1 =
+0.250, M = 0.345, Q3 = 0.424, max = 0.517) was better than the
+performance of configurations based on titles and abstracts (min =
+0.169, Q1 = 0.242, M = 0.337, Q3 = 0.424, max = 0.517).}
+\end{figure}
+
 Let us first consider overall performance. Here the most remarkable
 result is that Wikidata configurations outperformed YSO configurations
-(see Figure X). However, the explanation of this effect is not evident.
-The two main explanatory hypotheses are 1. that the suggestions by the
-Wikidata configurations are more salient, or 2. that the native gold
-standard is biased towards Wikidata due to its higher coverage of QIDs
-as compared to YSO IDs. By contrast, the Wikidata configurations are
-more productive than the YSO configurations, and the reason for this
+(see Figure 6, left). However, the explanation of this effect is not
+evident. The two main explanatory hypotheses are 1. that the suggestions
+by the Wikidata configurations are more salient, or 2. that the native
+gold standard is biased towards Wikidata due to its higher coverage of
+QIDs as compared to YSO IDs. By contrast, the Wikidata configurations
+are more productive than the YSO configurations, and the reason for this
 effect is the higher coverage of QIDs as compared to YSO IDs (see Figure
-Y). By ``productivity'' I mean that the absolute number of assigned
+7). By ``productivity'' I mean that the absolute number of assigned
 subject terms. So Wikidata configurations are not only qualitatively but
@@
 \centering
-\includegraphics{images/metrics_all_project+abstract.pdf}
-\caption{Distribution of weighted F1-scores per class of algorithm
-(left) and per class of text basis (right). Figure X.}
-\end{figure}
-
-\begin{figure}
-\centering
 \includegraphics{images/metrics_all_productivity.pdf}
-\caption{The distribution of cumulative sample size per class of Annif
-configuration. Figure Y}
+\caption{The distribution of cumulative sample size per project class of
+Annif configuration. Wikidata configurations (min = 28'618, Q1 = 29'912,
+M = 35'121, Q3 = 42'439, max = 48'776) are more productive than YSO
+configurations (min = 9'878, Q1 = 12'546, M = 16'710, Q3 = 22'694, max =
+27'354).}
 \end{figure}
@@
 configurations perform very similarily and are slightly outperformed by
-\texttt{yso-maui-en}.
+\texttt{yso-maui-en} (see Figure 6, left).
+
+A surprising find is that there was no performance gain achieved by
+increasing the text basis from titles to titles and abstracts (see
+section X): if anything, the performance for the extended text basis was
+slightly worse (see Figure 6, right).
 

### 2021-03-06 edoc/edoc_main.py

@@ -884,7 +884,6 @@ class _Analysis:
 
         _Utility.save_json(stats, DIR + "/analysis/metrics.json")
 
-
 exit()
 
 for dept in _Data.get_departments():

### 2021-03-07 text/draft.tex
dept results

@@
 four distributions are similarly consistent, but there is a linear
-shrinkage of the center leaving MeSH and YSO with potentially too few
-descriptors to represent an adequate indexing.}
+decrease of the distribution's center leaving MeSH and YSO with
+potentially too few descriptors to represent an adequate indexing.}
 \end{figure}
@@
 Gantert 2016, 197) whereby the F1 score plays are more prominent role in
-the assessment of machine indexing (e.g., Suominen 2018, 11--14; Toepfer
+the assessment of machine indexing (e.g., Suominen 2019, 11--14; Toepfer
 and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
@@
 performance of the 100 Annif configurations versus the native gold
-standard with respect to the Edoc sample data set.
+standard with respect to the Edoc sample data set. The data foundation
+is available at \texttt{/analysis/metrics.json}.
 
@@
 the performance of configurations based on titles (min = 0.169, Q1 =
-0.250, M = 0.345, Q3 = 0.424, max = 0.517) was better than the
-performance of configurations based on titles and abstracts (min =
+0.250, M = 0.345, Q3 = 0.424, max = 0.517) was marginally better than
+the performance of configurations based on titles and abstracts (min =
 0.169, Q1 = 0.242, M = 0.337, Q3 = 0.424, max = 0.517).}
@@
 
-Let us first consider overall performance. Here the most remarkable
-result is that Wikidata configurations outperformed YSO configurations
-(see Figure 6, left). However, the explanation of this effect is not
-evident. The two main explanatory hypotheses are 1. that the suggestions
-by the Wikidata configurations are more salient, or 2. that the native
-gold standard is biased towards Wikidata due to its higher coverage of
-QIDs as compared to YSO IDs. By contrast, the Wikidata configurations
-are more productive than the YSO configurations, and the reason for this
+Let us first consider overall performance. Here the most striking result
+is that Wikidata configurations outperformed YSO configurations (see
+Figure 6, left). However, the explanation of this effect is not evident.
+The two main explanatory hypotheses are 1. that the suggestions by the
+Wikidata configurations are more salient, or 2. that the native gold
+standard is biased towards Wikidata due to its higher coverage of QIDs
+as compared to YSO IDs. By contrast, the Wikidata configurations are
+more productive than the YSO configurations, and the reason for this
 effect is the higher coverage of QIDs as compared to YSO IDs (see Figure
@@
 \texttt{yso-bonsai-en}, \texttt{yso-en}, and \texttt{yso-fasttext-en}
-configurations perform very similarily and are slightly outperformed by
-\texttt{yso-maui-en} (see Figure 6, left).
-
-A surprising find is that there was no performance gain achieved by
+configurations perform very similarly and are slightly outperformed by
+\texttt{yso-maui-en} (see Figure 6, left). This result is consistent
+with other assessments reporting that ``{[}o{]}f the individual
+algorithms, Maui performed best on all corpora'' (Suominen 2019, 13).
+
+A surprising result is that there was no performance gain achieved by
 increasing the text basis from titles to titles and abstracts (see
-section X): if anything, the performance for the extended text basis was
-slightly worse (see Figure 6, right).
+\protect\hyperlink{creating-the-data-foundation}{section ``Creating the
+data foundation''}: if anything, the performance for the extended text
+basis was slightly worse (see Figure 6, right). There is again no easy
+explanation for this find since there are multiple plausible causes
+which cannot be distangled here. For example, the abstract of an item in
+the Edoc sample data set might be less representative of the item's
+content than its title. In that case, the observed worse perfomance of
+the Annif configurations based on title and abstracts would even be
+expected. Alternatively, it might be the case that the problem lies with
+Annif: a larger text basis introduces more confounding factors and might
+make it harder to extract the subject terms required. An experimentum
+crucis to decide between the two discussed explanations would be to
+further extend the text basis to include full texts in addition to
+titles and abstracts.
+
+\begin{figure}
+\centering
+\includegraphics{images/metrics_all_n.pdf}
+\caption{Distribution of weighted F1-scores per maximum number of
+suggestions 1 \(\leq\) n \(\leq\) 10. See Table 2 for numeric values. n
+= 2 is the best perfomring type of configuration. However, it is
+outperformed by n = 4 and n = 5 token configurations. The distribution
+of the distributions is skewed left. Types of configurations with a
+smaller maximum number of suggestions display a more consistent
+performance.}
+\end{figure}
+
+\begin{table}[]
+\begin{tabular}{lllllllllll}
+    & n=1   & n=2   & n=3   & n=4   & n=5   & n=6   & n=7   & n=8   & n=9   & n=10  \\ \hline
+min & 0.239 & 0.403 & 0.454 & 0.391 & 0.336 & 0.289 & 0.250 & 0.218 & 0.192 & 0.169 \\
+Q1  & 0.407 & 0.491 & 0.454 & 0.391 & 0.336 & 0.289 & 0.250 & 0.218 & 0.192 & 0.169 \\
+M   & 0.414 & 0.496 & 0.454 & 0.391 & 0.336 & 0.289 & 0.250 & 0.218 & 0.192 & 0.169 \\
+Q3  & 0.414 & 0.496 & 0.456 & 0.400 & 0.351 & 0.309 & 0.277 & 0.251 & 0.231 & 0.215 \\
+max & 0.414 & 0.496 & 0.492 & 0.517 & 0.503 & 0.467 & 0.427 & 0.389 & 0.355 & 0.324
+\end{tabular}
+\caption{Distribution of weighted F1-scores per maximum number of suggestions 1 $\leq$ n $\leq$ 10.}
+\label{tab:max-number}
+\end{table}
+
+Let us turn to the parameter of the maximum number of suggestions per
+item in the Edoc sample data set (see Figure 8). Here the best
+performance was achieved by a token n = 4 configuration. However, the
+type n = 4 configuration performed on average significantly worse than
+the type n = 3 and type n = 2 configurations. So with respect to the
+maximum number of suggestions, there is a discrepancy between the best
+performing token configuration and the best performing type of
+configuration. This distinction is important: when choosing a
+configuration for the purpose of a production system, we are usually
+interested in the best token configuration. The top 20 token
+configurations are summarized in Figure 9. The best performing
+configuration with a weighted F1-score of 0.517 is \texttt{wikidata-en}
+with a maximum number of 4 suggestions per item; the text basis (title
+or abstract and title) does not matter.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{images/metrics_all_n.pdf}
-\caption{Distribution of weighted F1-scores per maximum number of
-suggestions 0 \textless{} n \textless11.}
-\end{figure}
-
-we can then discuss whether the best performance is actually useful;
-perhaps do this by comparing absolute scores with other assessments. if
-results are much lower it is to be suspected that the native gold
-standard is not very good (i.e., that the measure we use to judge annif
-performance is inadequte =\textgreater{} motivation for foreign
-standard)
-
-construct all metrics: \_Analysis.super\_make\_metrics(file\_path=DIR +
-``/indexed/indexed\_master\_mesh\_enriched.json'')
-
-construcht all stats for metrics: \_Analysis.super\_make\_stats()
-
-\hypertarget{departments}{%
-\subsubsection{Departments}\label{departments}}
-
-I had noted in section X as caveat that the performance of Annif might
-vary according to department due to systematic biases in constructing
-the Edoc sample data set. It might therefore be illuminating to assess
-the performance of the various Annif configurations per department.
-Since the Edoc \texttt{department} data field is mandatory, the sample
-data set is partioned into blocks of departments by default. We can thus
-create a data foundation for each such block by calling
+\hypertarget{results-by-department}{%
+\subsubsection{Results by department}\label{results-by-department}}
+
+In \protect\hyperlink{general-results}{section ``General results''} I
+have identified and discussed the overall best Annif configerations.
+However, in \protect\hyperlink{analysis}{section ``Analysis''}) I had
+also noted the caveat that the performance of Annif might vary according
+to department due to systematic biases in constructing the Edoc sample
+data set. In this section I will therefore assess the performance of the
+various Annif configurations per department.
+
+We begin again by constructing the data foundation. Since the Edoc
+\texttt{department} data field is mandatory, the sample data set is
+partitioned into blocks of departments by default. We can thus create a
+data foundation for each such block by calling
 \texttt{\_Analysis.super\_make\_metrics} with a departmental parameter:
@@
 configurations \(*\) 10 departments) where \texttt{department} specifies
-the department according to the Edoc convention.
-
-Let us now look at the results. For each department, we are interested
-in the highest weighted F1-score and the corresponding configuration as
-summarized in Figure X.
+the department according to the Edoc convention. The data foundation is
+summarized in \texttt{/analysis/metrics.json}.
+
+\begin{figure}
+\centering
+\includegraphics{images/metrics_dept_distribution.pdf}
+\caption{Distribution of weighted F1-scores for all Annif configurations
+per department.}
+\end{figure}
+
+Let us now look at the results. First consider the distribution of the
+performance scores across departments as shown in Figure 11. We can see
+that there are striking differences in variability between departments.
+The departments with the most consistent weighted F1-scores are Medicine
+and Central Services. However, these two departments have also the
+lowest maximum F1-scores. It is noteworthy that all other departments
+have maximum F1-scores that are well above the F1-score of 0.517 of the
+best performing general Annif configuration.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{images/metrics_dept_distribution.pdf}
-\caption{Distribution of weighted F1-scores for all Annif configurations
-per department.}
-\end{figure}
-
-\hypertarget{yso-configurations}{%
-\subsubsection{YSO configurations}\label{yso-configurations}}
-
-\hypertarget{wikidata-configurations}{%
-\subsubsection{Wikidata configurations}\label{wikidata-configurations}}
+Let us now consider the best performing Annif configurations per
+department as summarized in Figure 12.
+
+For each department, we are interested in the highest weighted F1-score
+and the corresponding configuration as summarized in Figure X.
 
@@
 
-\hypertarget{digression-truth-conditions-for-indexing}{%
-\subsection{Digression: truth-conditions for
-indexing}\label{digression-truth-conditions-for-indexing}}
-
-(Correspondence theory of indexing: subject term T fits text X iff text
-X is about T) \#\# Targets !! Find out what I meant here.
-
-\hypertarget{analysis-2}{%
-\subsection{Analysis}\label{analysis-2}}
-
-\hypertarget{discussion-1}{%
-\subsection{Discussion}\label{discussion-1}}
-
 \hypertarget{outlook-and-conclusion}{%
@@
 \subsection{Refinement}\label{refinement}}
+
+\begin{itemize}
+\tightlist
+\item
+  fulltext support
+\end{itemize}
 
@@
 
-\leavevmode\hypertarget{ref-Suominen.2018}{}%
-Suominen, Osma. 2018. {``Annif: DIY Automated Subject Indexing Using
+\leavevmode\hypertarget{ref-Suominen.2019}{}%
+Suominen, Osma. 2019. {``Annif: DIY Automated Subject Indexing Using
 Multiple Algorithms.''} \emph{LIBER Quarterly} 29 (1): 1--25.

### 2021-03-07 text/draft.tex
refactor class names

@@
 \texttt{id\_number}, and \texttt{keywords}. We do so by calling
-\texttt{\_Data.select\_from\_file} iteratively for all files in
+\texttt{\Data.select\_from\_file} iteratively for all files in
 \texttt{/edoc/raw}. The resulting file is saved in
@@
 \(\chi^2\)-statistic can be calculated by calling
-\texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
+\texttt{\Analysis.print\_chi\_square\_fit} on the data foundation
 files.}
@@
 the \(\chi^2\)-statistic can be calculated by calling
-\texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
+\texttt{\Analysis.print\_chi\_square\_fit} on the data foundation
 files.}
@@
 \texttt{keywords} data field on a per item basis. To do this, we call
-\texttt{\_Keywords.extract\_keywords} with the sample data set as
+\texttt{\Keywords.extract\_keywords} with the sample data set as
 argument and save the output as
@@
 \begin{Highlighting}[]
-\NormalTok{keywords }\OperatorTok{=}\NormalTok{ \_Keywords.extract\_keywords(DIR }\OperatorTok{+} \StringTok{"/sample/sample\_master.json"}\NormalTok{)}
+\NormalTok{keywords }\OperatorTok{=}\NormalTok{ \Keywords.extract\_keywords(DIR }\OperatorTok{+} \StringTok{"/sample/sample\_master.json"}\NormalTok{)}
 \NormalTok{\_Utility.save\_json(keywords, DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
@@
 
-\texttt{\_Keywords.clean\_keywords} is the implementation the parser
+\texttt{\Keywords.clean\_keywords} is the implementation the parser
 while the recursive cleaner is implemented by
-\texttt{\_Keywords.clean\_keyword}. To create the desired list of clean
+\texttt{\Keywords.clean\_keyword}. To create the desired list of clean
 keywords, saved as \texttt{/keywords/keywords\_clean.json}, we call
-\texttt{\_Keywords.clean\_keywords} with the extracted keywords as
+\texttt{\Keywords.clean\_keywords} with the extracted keywords as
 argument:
@@
 \NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
-\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \_Keywords.clean\_keywords(keywords\_extracted)}
+\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \Keywords.clean\_keywords(keywords\_extracted)}
 \NormalTok{\_Utility.save\_json(keywords\_clean, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
@@
 of each keyword. This is achieved by calling
-\texttt{\_Keywords.make\_histogram} on
+\texttt{\Keywords.make\_histogram} on
 \texttt{/keywords/keywords\_clean.json} and saving the output as
@@
 \NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
-\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ \_Keywords.make\_histogram(keywords\_clean)}
+\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ \Keywords.make\_histogram(keywords\_clean)}
 \NormalTok{\_Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
@@
 To analyse the spread of keywords in the sample data set, the keywords
-per item are counted. To do so, we call \texttt{\_Keywords.make\_count}
+per item are counted. To do so, we call \texttt{\Keywords.make\_count}
 on \texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
@@
 \NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
-\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ \_Keywords.make\_count(sample\_data\_set)}
+\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ \Keywords.make\_count(sample\_data\_set)}
 \NormalTok{\_Utility.save\_json(keywords\_counted, DIR }\OperatorTok{+} \StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
@@
 reconcilement is detailed in Figure 4. It is achieved by calling
-\texttt{\_Keywords.enrich\_with\_yso} on
+\texttt{\Keywords.enrich\_with\_yso} on
 \texttt{/keywords/keywords\_reference.json} and saving the output as
@@
 \NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
-\NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ \_Keywords.enrich\_with\_yso(keywords\_reference)}
+\NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ \Keywords.enrich\_with\_yso(keywords\_reference)}
 \NormalTok{\_Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
@@
 keywords per item in the Edoc sample data set. The corresponding data is
-generated with \texttt{\_Keywords.make\_count} as described in
+generated with \texttt{\Keywords.make\_count} as described in
 \protect\hyperlink{analysis}{subsection Analysis} above and available as
@@
 (\(n=500\)) was created by calling
-\texttt{\_Analysis.make\_random\_sample} on
+\texttt{\Analysis.make\_random\_sample} on
 \texttt{/keywords/reference\_keywords\_master.json}; it is available at
@@
 To compute the F1-score, we call
-\texttt{\_Analysis.super\_make\_metrics} on
+\texttt{\Analysis.super\_make\_metrics} on
 \texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
@@
 \begin{Highlighting}[]
-\NormalTok{\_Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
+\NormalTok{\Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
 \end{Highlighting}
@@
 data foundation for each such block by calling
-\texttt{\_Analysis.super\_make\_metrics} with a departmental parameter:
+\texttt{\Analysis.super\_make\_metrics} with a departmental parameter:
 
@@
 \begin{Highlighting}[]
-\ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ \_Data.get\_departments():}
-\NormalTok{    \_Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{, deparment}\OperatorTok{=}\NormalTok{dept)}
+\ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ \Data.get\_departments():}
+\NormalTok{    \Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{, deparment}\OperatorTok{=}\NormalTok{dept)}
 \end{Highlighting}

### 2021-03-07 edoc/edoc_main.py

@@ -15,7 +15,7 @@ from sklearn.metrics import f1_score, recall_score, precision_score
 DIR = os.path.dirname(__file__)
 
 
-class _Utility:
+class Utility:
     """ A collection of utility functions. """
 
     @classmethod
@@ -67,7 +67,7 @@ class _Utility:
                 position = position + 5000
 
 
-class _Data:
+class Data:
     """ A collection of edoc data functions. """
 
     @classmethod
@@ -106,12 +106,12 @@ class _Data:
         :param fields: the required fields for an item to be sample
         """
 
-        data = _Utility.load_json(file_path)
+        data = Utility.load_json(file_path)
         print(f"{file_path} loaded")
-        selected = _Data.select_from_data(data, *fields)
+        selected = Data.select_from_data(data, *fields)
         print(f"Items sample")
         save_file_path = DIR + "/sample/" + str(datetime.now()).split(".")[0].replace(":", "-").replace(" ", "-")
-        _Utility.save_json(selected, save_file_path)
+        Utility.save_json(selected, save_file_path)
 
     @classmethod
     def inspect(cls,
@@ -147,7 +147,7 @@ class _Data:
         :param save_path: complete path to save folder including filename without extension
         """
 
-        data = _Utility.load_json(file_path)
+        data = Utility.load_json(file_path)
         modified_data = []
 
         for item in data:
@@ -157,7 +157,7 @@ class _Data:
 
             # clean keywords
             keywords = modified_item.get("keywords")
-            keywords_clean = _Keywords.clean_keywords([keywords])
+            keywords_clean = Keywords.clean_keywords([keywords])
 
             # enrich keywords
             enriched_keywords = []
@@ -169,7 +169,7 @@ class _Data:
             # add modified item to output:
             modified_data.append(modified_item)
 
-        _Utility.save_json(modified_data, save_path + ".json")
+        Utility.save_json(modified_data, save_path + ".json")
 
     @classmethod
     def map2reference(cls,
@@ -182,7 +182,7 @@ class _Data:
         """
 
         # load reference keywords:
-        keywords_reference = _Utility.load_json(DIR + "/keywords/keywords_reference_master.json")
+        keywords_reference = Utility.load_json(DIR + "/keywords/keywords_reference_master.json")
 
         # enrich keywords
         for entry in keywords_reference:
@@ -201,7 +201,7 @@ class _Data:
[…]

### 2021-03-07 text/draft.tex
refactor structure

@@
 
+\hypertarget{method}{%
+\subsection{Method}\label{method}}
+
+!! Say something to the effect that all data and code are available on
+GitHub.
+
+!! In this chapter, the prototype for a machine indexing of Edoc is
+presented. The focus is primarily on practical implementation although
+care is taken to spell out design decisions in as much detail as is
+needed.
+
 \hypertarget{outline}{%
@@
 
-\hypertarget{method}{%
-\subsection{Method}\label{method}}
-
-!! Say something to the effect that all data and code are available on
-GitHub.
-
-\hypertarget{tools-and-configuration}{%
-\subsection{Tools and configuration}\label{tools-and-configuration}}
-
-\hypertarget{openrefine}{%
-\subsubsection{OpenRefine}\label{openrefine}}
+Let us start by stating the aim of the prototype. From a functional
+perspective, the prototype takes a subset of the data from Edoc as input
+and provides index terms for each item in this subset as output. In
+order to fulfill this aim we can distinguish a number of steps that need
+to be taken:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Understand the Edoc data.\\
+\item
+  Select and construct a sample data set.
+\item
+  Use Annif to index the items in the sample data set.
+\item
+  Construct a gold standard from the keywords.
+\item
+  Assess the quality of the output based on the gold standard.
+\end{enumerate}
+
+In the sections below, these steps will be discussed in detail.
+
+\hypertarget{tools}{%
+\subsection{Tools}\label{tools}}
 
@@
 https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation
-for details). ALso note that OpenRefine always counts the number of
+for details). Also note that OpenRefine always counts the number of
 records by the first column (a fact which caused me many headaches).
-
-\hypertarget{prototype}{%
-\section{Prototype}\label{prototype}}
-
-In this chapter, the prototype for a machine indexing of Edoc is
-presented. The focus is primarily on practical implementation although
-care is taken to spell out design decisions in as much detail as is
-needed.
-
-\hypertarget{aim}{%
-\section{Aim}\label{aim}}
-
-Let us start by stating the aim of the prototype. From a functional
-perspective, the prototype takes a subset of the data from Edoc as input
-and provides index terms for each item in this subset as output. In
-order to fulfill this aim we can distinguish a number of steps that need
-to be taken:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Understand the Edoc data.\\
-\item
-  Select and construct a sample data set.
-\item
-  Use Annif to index the items in the sample data set.
-\item
-  Construct a gold standard from the keywords.
-\item
-  Assess the quality of the output based on the gold standard.
-\end{enumerate}
-
-In the sections below, these steps will be discussed in detail.
 
@@
 handled and can be uploaded to GitHub. For this
-\texttt{\_Utility.split\_json} was used yielding 14 files of size 20 MB
-or less containing 5000 or fewer entries each. These files are called
+\texttt{Utility.split\_json} was used yielding 14 files of size 20 MB or
+less containing 5000 or fewer entries each. These files are called
 \texttt{raw\_master\_x-y.json} (where x and y indicate the entries as
@@
 \texttt{id\_number}, and \texttt{keywords}. We do so by calling
-\texttt{\Data.select\_from\_file} iteratively for all files in
+\texttt{Data.select\_from\_file} iteratively for all files in
 \texttt{/edoc/raw}. The resulting file is saved in
@@
 \(\chi^2\)-statistic can be calculated by calling
-\texttt{\Analysis.print\_chi\_square\_fit} on the data foundation
-files.}
+\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
 \end{figure}
@@
 the \(\chi^2\)-statistic can be calculated by calling
-\texttt{\Analysis.print\_chi\_square\_fit} on the data foundation
-files.}
+\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
 \end{figure}
@@
 
-In this chapter I will construct two distinct gold standards in order to
-assess the quality of machine indexing the sample data set with Annif.\\
-!! Say something about assessments of Annif that have already been
-carried out.
+In this section I will construct a derivative gold standard in order to
+assess the quality of machine indexing the sample data set with Annif.
 
@@
 scratch is very expensive. It is therefore not an option for the project
-at hand. Rather, I will construct what could be called derivative gold
-standards by reusing indexing data that is already available. Here we
-can distinguish two distinct kinds of derivative gold standards: first,
-I will construct a derivative gold standard based on the author keywords
-available in the sample data set; call this the ``native'' gold
-standard. Second, I will construct a derivative gold standard based on
-indexing metadata available in repositories distinct from Edoc; call
-this the ``foreign'' gold standard.
+at hand. Rather, I will construct what could be called a ``derivative''
+gold standard by reusing indexing data that is already available.
 
@@
 
-\hypertarget{native-gold-standard}{%
-\subsection{Native gold standard}\label{native-gold-standard}}
-
-The construction of the native gold standard takes x steps:
+The construction of the derivative gold standard takes x steps:
 
@@
 
-\hypertarget{extract-keywords}{%
-\subsubsection{Extract keywords}\label{extract-keywords}}
+\hypertarget{extract-and-clean-keywords}{%
+\subsection{Extract and clean
+keywords}\label{extract-and-clean-keywords}}
 
@@
 \texttt{keywords} data field on a per item basis. To do this, we call
-\texttt{\Keywords.extract\_keywords} with the sample data set as
-argument and save the output as
-\texttt{keywords/keywords\_extracted.json} like so:
+\texttt{Keywords.extract\_keywords} with the sample data set as argument
+and save the output as \texttt{keywords/keywords\_extracted.json} like
+so:
 
@@
 \begin{Highlighting}[]
-\NormalTok{keywords }\OperatorTok{=}\NormalTok{ \Keywords.extract\_keywords(DIR }\OperatorTok{+} \StringTok{"/sample/sample\_master.json"}\NormalTok{)}
-\NormalTok{\_Utility.save\_json(keywords, DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
+\NormalTok{keywords }\OperatorTok{=}\NormalTok{ Keywords.extract\_keywords(DIR }\OperatorTok{+} \StringTok{"/sample/sample\_master.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords, DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
 \end{Highlighting}
 \end{Shaded}
-
-\hypertarget{clean-keywords}{%
-\subsubsection{Clean keywords}\label{clean-keywords}}
 
@@
 
-\texttt{\Keywords.clean\_keywords} is the implementation the parser
-while the recursive cleaner is implemented by
-\texttt{\Keywords.clean\_keyword}. To create the desired list of clean
+\texttt{Keywords.clean\_keywords} is the implementation the parser while
+the recursive cleaner is implemented by
+\texttt{Keywords.clean\_keyword}. To create the desired list of clean
 keywords, saved as \texttt{/keywords/keywords\_clean.json}, we call
-\texttt{\Keywords.clean\_keywords} with the extracted keywords as
+\texttt{Keywords.clean\_keywords} with the extracted keywords as
 argument:
@@
 \begin{Highlighting}[]
-\NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
-\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \Keywords.clean\_keywords(keywords\_extracted)}
-\NormalTok{\_Utility.save\_json(keywords\_clean, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
+\NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
+\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Keywords.clean\_keywords(keywords\_extracted)}
+\NormalTok{Utility.save\_json(keywords\_clean, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \hypertarget{analysis-1}{%
-\subsubsection{Analysis}\label{analysis-1}}
+\subsection{Analysis}\label{analysis-1}}
 
@@
 of each keyword. This is achieved by calling
-\texttt{\Keywords.make\_histogram} on
+\texttt{Keywords.make\_histogram} on
 \texttt{/keywords/keywords\_clean.json} and saving the output as
@@
 \begin{Highlighting}[]
-\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
-\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ \Keywords.make\_histogram(keywords\_clean)}
-\NormalTok{\_Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
+\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
+\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ Keywords.make\_histogram(keywords\_clean)}
+\NormalTok{Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
 \end{Highlighting}
@@
 To analyse the spread of keywords in the sample data set, the keywords
-per item are counted. To do so, we call \texttt{\Keywords.make\_count}
-on \texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
+per item are counted. To do so, we call \texttt{Keywords.make\_count} on
+\texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
 output as \texttt{/analysis/keywords\_counted.json}:
@@
 \begin{Highlighting}[]
-\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
-\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ \Keywords.make\_count(sample\_data\_set)}
-\NormalTok{\_Utility.save\_json(keywords\_counted, DIR }\OperatorTok{+} \StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
+\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
+\NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ Keywords.make\_count(sample\_data\_set)}
+\NormalTok{Utility.save\_json(keywords\_counted, DIR }\OperatorTok{+} \StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \hypertarget{reconciliation}{%
-\subsubsection{Reconciliation}\label{reconciliation}}
+\subsection{Reconciliation}\label{reconciliation}}
 
@@
 (English) vocabularies are Wikidata YSO. The next step in constructing
-the native gold standard is hence to match the extracted and cleaned
+the derivative gold standard is hence to match the extracted and cleaned
 keywords with keywords from YSO and Wikidata. This process is called
@@
 reconcilement is detailed in Figure 4. It is achieved by calling
-\texttt{\Keywords.enrich\_with\_yso} on
+\texttt{Keywords.enrich\_with\_yso} on
 \texttt{/keywords/keywords\_reference.json} and saving the output as
@@
 \begin{Highlighting}[]
-\NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
-\NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ \Keywords.enrich\_with\_yso(keywords\_reference)}
-\NormalTok{\_Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
+\NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
+\NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ Keywords.enrich\_with\_yso(keywords\_reference)}
+\NormalTok{Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
 \end{Highlighting}
@@
 keywords per item in the Edoc sample data set. The corresponding data is
-generated with \texttt{\Keywords.make\_count} as described in
+generated with \texttt{Keywords.make\_count} as described in
 \protect\hyperlink{analysis}{subsection Analysis} above and available as
@@
 \hypertarget{discussion}{%
-\subsubsection{Discussion}\label{discussion}}
+\subsection{Discussion}\label{discussion}}
 
@@
 (\(n=500\)) was created by calling
-\texttt{\Analysis.make\_random\_sample} on
+\texttt{Analysis.make\_random\_sample} on
 \texttt{/keywords/reference\_keywords\_master.json}; it is available at
@@
 
-\hypertarget{foreign-gold-standard}{%
-\subsection{Foreign gold standard}\label{foreign-gold-standard}}
-
-\begin{itemize}
-\tightlist
-\item
-  !! Explain MeSH
-\item
-  !! Explain how to get MeSH for subset of sample data set
-\end{itemize}
-
 \hypertarget{assessment}{%
@@
 
-In this chapter I will assess the quality of the sample data set's
-indexing with Annif based on the native and foreign gold standards.
+In this section I will assess the quality of the sample data set's
+indexing with Annif based on the gold standard.
 
@@
 metrics. Remember that a suggestion of a subject term is correct if and
-only if the subject term is in the native gold standard. The possible
-outcomes are summarized in Table 1.
+only if the subject term is in the derivative gold standard. The
+possible outcomes are summarized in Table 1.
 
@@
 
-\hypertarget{precision}{%
-\subsubsection{Precision}\label{precision}}
-
 ``Precision'' is the fraction of the correctly suggested subject terms;
-a suggestion is correct if and only if it is in the native gold
+a suggestion is correct if and only if it is in the derivative gold
 standard:
@@
 Or put as question: what fraction of the subject terms suggested by
-Annif are also in the native gold standard?
-
-\hypertarget{recall}{%
-\subsubsection{Recall}\label{recall}}
+Annif are also in the derivative gold standard?
 
@@
 
-\hypertarget{f1-score}{%
-\subsubsection{F1-score}\label{f1-score}}
-
 The F1-score is the harmonic mean between precision and recall:
@@
 
-\hypertarget{implementation-1}{%
-\subsubsection{Implementation}\label{implementation-1}}
-
 The above scoring metrics were implemented using the scikit-learn
@@
 configuration
-(\protect\hyperlink{annif-versus-native-gold-standard}{section ``Annif
-versus native gold standard''})\ldots{} {[}perhaps explain how it is
-done, important to mention transformation of multilabel to binary{]}.
-Note that while
-
-\hypertarget{annif-versus-native-gold-standard}{%
-\subsection{Annif versus native gold
-standard}\label{annif-versus-native-gold-standard}}
-
-In this section, I will assess the performance of Annif versus the
-native gold standard.
+(\protect\hyperlink{annif-versus-derivative-gold-standard}{section
+``Annif versus derivative gold standard''})\ldots{} {[}perhaps explain
+how it is done, important to mention transformation of multilabel to
+binary{]}.
 
 \hypertarget{creating-the-data-foundation}{%
-\subsubsection{Creating the data
+\subsection{Creating the data
 foundation}\label{creating-the-data-foundation}}
@@
 
-To compute the F1-score, we call
-\texttt{\Analysis.super\_make\_metrics} on
-\texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output files
-are saved as \texttt{/metrics/metrics\_\{marker\}.json} where
+To compute the F1-score, we call \texttt{Analysis.super\_make\_metrics}
+on \texttt{/indexed/indexed\_master\_mesh\_enriched}. The 100 output
+files are saved as \texttt{/metrics/metrics\_\{marker\}.json} where
 \texttt{marker} specifies the Annif configuration; a single file for
@@
 \begin{Highlighting}[]
-\NormalTok{\Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
+\NormalTok{Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
 \end{Highlighting}
@@
 matrix was computed, that is, each case in which either Annif or the
-native gold standard assigned a subject term. Finally, note that if an
-item in the Edoc sample data set had an empty native gold standard, no
-score was computed; this is the case exactly if none of the cleaned
-keywords had been matched to Wikidata or YSO respectively.
+derivative gold standard assigned a subject term. Finally, note that if
+an item in the Edoc sample data set had an empty derivative gold
+standard, no score was computed; this is the case exactly if none of the
+cleaned keywords had been matched to Wikidata or YSO respectively.
 Configurations with a Wikidata vocabulary had a scoring coverage of
@@
 \hypertarget{general-results}{%
-\subsubsection{General results}\label{general-results}}
+\subsection{General results}\label{general-results}}
 
 In this section I will discuss the general results of assessing the
-performance of the 100 Annif configurations versus the native gold
+performance of the 100 Annif configurations versus the derivative gold
 standard with respect to the Edoc sample data set. The data foundation
@@
 The two main explanatory hypotheses are 1. that the suggestions by the
-Wikidata configurations are more salient, or 2. that the native gold
+Wikidata configurations are more salient, or 2. that the derivative gold
 standard is biased towards Wikidata due to its higher coverage of QIDs
@@
 \includegraphics{images/metrics_f1_top20.pdf}
-\caption{The top 20 Annif configurations (according to F1-score).}
+\caption{20 best performing Annif configurations (according to
+F1-score).}
 \end{figure}
@@
 \hypertarget{results-by-department}{%
-\subsubsection{Results by department}\label{results-by-department}}
+\subsection{Results by department}\label{results-by-department}}
 
@@
 data foundation for each such block by calling
-\texttt{\Analysis.super\_make\_metrics} with a departmental parameter:
+\texttt{Analysis.super\_make\_metrics} with a departmental parameter:
 
@@
 \begin{Highlighting}[]
-\ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ \Data.get\_departments():}
-\NormalTok{    \Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{, deparment}\OperatorTok{=}\NormalTok{dept)}
+\ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ Data.get\_departments():}
+\NormalTok{    Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{, deparment}\OperatorTok{=}\NormalTok{dept)}
 \end{Highlighting}
@@
 and Central Services. However, these two departments have also the
-lowest maximum F1-scores. It is noteworthy that all other departments
-have maximum F1-scores that are well above the F1-score of 0.517 of the
-best performing general Annif configuration.
+lowest maximum weighted F1-scores. It is noteworthy that all other
+departments have maximum weighted F1-scores that are well above the
+F1-score of 0.517 of the best performing general Annif configuration.
 
@@
 \caption{Best performing Annif configuration (according to weighted
-F1-score) per department.}
+F1-score) per department as compared to the overall best performing
+Annif configuration \texttt{wikidata-en-F-F-4-N}.}
 \end{figure}
@@
 Let us now consider the best performing Annif configurations per
-department as summarized in Figure 12.
-
-For each department, we are interested in the highest weighted F1-score
-and the corresponding configuration as summarized in Figure X.
-
-\hypertarget{annif-versus-foreign-gold-standard}{%
-\subsection{Annif versus foreign gold
-standard}\label{annif-versus-foreign-gold-standard}}
-
-!! but to do this we would first have to map the annif suggested terms
-to mesh\ldots! yes.
+department as summarized in Figure 12. It is evident that only two of
+the ten departments (namely Associated and Central Services) have as
+best performing configuration the configuration that was declared the
+overall best performing configuration (namely
+\texttt{wikidata-en-F-F-4-N}). More surprisingly, YSO outperforms
+Wikidata in all other departments except Interdisciplinary. However, the
+margin is rather slim. The notable exception is the department
+Economics, where the YSO configuration outperforms the Wikidata
+configuration by a factor of 3. More importantly, the best performing
+YSO configurations are significantly less productive than the slightly
+worse performing Wikidata configuration, except for
+\texttt{yso-en-F-F-4-N} in the Medicine department.
 
@@
   fulltext support
+\item
+  mesh; A gold standard is usually the product of manual indexing by
+  ``information experts, subject experts, or potential or real end
+  users'' (Golub et al. 2016, 10). This entails its own host of
+  epistemic problems relating to objectivity and consistency of the
+  assigned subject terms. Most importantly, however, the construction of
+  a gold standard from scratch is very expensive. It is therefore not an
+  option for the project at hand. Rather, I will construct what could be
+  called derivative gold standards by reusing indexing data that is
+  already available. Here we can distinguish two distinct kinds of
+  derivative gold standards: first, I will construct a derivative gold
+  standard based on the author keywords available in the sample data
+  set; call this the ``derivative'' gold standard. Second, I will
+  construct a derivative gold standard based on indexing metadata
+  available in repositories distinct from Edoc; call this the
+  ``foreign'' gold standard.
 \end{itemize}
@@
 \subsection{Implementation strategy}\label{implementation-strategy}}
-
-\hypertarget{other-use-cases}{%
-\subsection{Other use cases}\label{other-use-cases}}
 

### 2021-03-07 text/draft.tex
refactor structure

@@
 
-\hypertarget{edoc}{%
-\subsection{Edoc}\label{edoc}}
+\hypertarget{edoc-and-data-extraction}{%
+\subsection{Edoc and data extraction}\label{edoc-and-data-extraction}}
 
@@
 scope when the University of Basel adapted its first open access policy
-in 2013. As per today Edoc contains roughly 68'000 items.
-
-Edoc runs on the EPrints 3 document management system
-(https://github.com/eprints/eprints).\\
-!! Add technical description of Edoc.\\
-!! Perhaps add description of how files are added to Edoc, see PDF in
-\texttt{/todo}.
-
-\hypertarget{data-extraction}{%
-\subsection{Data extraction}\label{data-extraction}}
+in 2013. As per today Edoc contains roughly 68'000 items. Edoc runs on
+the EPrints 3 document management system
+(https://github.com/eprints/eprints).
 
@@
 \begin{Highlighting}[]
-\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
+\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master.json"}\NormalTok{)}
 \NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ Keywords.make\_count(sample\_data\_set)}
@@
 \begin{Highlighting}[]
-\NormalTok{Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{)}
+\NormalTok{Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master.json"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\hypertarget{results-by-department}{%
-\subsection{Results by department}\label{results-by-department}}
+\hypertarget{departmental-results}{%
+\subsection{Departmental results}\label{departmental-results}}
 
@@
 \ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ Data.get\_departments():}
-\NormalTok{    Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master\_mesh\_enriched.json"}\NormalTok{, deparment}\OperatorTok{=}\NormalTok{dept)}
+\NormalTok{    Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master.json"}\NormalTok{, dept)}
 \end{Highlighting}
@@
   available in repositories distinct from Edoc; call this the
-  ``foreign'' gold standard.
+  ``foreign'' gold standard. -We enrich the sample items with MeSH
+  keywords from PubMed if available (item needs a PubMed ID and items
+  needs to be indexed with MeSH on PubMed, 1653 items match this
+  requirement); the resulting file is indexed\_master\_mesh.json. Like
+  so: Data.enrich\_with\_mesh(DIR + ``/indexed/indexed\_master.json,''
+  DIR + ``/indexed/indexed\_master\_mesh'')
 \end{itemize}
@@
 \subsection{Implementation strategy}\label{implementation-strategy}}
-
-!! Clean up: rename
-\texttt{/indexed/indexed\_master\_mesh\_enriched.json} to
-\texttt{/indexed/master\_final.json} or something short.
 

### 2021-03-07 edoc/edoc_main.py

@@ -883,117 +883,3 @@ class Analysis:
             stats.append({"stat": metrics})
 
         Utility.save_json(stats, DIR + "/analysis/metrics.json")
-
-exit()
-
-for dept in Data.get_departments():
-    Analysis.super_make_metrics(file_path=DIR + "/indexed/indexed_master_mesh_enriched.json", department=dept)
-
-exit()
-
-Analysis.make_metrics(file_path=DIR + "/indexed/indexed_master_mesh_enriched.json",
-                      project_id="yso-en",
-                      abstract=True,
-                      fulltext=False,
-                      limit=None,
-                      threshold=None,
-                      n=10)
-
-
-
-"""
-Here I describe _Utility and Data in relation to the files in the edoc folder. 
-
-OK 1. We start by extracting all data from edoc. We do this by conducting an advanced search with the date-field set to
-1900-2020. On the results page, we export the results as JSON. We use the data extracted pm 20201210 We have 68345 
-entries and the file has a size of about 326 MB (which is why it won't fit on GitHub). We call this file 1900-2020.json.
-
-OK 2. We split 1900-2020.json into smaller files that are easier handled and can be uploaded to GitHub. For this we use 
-_Utility.split_json and we end up with files of size 20 MB or less containing 5000 or less entries each. These files are
-called raw_master_x-y.json where x and y indicate the entries as given by 1900-2020.json. These files are saved under
-eodc/raw
-
-OK 3. We select a subset of the entries downloaded from edoc. We use Data.select_from_file to do so (for convencience on 
-1900-2020.json, but it could also be iteratively employed on the files in edoc/raw). The fields chosen are "title", 
-"abstract", "keywords" and "id_number". The rationale for choosing these fields is given elsewhere (in short: we need 
-items from which to construct a gold standard). The resulting 4111 items are saved as sample_master.json in 
-edoc/sample.
-
-ok 4. We extract the keywords (per entry) from the sample entries with Keywords.extract_keywords like so:
-keywords = Keywords.extract_keywords(DIR + "/sample/sample_master.json")
-We the save the resulting list under edoc/keywords as keywords_raw.json like so:
-_Utility.save_json(keywords, DIR + "/keywords/keywords_extracted.json")
-
[…]

### 2021-03-07 docs/conf.py
add documentation

@@ -1,0 +1,54 @@
+# Configuration file for the Sphinx documentation builder.
+#
+# This file only contains a selection of the most common options. For a full
+# list see the documentation:
+# https://www.sphinx-doc.org/en/master/usage/configuration.html
+
+# -- Path setup --------------------------------------------------------------
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#
+import os
+import sys
+sys.path.insert(0, os.path.abspath('..'))
+
+
+# -- Project information -----------------------------------------------------
+
+project = 'Machine indexing of institutional repositories: indexing Edoc with Annif as proof of concept'
+copyright = '2021, Maximilian Hindermann'
+author = 'Maximilian Hindermann'
+
+
+# -- General configuration ---------------------------------------------------
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = ['sphinx.ext.autodoc',
+              'sphinxcontrib.restbuilder',  # https://pythonhosted.org/sphinxcontrib-restbuilder/
+              'sphinx_autodoc_typehints',  # https://github.com/agronholm/sphinx-autodoc-typehints/blob/master/README.rst
+]
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# List of patterns, relative to source directory, that match files and
+# directories to ignore when looking for source files.
+# This pattern also affects html_static_path and html_extra_path.
+exclude_patterns = ['_build', 'Thumbs.db', '.DS_Store']
+
+
+# -- Options for HTML output -------------------------------------------------
+
+# The theme to use for HTML and HTML Help pages.  See the documentation for
+# a list of builtin themes.
+#
+html_theme = 'alabaster'
+
+# Add any paths that contain custom static files (such as style sheets) here,
+# relative to this directory. They are copied after the builtin static files,
+# so a file named "default.css" will overwrite the builtin "default.css".
+html_static_path = ['_static']

### 2021-03-07 files/__init__.py

@@ -68,7 +68,7 @@ class Utility:
 
 
 class Data:
-    """ A collection of edoc data functions. """
+    """ A collection of Edoc data functions. """
 
     @classmethod
     def select_from_data(cls,
@@ -140,7 +140,7 @@ class Data:
                                save_path: str) -> None:
         """ Enrich author keywords.
 
-        For each edoc item: the string of author keywords is cut into single keywords and each keyword is cleaned. Each
+        For each Edoc item: the string of author keywords is cut into single keywords and each keyword is cleaned. Each
         keyword is then enriched with Qid, MeSH and YSO ID if available.
 
         :param file_path: complete path to file including filename and extension
@@ -195,7 +195,7 @@ class Data:
     def enrich_with_mesh(cls,
                          file_path: str,
                          save_path: str) -> None:
-        """ Enrich edoc data per item with MeSH keywords from PubMed if available.
+        """ Enrich Edoc data per item with MeSH keywords from PubMed if available.
 
         :param file_path: complete path to file including filename and extension
         :param save_path: complete path to save folder including filename without extension
@@ -345,7 +345,7 @@ class Data:
 
 
 class Keywords:
-    """ A collection of functions for manipulating edoc author keywords. """
+    """ A collection of functions for manipulating Edoc author keywords. """
 
     @classmethod
     def extract_keywords(cls,

### 2021-03-08 text/draft.tex
refactor structure

@@
 \section{Introduction}\label{introduction}}
+
+In this section I will\ldots{}
+
+\hypertarget{problem-statement-and-goal}{%
+\subsection{Problem statement and
+goal}\label{problem-statement-and-goal}}
+
+Edoc is the institutional repository of the University of Basel. It runs
+on the EPrints 3 document management system
+(https://github.com/eprints/eprints). Edoc was conceived in 2009 as
+repository for electronic dissertations and grew in scope when the
+University of Basel adapted its first open access policy in 2013. Today
+Edoc contains roughly 68'000 items, most of them journal articles
+without full text support. Even though descriptive and administrative
+metadata are collected for each item, this does not include subject
+terms. The lack of subject indexing hampers the repository's usability
+and potential with respect to the topic-based monitoring of research
+output and, to a lesser extent, information retrieval. The goal of this
+project is to remedy this situation with the help of machine indexing.
+
+!! More precisely, this project aims to provide a roadmap for indexing
+the elements of Edoc with Annif (Suominen, 2018) -- an open source tool
+for automated subject indexing and classification -- and BARTOC FAST
+(Hindermann and Ledl, 2020), a federated asynchronous search tool that
+covers concepts of thousands of knowledge organization systems like
+thesauri, classifications etc.
+
+!! The goal of this thesis is to investigate to what extent machine
+indexing can be used to ameliorate institutional repositories.
 
@@
 
-\hypertarget{edoc-and-data-extraction}{%
-\subsection{Edoc and data extraction}\label{edoc-and-data-extraction}}
-
-Edoc is the institutional repository of the University of Basel. It was
-conceived in 2009 as repository for electronic dissertations and grew in
-scope when the University of Basel adapted its first open access policy
-in 2013. As per today Edoc contains roughly 68'000 items. Edoc runs on
-the EPrints 3 document management system
-(https://github.com/eprints/eprints).
+In this section, I will describe the Edoc data and how it was extracted.
+
+\hypertarget{edoc-data-extraction}{%
+\subsection{Edoc data extraction}\label{edoc-data-extraction}}
 
@@
 available search fields has to be filled in. The complete database can
-hence be extracted by only filling in the \texttt{Date} field and using
+hence be extracted by only filling in the \texttt{date} field and using
 a sufficiently permissive time period such as 1940 to 2020 since the
@@
 less containing 5000 or fewer entries each. These files are called
-\texttt{raw\_master\_x-y.json} (where x and y indicate the entries as
-given by \texttt{1942-2020.json}) and saved under \texttt{/edoc/raw}.
-
-\hypertarget{data-description-and-analysis}{%
-\subsection{Data description and
-analysis}\label{data-description-and-analysis}}
-
-!! Explain the Edoc data fields. Say perhaps something about the
-granularity of the relevant fields. Say something about how the fields
-are filled in (and by whom).
+\texttt{raw\_master\_\{year\}.json} and saved under \texttt{/files/raw}.
+
+\hypertarget{data-description}{%
+\subsection{Data description}\label{data-description}}
+
+Each Edoc item has 43 main data fields. Most of these data fields belong
+to the class of descriptive metadata. The data entry for an item's
+descriptive metadata is undertaken by the person who uploads the item
+which is in most cases one of the item's authors. The Note that an item
+is first uploaded to the University of Basel's research database
+(https://www.forschdb2.unibas.ch) before being automatically fed into
+Edoc. There are explicit rules on how to enter the data as summarized in
+the user manual (Universität Basel, n.d.). However, there is no (or at
+least no systematic) manual or automatic validation of the entered data.
+This means that some data fields are very heterogenous and require
+further parsing (see \protect\hyperlink{gold-standard}{section ``Gold
+standard''}). The data fields that are of interest to the project at
+hand are discussed in more detail in (see
+\protect\hyperlink{sample-data-set}{section ``Sample data set''} below).
 
@@
 In this section, I will explain how the sample data set is selected and
-constructed. ``Selection'' means the task of specifying a subset of the
-Edoc data and ``construction'' means the task of implementing this
-selection.
+constructed. ``Selection'' hereby means the task of specifying a subset
+of the Edoc data; by ``construction'' I mean the task of implementing
+this selection.
 
@@
 the out of the box instance of Annif employed in this chapter (see
-\protect\hyperlink{machine-indexing}{subsection ``Machine indexing''}).
+\protect\hyperlink{machine-indexing}{section ``Machine indexing''}).
 
@@
 employ any further restrictions. We can hence construct the sample data
-set by choosing exactly those items from \texttt{/edoc/raw} which have
+set by choosing exactly those items from \texttt{/files/raw} which have
 non-empty data fields \texttt{title}, \texttt{abstract},
@@
 \texttt{Data.select\_from\_file} iteratively for all files in
-\texttt{/edoc/raw}. The resulting file is saved in
-\texttt{/edoc/selected} as \texttt{selected\_master.json}.
+\texttt{/files/raw}. The resulting file is saved in
+\texttt{/files/selected} as \texttt{selected\_master.json}.
 
@@
 
-Of the 68'345 items in \texttt{/edoc/raw}, all have a title (non-empty
+\begin{figure}
+\centering
+\includegraphics{images/chi_square_selection_fields.pdf}
+\caption{The sample data set (\(n\) = 4'111) is not representative of
+the raw Edoc data per department. Data field \texttt{abstract}:
+\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
+\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
+field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
+The data foundation is available at
+\texttt{/files/analysis/chi\_square\_\{data\ field\}} and the
+\(\chi^2\)-statistic can be calculated by calling
+\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
+\end{figure}
+
+Of the 68'345 items in \texttt{/files/raw}, all have a title (non-empty
 \texttt{title} data field), a little more than half of the items have an
@@
 above data fields to be non-empty;
-\texttt{/edoc/sample/sample\_master.json} has 4'111 items and hence
+\texttt{/files/sample/sample\_master.json} has 4'111 items and hence
 constitutes 6\% of the raw data.
@@
 details).
-
-\begin{figure}
-\centering
-\includegraphics{images/chi_square_selection_fields.pdf}
-\caption{The sample data set (\(n\) = 4'111) is not representative of
-the raw Edoc data per department. Data field \texttt{abstract}:
-\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
-\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
-field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
-The data foundation is available at
-\texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and the
-\(\chi^2\)-statistic can be calculated by calling
-\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
-\end{figure}
 
@@
 \(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
-available at \texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and
+available at \texttt{/files/analysis/chi\_square\_\{data\ field\}} and
 the \(\chi^2\)-statistic can be calculated by calling
@@
 
-\hypertarget{general-overview}{%
-\subsection{General overview}\label{general-overview}}
-
-!! Give an overview over machine indexing.
+In this section, I will briefly introduce Annif and how indexing with
+Annif was implemented. For a general overview concerning machine
+indexing, see Golub (2019).
 
@@
 
-!! Given an intro to Annif. Explain that we are using the out of the box
-version
+Annif (Suominen et al. 2021) is an open source multi-algorithm automated
+indexing tool developed at the Finnish National Library (see Suominen
+2019 for an overview). Training a local Annif instance for machine
+indexing is currently evaluated at different libraries, for example at
+the German National Library (Nagelschmidt 12.11.2020). As stated in
+section \protect\hyperlink{introduction}{section ``Introduction''}, in
+this project I am interested in using Annif out of the box. This means
+that instead of training a local Annif instance, I will be relying on
+the Annif REST-style API (see https://api.annif.org/).\footnote{This API
+  is specifically intended for testing. For integration into a
+  production system, the Finto AI API is available (see
+  https://ai.finto.fi/v1/ui/).} The advantage of this approach is that
+it is quick and relatively easy to implement. The disadvantage is that
+no custom algorithms or vocabularies can be used. The task of
+constructing a gold standard (see
+\protect\hyperlink{gold-standard}{section ``Gold standard''}) remains
+the same.
 
@@
 latter case, at least with respect to YSO, there is a solution: Finto
-provides a REST-sytle API to access the YSO vocabulary directly (see
+provides a REST-style API to access the YSO vocabulary directly (see
 https://api.finto.fi/). For each keyword in the list of reference
@@
 departments have maximum weighted F1-scores that are well above the
-F1-score of 0.517 of the best performing general Annif configuration.
+weighted F1-score of 0.517 of the best performing general Annif
+configuration.
 
@@
 
+Codebase available at: \url{https://github.com/MHindermann/mas}
+
+\hypertarget{class-files.utility}{%
+\subsection{class files.Utility()}\label{class-files.utility}}
+
+A collection of utility functions.
+
+\hypertarget{classmethod-load_jsonfile_path}{%
+\subsubsection{classmethod
+load\_json(file\_path)}\label{classmethod-load_jsonfile_path}}
+
+Load a JSON object from file.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{file\_path} (\texttt{str}) -- complete path to file including
+  filename and extension
+\item
+  \textbf{Return type}
+
+  \texttt{list}
+\end{itemize}
+
+\hypertarget{classmethod-save_jsondata-file_path}{%
+\subsubsection{classmethod save\_json(data,
+file\_path)}\label{classmethod-save_jsondata-file_path}}
+
+Save data as JSON file.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{data} (\texttt{Union}{[}\texttt{List}, \texttt{Dict}{]}) --
+    the data to be saved
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-split_jsonfile_path-save_path}{%
+\subsubsection{classmethod split\_json(file\_path,
+save\_path)}\label{classmethod-split_jsonfile_path-save_path}}
+
+Split a JSON file into files not larger than 100MB.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
+    including filename without extension
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{class-files.data}{%
+\subsection{class files.Data()}\label{class-files.data}}
+
+A collection of Edoc data functions.
+
+\hypertarget{classmethod-enrich_author_keywordsfile_path-save_path}{%
+\subsubsection{classmethod enrich\_author\_keywords(file\_path,
+save\_path)}\label{classmethod-enrich_author_keywordsfile_path-save_path}}
+
+Enrich author keywords.
+
+For each Edoc item: the string of author keywords is cut into single
+keywords and each keyword is cleaned. Each keyword is then enriched with
+Qid, MeSH and YSO ID if available.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
+    including filename without extension
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-enrich_with_anniffile_path-save_path-project_ids-abstractfalse-fulltextfalse-limitnone-thresholdnone}{%
+\subsubsection{classmethod enrich\_with\_annif(file\_path, save\_path,
+project\_ids, abstract=False, fulltext=False, limit=None,
+threshold=None)}\label{classmethod-enrich_with_anniffile_path-save_path-project_ids-abstractfalse-fulltextfalse-limitnone-thresholdnone}}
+
+Enrich items from file with automatic keywords using Annif-client.
+
+Available Annif-client project IDs are yso-en, yso-maui-en,
+yso-bonsai-en, yso-fasttext-en, wikidata-en.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
+    including filename without extension
+  \item
+    \textbf{project\_ids} (\texttt{List}{[}\texttt{str}{]}) --
+    Annif-client project IDs to be used
+  \item
+    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
+    indexing, defaults to False
+  \item
+    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
+    indexing, defaults to False
+  \item
+    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
+    limit, defaults to None
+  \item
+    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
+    Annif-client threshold, defaults to None
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-enrich_with_meshfile_path-save_path}{%
+\subsubsection{classmethod enrich\_with\_mesh(file\_path,
+save\_path)}\label{classmethod-enrich_with_meshfile_path-save_path}}
+
+Enrich Edoc data per item with MeSH keywords from PubMed if available.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
+    including filename without extension
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-fetch_meshpubmed_id}{%
+\subsubsection{classmethod
+fetch\_mesh(pubmed\_id)}\label{classmethod-fetch_meshpubmed_id}}
+
+Fetch MeSH keywords for article based on PubMed ID.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{pubmed\_id} (\texttt{str}) -- article PubMed ID
+\item
+  \textbf{Return type}
+
+  \texttt{List}{[}\texttt{Dict}{]}
+\end{itemize}
+
+\hypertarget{classmethod-get_departments}{%
+\subsubsection{classmethod
+get\_departments()}\label{classmethod-get_departments}}
+
+Get all Edoc departments.
+
+\begin{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{List}{[}\texttt{str}{]}
+\end{itemize}
+
+\hypertarget{classmethod-inspectdata-fields}{%
+\subsubsection{classmethod inspect(data,
+*fields)}\label{classmethod-inspectdata-fields}}
+
+Print fields of items in data.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{data} (\texttt{List}{[}\texttt{Dict}{]}) -- data to be
+    inspected
+  \item
+    \textbf{fields} (\texttt{str}) -- fields to focus on
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-map2referencekeyword}{%
+\subsubsection{classmethod
+map2reference(keyword)}\label{classmethod-map2referencekeyword}}
+
+Map a keyword to its reference keyword.
+
+Keyword must first be cleaned by corresponding \_Keyword method.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{keyword} (\texttt{str}) -- the keyword
+\item
+  \textbf{Return type}
+
+  \texttt{Dict}
+\end{itemize}
+
+\hypertarget{classmethod-select_from_datadata-fields}{%
+\subsubsection{classmethod select\_from\_data(data,
+*fields)}\label{classmethod-select_from_datadata-fields}}
+
+Select items from data based on non-empty fields.
+
+Only items where all required fields are non-empty are sample.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{data} (\texttt{List}{[}\texttt{Dict}{]}) -- the input data
+  \item
+    \textbf{fields} (\texttt{str}) -- the required fields for an item to
+    be sample
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{List}{[}\texttt{Dict}{]}
+\end{itemize}
+
+\hypertarget{classmethod-select_from_filefile_path-fields}{%
+\subsubsection{classmethod select\_from\_file(file\_path,
+*fields)}\label{classmethod-select_from_filefile_path-fields}}
+
+Select items from file according to fields.
+
+For example: select\_from\_file(DIR + ``/raw/2019.json,'' ``title,''
+``abstract,'' ``keywords,'' ``id\_number'')
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{fields} (\texttt{str}) -- the required fields for an item to
+    be sample
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-super_enrich_with_annifabstract}{%
+\subsubsection{classmethod
+super\_enrich\_with\_annif(abstract)}\label{classmethod-super_enrich_with_annifabstract}}
+
+Enrich items with automatic keywords using all Annif-client projects.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{abstract} (\texttt{bool}) -- toggle use abstract for indexing
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{class-files.keywords}{%
+\subsection{class files.Keywords()}\label{class-files.keywords}}
+
+A collection of functions for manipulating Edoc author keywords.
+
+\hypertarget{classmethod-clean_keywordkeyword}{%
+\subsubsection{classmethod
+clean\_keyword(keyword)}\label{classmethod-clean_keywordkeyword}}
+
+Clean a keyword.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{keyword} (\texttt{str}) -- the keyword
+\item
+  \textbf{Return type}
+
+  \texttt{List}{[}\texttt{str}{]}
+\end{itemize}
+
+\hypertarget{classmethod-clean_keywordskeywords_per_item}{%
+\subsubsection{classmethod
+clean\_keywords(keywords\_per\_item)}\label{classmethod-clean_keywordskeywords_per_item}}
+
+Turn a string of keywords per item into a list of cleaned (=normalized)
+keywords.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{keywords\_per\_item} (\texttt{List}{[}\texttt{str}{]}) -- the
+  keywords
+\item
+  \textbf{Return type}
+
+  \texttt{List}{[}\texttt{str}{]}
+\end{itemize}
+
+\hypertarget{classmethod-enrich_with_ysofile_path-save_path}{%
+\subsubsection{classmethod enrich\_with\_yso(file\_path,
+save\_path)}\label{classmethod-enrich_with_ysofile_path-save_path}}
+
+Blah.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
+    including filename without extension
+  \end{itemize}
+\end{itemize}
+
+\hypertarget{classmethod-extract_keywordsfile_path}{%
+\subsubsection{classmethod
+extract\_keywords(file\_path)}\label{classmethod-extract_keywordsfile_path}}
+
+Extract keywords per item from file.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{file\_path} (\texttt{str}) -- complete path to file including
+  filename and extension
+\item
+  \textbf{Return type}
+
+  \texttt{List}{[}\texttt{str}{]}
+\end{itemize}
+
+\hypertarget{classmethod-fetch_ysokeyword}{%
+\subsection{classmethod
+fetch\_yso(keyword)}\label{classmethod-fetch_ysokeyword}}
+
+Fetch the YSO ID for a keyword if any.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{keyword} (\texttt{str}) -- the keyword
+\item
+  \textbf{Return type}
+
+  \texttt{Optional}{[}\texttt{str}{]}
+\end{itemize}
+
+\hypertarget{classmethod-make_countfile_path-save_path}{%
+\subsubsection{classmethod make\_count(file\_path,
+save\_path)}\label{classmethod-make_countfile_path-save_path}}
+
+Count all keywords and their respective IDs per item in file.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
+    including filename and extension
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-make_histogramkeywords}{%
+\subsubsection{classmethod
+make\_histogram(keywords)}\label{classmethod-make_histogramkeywords}}
+
+Make a histogram for keywords.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{keywords} (\texttt{List}{[}\texttt{str}{]}) -- the keywords
+\item
+  \textbf{Return type}
+
+  \texttt{List}{[}\texttt{Dict}{]}
+\end{itemize}
+
+\hypertarget{class-files.analysis}{%
+\subsection{class files.Analysis()}\label{class-files.analysis}}
+
+A collection of data analysis functions.
+
+\hypertarget{classmethod-count_confusionstandard-suggestions}{%
+\subsubsection{classmethod count\_confusion(standard,
+suggestions)}\label{classmethod-count_confusionstandard-suggestions}}
+
+Count the values in the confusion matrix for standard and suggestions.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{standard} (\texttt{list}) -- the standard
+  \item
+    \textbf{suggestions} (\texttt{list}) -- the suggestions
+  \end{itemize}
+\end{itemize}
+
+\hypertarget{classmethod-extract_standarditem-marker}{%
+\subsubsection{classmethod extract\_standard(item,
+marker)}\label{classmethod-extract_standarditem-marker}}
+
+Extract gold standard IDs from item.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{item} (\texttt{dict}) -- the Edoc item
+  \item
+    \textbf{marker} (\texttt{str}) -- the type of ID
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{Optional}{[}\texttt{list}{]}
+\end{itemize}
+
+\hypertarget{classmethod-extract_suggestionsitem-marker-n10}{%
+\subsubsection{classmethod extract\_suggestions(item, marker,
+n=10)}\label{classmethod-extract_suggestionsitem-marker-n10}}
+
+Extract top n Annif suggestion IDs from item.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{item} (\texttt{dict}) -- the Edoc item
+  \item
+    \textbf{marker} (\texttt{str}) --
+    project\_id-abstract-fulltext-limit-threshold
+  \item
+    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
+    extracted, defaults to 10
+  \end{itemize}
+\end{itemize}
+
+\hypertarget{classmethod-get_id_typemarker}{%
+\subsubsection{classmethod
+get\_id\_type(marker)}\label{classmethod-get_id_typemarker}}
+
+Get the ID type from the project ID.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{marker} (\texttt{str}) --
+  project\_id-abstract-fulltext-limit-threshold
+\item
+  \textbf{Return type}
+
+  \texttt{str}
+\end{itemize}
+
+\hypertarget{classmethod-get_sklearn_arrayitem-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10}{%
+\subsubsection{classmethod get\_sklearn\_array(item, project\_id,
+abstract=False, fulltext=False, limit=None, threshold=None,
+n=10)}\label{classmethod-get_sklearn_arrayitem-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10}}
+
+Get Sklearn y\_true and y\_pred for an item.
+
+Available Annif-client project IDs are yso-en, yso-maui-en,
+yso-bonsai-en, yso-fasttext-en, wikidata-en.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{item} (\texttt{dict}) -- sample data set item
+  \item
+    \textbf{project\_id} (\texttt{str}) -- Annif-client project ID
+  \item
+    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
+    indexing, defaults to False
+  \item
+    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
+    indexing, defaults to False
+  \item
+    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
+    limit, defaults to None
+  \item
+    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
+    Annif-client threshold, defaults to None
+  \item
+    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
+    extracted, defaults to 10
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{Optional}{[}\texttt{dict}{]}
+\end{itemize}
+
+\hypertarget{classmethod-make_metricsfile_path-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10-departmentnone}{%
+\subsubsection{classmethod make\_metrics(file\_path, project\_id,
+abstract=False, fulltext=False, limit=None, threshold=None, n=10,
+department=None)}\label{classmethod-make_metricsfile_path-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10-departmentnone}}
+
+Make Sklearn metrics F1, recall, precision for file.
+
+The output is saved as /metrics/metrics\_\{marker\}.json.
+
+Available Annif-client project IDs are yso-en, yso-maui-en,
+yso-bonsai-en, yso-fasttext-en, wikidata-en.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{project\_id} (\texttt{str}) -- Annif-client project ID
+  \item
+    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
+    indexing, defaults to False
+  \item
+    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
+    indexing, defaults to False
+  \item
+    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
+    limit, defaults to None
+  \item
+    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
+    Annif-client threshold, defaults to None
+  \item
+    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
+    extracted per item, defaults to 10
+  \item
+    \textbf{department} (\texttt{Optional}{[}\texttt{str}{]}) --
+    restrict to items from department
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-make_random_samplefile_path-save_path-size}{%
+\subsubsection{classmethod make\_random\_sample(file\_path, save\_path,
+size)}\label{classmethod-make_random_samplefile_path-save_path-size}}
+
+Save a random sample from the population in the file.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
+    including filename and extension
+  \item
+    \textbf{size} (\texttt{int}) -- the sample size
+  \end{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-print_chi_square_fitfile_path}{%
+\subsubsection{classmethod
+print\_chi\_square\_fit(file\_path)}\label{classmethod-print_chi_square_fitfile_path}}
+
+Print chi square goodness of fit.
+
+File must be CSV with first line title; three columns with first column
+categories, second column expected and third column observed values.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \textbf{file\_path} (\texttt{str}) -- complete path to file including
+  filename and extension
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
+\hypertarget{classmethod-super_make_metricsfile_path-departmentnone}{%
+\subsubsection{classmethod super\_make\_metrics(file\_path,
+department=None)}\label{classmethod-super_make_metricsfile_path-departmentnone}}
+
+Make metrics for all combinations of Annif projects and parameters in
+enriched Edoc file.
+
+Output files are saved in /metrics/. Joint results are saved in
+/analysis/metrics.json.
+
+\begin{itemize}
+\item
+  \textbf{Parameters}
+
+  \begin{itemize}
+  \item
+    \textbf{file\_path} (\texttt{str}) -- complete path to file
+    including filename and extension
+  \item
+    \textbf{department} (\texttt{Optional}{[}\texttt{str}{]}) --
+    restrict to items from department
+  \end{itemize}
+\end{itemize}
+
+\hypertarget{classmethod-super_make_stats}{%
+\subsubsection{classmethod
+super\_make\_stats()}\label{classmethod-super_make_stats}}
+
+Make metrics for files in /metrics.
+
+Output is saved as /analysis/metrics.json.
+
+\begin{itemize}
+\item
+  \textbf{Return type}
+
+  \texttt{None}
+\end{itemize}
+
 \hypertarget{bibliography}{%
@@
 
+\leavevmode\hypertarget{ref-Golub.2019}{}%
+Golub, Koraljka. 2019. {``Automatic Subject Indexing of Text.''}
+\emph{Knowledge Organization} 46 (2): 104--21.
+\url{https://doi.org/10.5771/0943-7444-2019-2-104}.
+
 \leavevmode\hypertarget{ref-Golub.2016}{}%
@@
 
+\leavevmode\hypertarget{ref-Nagelschmidt.12.11.2020}{}%
+Nagelschmidt, Matthias. 12.11.2020. {``Evaluation von Annif f{ü}r Die
+Maschinelle Inhaltserschlie{ß}ung an Der Deutschen
+Nationalbibliothek.''}
+\url{https://wiki.dnb.de/download/attachments/181735291/07-EvaluationVonAnnif.pdf?version=1\&modificationDate=1605778295000\&api=v2}.
+
 \leavevmode\hypertarget{ref-Parke.2013}{}%
@@
 
+\leavevmode\hypertarget{ref-Suominen.2021}{}%
+Suominen, Osma, Juho Inkinen, Tuomo Virolainen, Moritz Fürneisen, Bruno
+P. Kinoshita, Sara Veldhoen, Mats Sjöberg, Philipp Zumstein, Robin
+Neatherway, and monalehtinen. 2021. {``NatLibFi/Annif: Annif 0.51.''}
+\url{https://doi.org/10.5281/zenodo.4521923}.
+
 \leavevmode\hypertarget{ref-Toepfer.2016}{}%

### 2021-03-08 text/draft.tex
machine indexing

@@
 
+Annif vocs that are available
+
 \hypertarget{implementation}{%
@@
 
-As explained above, for the prototype we will use the out
-
-!! Explain how to implementation works.
-
-In addition to the already used algorithms we should also try
-https://ai.finto.fi/?locale=en
-
-!! Somewhere here we talk about indexing based on title and/or abstract
-and/or fulltext. Fulltext is not yet implemented. Some observations to
-do so: - the link to the fulltext is constructed from the data fields
-\texttt{offical\ url} and \texttt{documebts\ -\ main}, e.g.,
-\texttt{https\ \ ://edoc.unibas.ch/79633/} + \texttt{1/} +
-\texttt{2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}
-to get
-\texttt{https://edoc.unibas.ch/79633/1/2020\_18\_Informed\ by\ wet\ feet\_How\ do\ floods\ affect\ property\ prices.pdf}
+Machine indexing with Annif was implemented using the annif-client
+Python library (see https://pypi.org/project/annif-client/). The desired
+output is that every item in the Edoc sample data set is assigned
+subject terms by all available Annif API projects (namely,
+\texttt{yso-en}, \texttt{yso-maui-en}, \texttt{yso-bonsai-en},
+\texttt{yso-fasttext-en}, \texttt{wikidata-en}) based on all available
+text bases (title or title and abstract). In order to distinguish these
+assignments, we use a unique ID (called ``marker'' in what follows) for
+each Annif configuration. A marker is constructed by the convention:
+\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}},
+where \texttt{project\_id} is the Annif project, \texttt{abstract} and
+\texttt{fulltext} are boolean variables, \texttt{n} is the maximum
+number of suggestions per item, and \texttt{threshold} is a variable for
+a threshold Annif score.
+
+In order to generate the ouput, we call
+\texttt{Data.super\_enrich\_with\_annif}, thereby iteratively calling
+\texttt{Data.enrich\_with\_annif} for all items in
+\texttt{/files/sample/sample\_master.json} for all Annif projects. The
+output is saved in \texttt{/indexed/} as \texttt{indexed\_master.json}.
 
@@
 
-The construction of the derivative gold standard takes x steps:
+The construction of the derivative gold standard takes three steps:
 
@@
 \item
-  Extract the keywords from the sample data set.\\
+  Extract the keywords from the sample data set.
 \item
@@
 \item
-  Reconcile the extracted keywords with\ldots{}
+  Reconcile the extracted keywords with.
 \end{enumerate}
@@
 text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
-Each configuration has a unique ID (called ``marker'' in what follows)
-constructed by the convention:
-\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}}
-where \texttt{project\_id} is the Annif project, \texttt{abstract} and
-\texttt{fulltext} are boolean variables, \texttt{n} is the maximum
-number of suggestions per item, and \texttt{threshold} is a variable for
-a threshold Annif score.
+Remember the convention for constructing the marker that identifies a
+configuration (see \protect\hyperlink{annif}{section ``Annif''}):
+\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}}.
 

### 2021-03-08 text/draft.tex
machine indexing

@@
 
-Annif vocs that are available
+The vocabularies provided by the Annif API are the General Finnish
+Ontology or YSO in short (see https://finto.fi/yso/en/) and Wikidata
+(see https://www.wikidata.org/). Each vocabulary is combined with an
+algorithm or algorithm ensemble respectively and a specific language to
+create a so-called Annif ``project.'' The five projects used in what
+follows are summarized in Table 1. A high-level description of the
+algorithm(s) is given by Suominen (2019, 7--10). Information on
+implementation can be found at the Annif GitHub Wiki (see
+https://github.com/NatLibFi/Annif/wiki).
+
+\begin{table}[]
+\centering
+\begin{tabular}{llll}
+Annif project   & Vocabulary & Language & Algorithm(s)   \\ \hline
+\texttt{yso-en}  & YSO        & English  & NN ensemble \\
+\texttt{yso-maui-en}     & YSO        & English  & Maui        \\
+\texttt{yso-bonsai-en}   & YSO        & English  & Omikuji     \\
+\texttt{yso-fasttext-en} & YSO        & English  & fastText    \\
+\texttt{wikidata-en}     & Wikidata   & English  & TF-IDF     
+\end{tabular}
+\caption{Annif projects used to index the items of the Edoc sample data set.}
+\label{tab:my-table}
+\end{table}
 
@@
 \item
-  Reconcile the extracted keywords with.
+  Reconcile the extracted keywords with Wikidata and YSO.
 \end{enumerate}
-
-The intended output of this transformation process is\ldots{}
 
@@
 \begin{Highlighting}[]
-\NormalTok{keywords }\OperatorTok{=}\NormalTok{ Keywords.extract\_keywords(DIR }\OperatorTok{+} \StringTok{"/sample/sample\_master.json"}\NormalTok{)}
-\NormalTok{Utility.save\_json(keywords, DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
+\NormalTok{keywords }\OperatorTok{=}\NormalTok{ Keywords.extract\_keywords(}\StringTok{"/sample/sample\_master.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords, }\StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
+\NormalTok{keywords\_extracted }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_extracted.json"}\NormalTok{)}
 \NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Keywords.clean\_keywords(keywords\_extracted)}
-\NormalTok{Utility.save\_json(keywords\_clean, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords\_clean, }\StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
+\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
 \NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ Keywords.make\_histogram(keywords\_clean)}
-\NormalTok{Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master.json"}\NormalTok{)}
+\NormalTok{sample\_data\_set }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/indexed/indexed\_master.json"}\NormalTok{)}
 \NormalTok{keywords\_counted }\OperatorTok{=}\NormalTok{ Keywords.make\_count(sample\_data\_set)}
-\NormalTok{Utility.save\_json(keywords\_counted, DIR }\OperatorTok{+} \StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords\_counted, }\StringTok{"/analysis/keywords\_counted.json"}\NormalTok{)}
 \end{Highlighting}
@@
 of view: when it comes to subject indexing, some terms are required, but
-more is usually worse {[}!! source{]}. Items with too few or too many
-keywords will be discussed in more detail in section
-\protect\hyperlink{assessment}{section Assessment}
+more is usually worse. Items with too few or too many keywords will be
+discussed in more detail in section
+\protect\hyperlink{assessment}{section ``Assessment''}
 
@@
 
-As explained in section X, Annif assigns index terms from a controlled
-vocabulary. If we want to assess the quality of the indexing via a gold
-standard, we must therefore ensure that the gold standard makes use of
-the vocabulary used by Annif. As seen in section Y, the relevant
-(English) vocabularies are Wikidata YSO. The next step in constructing
-the derivative gold standard is hence to match the extracted and cleaned
-keywords with keywords from YSO and Wikidata. This process is called
-``reconciliation'' (see https://docs.openrefine.org/manual/reconciling)
-and the tool of choice for this task is OpenRefine (see
-\protect\hyperlink{openrefine}{section OpenRefine}).
-
-In this section, I will describe how the cleaned keywords were
+As explained in \protect\hyperlink{machine-indexing}{section ``Machine
+indexing''}, Annif assigns index terms from a controlled vocabulary. If
+we want to assess the quality of the indexing via a gold standard, we
+must therefore ensure that the gold standard makes use of the vocabulary
+used by Annif. The relevant (English) vocabularies are Wikidata and YSO.
+The next step in constructing the derivative gold standard is hence to
+match the extracted and cleaned keywords with keywords from Wikidata and
+YSO. This process is called ``reconciliation'' (see
+https://docs.openrefine.org/manual/reconciling) and the tool of choice
+for this task is OpenRefine (see
+\protect\hyperlink{introduction}{section ``Introduction''}).
+
+In what follows, I will describe how the cleaned keywords were
 reconciled with Wikidata and YSO, and which additional steps for
@@
 https://github.com/OpenRefine/OpenRefine/wiki/Reconciliation-Service-API
-for details). For example, {[}keyword/article{]}. To generalize,
-suggestions with types whose concepts are proper names are usually
-incorrect. Based on this observation, suggestions with the following
-types were rejected: ``scholarly article,'' ``clinical trial,''
-``scientific journal,'' ``academic journal,'' ``open access journal,''
-``thesis,'' ``doctoral thesis,'' ``natural number.'' Suggestions with
-the following types were manually verified (i.e., checked for
-correctness): ``human,'' ``album,'' ``film,'' ``musical group,''
-``business,'' ``literary work,'' ``television series,''
-``organization,'' ``family name,'' ``written work,'' ``video game,''
-``single, television series episode,'' ``painting,'' ``commune of
-France,'' ``city of the United States,'' ``magazine,'' ``studio album,''
-``year,'' ``nonprofit organization,'' ``border town,'' ``international
-organization,'' ``political party,'' ``software,'' ``song,''
-``website,'' ``article comic strip,'' ``collection,'' ``commune of
-Italy,'' ``fictional human,'' ``film,'' ``government agency,''
-``village,'' ``academic journal article,'' ``female given name,''
-``poem.''
+for details). To generalize, suggestions with types whose concepts are
+proper names are usually incorrect. Based on this observation,
+suggestions with types such as ``scholarly article,'' ``clinical
+trial,'' and ``scientific journal'' were rejected.\footnote{The complete
+  list includes ``academic journal,'' ``open access journal,''
+  ``thesis,'' ``doctoral thesis,'' and ``natural number.''} Suggestions
+types such as ``human,'' ``album,'' and ``commune of France'' were
+manually verified (i.e., checked for correctness).\footnote{The complete
+  list includes ``film,'' ``musical group,'' ``business,'' ``literary
+  work,'' ``television series,'' ``organization,'' ``family name,''
+  ``written work,'' ``video game,'' ``single, television series
+  episode,'' ``painting,'' , ``city of the United States,''
+  ``magazine,'' ``studio album,'' ``year,'' ``nonprofit organization,''
+  ``border town,'' ``international organization,'' ``political party,''
+  ``software,'' ``song,'' ``website,'' ``article comic strip,''
+  ``collection,'' ``commune of Italy,'' ``fictional human,'' ``film,''
+  ``government agency,'' ``village,'' ``academic journal article,''
+  ``female given name,'' and ``poem.''}
 
@@
 \begin{Highlighting}[]
-\NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
+\NormalTok{keywords\_reference }\OperatorTok{=}\NormalTok{ Utility.load\_json(}\StringTok{"/keywords/keywords\_reference.json"}\NormalTok{)}
 \NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ Keywords.enrich\_with\_yso(keywords\_reference)}
-\NormalTok{Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
 \end{Highlighting}
@@
 In this section I will assess the quality of the sample data set's
-indexing with Annif based on the gold standard.
+indexing by Annif based on the gold standard.
 
@@
 only if the subject term is in the derivative gold standard. The
-possible outcomes are summarized in Table 1.
+possible outcomes are summarized in Table 2.
 
@@
 The above scoring metrics were implemented using the scikit-learn
-machine learning library (Pedregosa et al. 2011). For a given Annif
-configuration
-(\protect\hyperlink{annif-versus-derivative-gold-standard}{section
-``Annif versus derivative gold standard''})\ldots{} {[}perhaps explain
-how it is done, important to mention transformation of multilabel to
-binary{]}.
+machine learning library (Pedregosa et al. 2011).
 
@@
 \begin{Highlighting}[]
-\NormalTok{Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master.json"}\NormalTok{)}
+\NormalTok{Analysis.super\_make\_metrics(}\StringTok{"/indexed/indexed\_master.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \caption{Distribution of weighted F1-scores per maximum number of
-suggestions 1 \(\leq\) n \(\leq\) 10. See Table 2 for numeric values. n
+suggestions 1 \(\leq\) n \(\leq\) 10. See Table 3 for numeric values. n
 = 2 is the best perfomring type of configuration. However, it is
@@
 \ControlFlowTok{for}\NormalTok{ dept }\KeywordTok{in}\NormalTok{ Data.get\_departments():}
-\NormalTok{    Analysis.super\_make\_metrics(DIR }\OperatorTok{+} \StringTok{"/indexed/indexed\_master.json"}\NormalTok{, dept)}
+\NormalTok{    Analysis.super\_make\_metrics(}\StringTok{"/indexed/indexed\_master.json"}\NormalTok{, dept)}
 \end{Highlighting}

### 2021-03-08 text/draft.tex
machine indexing

@@
 
-In this section I will\ldots{}
+In this section, the problem and goal of this project are stated and the
+employed methodology is outlined.
 
@@
 
-\hypertarget{outline}{%
-\subsection{Outline}\label{outline}}
-
 Let us start by stating the aim of the prototype. From a functional
@@
 In the sections below, these steps will be discussed in detail.
-
-\hypertarget{tools}{%
-\subsection{Tools}\label{tools}}
-
-For data refinement I use OpenRefine version 3.4.1
-(https://openrefine.org/). Data manipulation in OpenRefine is tracked:
-the manipulation history of some data can be exported as JSON file and
-then reproduced (on the same data on a different machine or on different
-data) by loading said file. I will supply a corresponding manipulation
-history whenever appropriate. Note that when using OpenRefine with
-larger files (and there are many such files in this project), the memory
-allocation to OpenRefine must be manually increased (see
-https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation
-for details). Also note that OpenRefine always counts the number of
-records by the first column (a fact which caused me many headaches).
 
@@
 less containing 5000 or fewer entries each. These files are called
-\texttt{raw\_master\_\{year\}.json} and saved under \texttt{/files/raw}.
+\texttt{raw\_master\_\{year\}.json} and saved under \texttt{/raw}.
 
@@
 employ any further restrictions. We can hence construct the sample data
-set by choosing exactly those items from \texttt{/files/raw} which have
+set by choosing exactly those items from \texttt{/raw} which have
 non-empty data fields \texttt{title}, \texttt{abstract},
@@
 \texttt{Data.select\_from\_file} iteratively for all files in
-\texttt{/files/raw}. The resulting file is saved in
-\texttt{/files/selected} as \texttt{selected\_master.json}.
+\texttt{/raw}. The resulting file is saved in \texttt{/selected} as
+\texttt{selected\_master.json}.
 
@@
 The data foundation is available at
-\texttt{/files/analysis/chi\_square\_\{data\ field\}} and the
+\texttt{/analysis/chi\_square\_\{data\ field\}} and the
 \(\chi^2\)-statistic can be calculated by calling
@@
 
-Of the 68'345 items in \texttt{/files/raw}, all have a title (non-empty
+Of the 68'345 items in \texttt{/raw}, all have a title (non-empty
 \texttt{title} data field), a little more than half of the items have an
@@
 \texttt{keywords} data field). The sample data set as requires all the
-above data fields to be non-empty;
-\texttt{/files/sample/sample\_master.json} has 4'111 items and hence
-constitutes 6\% of the raw data.
+above data fields to be non-empty; \texttt{/sample/sample\_master.json}
+has 4'111 items and hence constitutes 6\% of the raw data.
 
@@
 \(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
-available at \texttt{/files/analysis/chi\_square\_\{data\ field\}} and
-the \(\chi^2\)-statistic can be calculated by calling
+available at \texttt{/analysis/chi\_square\_\{data\ field\}} and the
+\(\chi^2\)-statistic can be calculated by calling
 \texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
@@
 \texttt{Data.enrich\_with\_annif} for all items in
-\texttt{/files/sample/sample\_master.json} for all Annif projects. The
-output is saved in \texttt{/indexed/} as \texttt{indexed\_master.json}.
+\texttt{/sample/sample\_master.json} for all Annif projects. The output
+is saved in \texttt{/indexed/} as \texttt{indexed\_master.json}.
 
@@
 https://docs.openrefine.org/manual/reconciling) and the tool of choice
-for this task is OpenRefine (see
-\protect\hyperlink{introduction}{section ``Introduction''}).
+for this task is OpenRefine).\footnote{For data refinement I use
+  OpenRefine version 3.4.1 (https://openrefine.org/). Data manipulation
+  in OpenRefine is tracked: the manipulation history of some data can be
+  exported as JSON file and then reproduced (on the same data on a
+  different machine or on different data) by loading said file. I will
+  supply a corresponding manipulation history whenever appropriate. Note
+  that when using OpenRefine with larger files (and there are many such
+  files in this project), the memory allocation to OpenRefine must be
+  manually increased (see
+  https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation
+  for details). Also note that OpenRefine always counts the number of
+  records by the first column (a fact which caused me many headaches).}
 
@@
 
-In this section I will discuss the general results of assessing the
+In what follows I will discuss the general results of assessing the
 performance of the 100 Annif configurations versus the derivative gold
@@
 \protect\hyperlink{creating-the-data-foundation}{section ``Creating the
-data foundation''}: if anything, the performance for the extended text
+data foundation''}): if anything, the performance for the extended text
 basis was slightly worse (see Figure 6, right). There is again no easy
@@
 have identified and discussed the overall best Annif configerations.
-However, in \protect\hyperlink{analysis}{section ``Analysis''}) I had
-also noted the caveat that the performance of Annif might vary according
-to department due to systematic biases in constructing the Edoc sample
-data set. In this section I will therefore assess the performance of the
+However, in \protect\hyperlink{analysis}{section ``Analysis''}, I had
+noted the caveat that the performance of Annif might vary according to
+department due to systematic biases in constructing the Edoc sample data
+set. In this section I will therefore assess the performance of the
 various Annif configurations per department.
@@
 
-\hypertarget{outlook-and-conclusion}{%
-\section{Outlook and conclusion}\label{outlook-and-conclusion}}
-
-\hypertarget{refinement}{%
-\subsection{Refinement}\label{refinement}}
+\hypertarget{conclusion-and-outlook}{%
+\section{Conclusion and outlook}\label{conclusion-and-outlook}}
+
+In this section, ..
+
+\hypertarget{recommendation}{%
+\subsection{Recommendation}\label{recommendation}}
 
@@
 
-\hypertarget{implementation-strategy}{%
-\subsection{Implementation strategy}\label{implementation-strategy}}
+\hypertarget{further-research}{%
+\subsection{Further research}\label{further-research}}
+
+Apart from implementing a production system as discussed above, natural
+next steps to build on this project include:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  mesh
+\item
+  full text
+\item
+  german vocabulary
+\item
+  select domain specific vocabularies with bartoc suggest
+\end{enumerate}
 
@@
 
-Codebase available at: \url{https://github.com/MHindermann/mas}
-
-\hypertarget{class-files.utility}{%
-\subsection{class files.Utility()}\label{class-files.utility}}
-
-A collection of utility functions.
-
-\hypertarget{classmethod-load_jsonfile_path}{%
-\subsubsection{classmethod
-load\_json(file\_path)}\label{classmethod-load_jsonfile_path}}
-
-Load a JSON object from file.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{file\_path} (\texttt{str}) -- complete path to file including
-  filename and extension
-\item
-  \textbf{Return type}
-
-  \texttt{list}
-\end{itemize}
-
-\hypertarget{classmethod-save_jsondata-file_path}{%
-\subsubsection{classmethod save\_json(data,
-file\_path)}\label{classmethod-save_jsondata-file_path}}
-
-Save data as JSON file.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{data} (\texttt{Union}{[}\texttt{List}, \texttt{Dict}{]}) --
-    the data to be saved
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-split_jsonfile_path-save_path}{%
-\subsubsection{classmethod split\_json(file\_path,
-save\_path)}\label{classmethod-split_jsonfile_path-save_path}}
-
-Split a JSON file into files not larger than 100MB.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
-    including filename without extension
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{class-files.data}{%
-\subsection{class files.Data()}\label{class-files.data}}
-
-A collection of Edoc data functions.
-
-\hypertarget{classmethod-enrich_author_keywordsfile_path-save_path}{%
-\subsubsection{classmethod enrich\_author\_keywords(file\_path,
-save\_path)}\label{classmethod-enrich_author_keywordsfile_path-save_path}}
-
-Enrich author keywords.
-
-For each Edoc item: the string of author keywords is cut into single
-keywords and each keyword is cleaned. Each keyword is then enriched with
-Qid, MeSH and YSO ID if available.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
-    including filename without extension
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-enrich_with_anniffile_path-save_path-project_ids-abstractfalse-fulltextfalse-limitnone-thresholdnone}{%
-\subsubsection{classmethod enrich\_with\_annif(file\_path, save\_path,
-project\_ids, abstract=False, fulltext=False, limit=None,
-threshold=None)}\label{classmethod-enrich_with_anniffile_path-save_path-project_ids-abstractfalse-fulltextfalse-limitnone-thresholdnone}}
-
-Enrich items from file with automatic keywords using Annif-client.
-
-Available Annif-client project IDs are yso-en, yso-maui-en,
-yso-bonsai-en, yso-fasttext-en, wikidata-en.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
-    including filename without extension
-  \item
-    \textbf{project\_ids} (\texttt{List}{[}\texttt{str}{]}) --
-    Annif-client project IDs to be used
-  \item
-    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
-    indexing, defaults to False
-  \item
-    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
-    indexing, defaults to False
-  \item
-    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
-    limit, defaults to None
-  \item
-    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
-    Annif-client threshold, defaults to None
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-enrich_with_meshfile_path-save_path}{%
-\subsubsection{classmethod enrich\_with\_mesh(file\_path,
-save\_path)}\label{classmethod-enrich_with_meshfile_path-save_path}}
-
-Enrich Edoc data per item with MeSH keywords from PubMed if available.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
-    including filename without extension
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-fetch_meshpubmed_id}{%
-\subsubsection{classmethod
-fetch\_mesh(pubmed\_id)}\label{classmethod-fetch_meshpubmed_id}}
-
-Fetch MeSH keywords for article based on PubMed ID.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{pubmed\_id} (\texttt{str}) -- article PubMed ID
-\item
-  \textbf{Return type}
-
-  \texttt{List}{[}\texttt{Dict}{]}
-\end{itemize}
-
-\hypertarget{classmethod-get_departments}{%
-\subsubsection{classmethod
-get\_departments()}\label{classmethod-get_departments}}
-
-Get all Edoc departments.
-
-\begin{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{List}{[}\texttt{str}{]}
-\end{itemize}
-
-\hypertarget{classmethod-inspectdata-fields}{%
-\subsubsection{classmethod inspect(data,
-*fields)}\label{classmethod-inspectdata-fields}}
-
-Print fields of items in data.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{data} (\texttt{List}{[}\texttt{Dict}{]}) -- data to be
-    inspected
-  \item
-    \textbf{fields} (\texttt{str}) -- fields to focus on
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-map2referencekeyword}{%
-\subsubsection{classmethod
-map2reference(keyword)}\label{classmethod-map2referencekeyword}}
-
-Map a keyword to its reference keyword.
-
-Keyword must first be cleaned by corresponding \_Keyword method.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{keyword} (\texttt{str}) -- the keyword
-\item
-  \textbf{Return type}
-
-  \texttt{Dict}
-\end{itemize}
-
-\hypertarget{classmethod-select_from_datadata-fields}{%
-\subsubsection{classmethod select\_from\_data(data,
-*fields)}\label{classmethod-select_from_datadata-fields}}
-
-Select items from data based on non-empty fields.
-
-Only items where all required fields are non-empty are sample.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{data} (\texttt{List}{[}\texttt{Dict}{]}) -- the input data
-  \item
-    \textbf{fields} (\texttt{str}) -- the required fields for an item to
-    be sample
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{List}{[}\texttt{Dict}{]}
-\end{itemize}
-
-\hypertarget{classmethod-select_from_filefile_path-fields}{%
-\subsubsection{classmethod select\_from\_file(file\_path,
-*fields)}\label{classmethod-select_from_filefile_path-fields}}
-
-Select items from file according to fields.
-
-For example: select\_from\_file(DIR + ``/raw/2019.json,'' ``title,''
-``abstract,'' ``keywords,'' ``id\_number'')
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{fields} (\texttt{str}) -- the required fields for an item to
-    be sample
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-super_enrich_with_annifabstract}{%
-\subsubsection{classmethod
-super\_enrich\_with\_annif(abstract)}\label{classmethod-super_enrich_with_annifabstract}}
-
-Enrich items with automatic keywords using all Annif-client projects.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{abstract} (\texttt{bool}) -- toggle use abstract for indexing
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{class-files.keywords}{%
-\subsection{class files.Keywords()}\label{class-files.keywords}}
-
-A collection of functions for manipulating Edoc author keywords.
-
-\hypertarget{classmethod-clean_keywordkeyword}{%
-\subsubsection{classmethod
-clean\_keyword(keyword)}\label{classmethod-clean_keywordkeyword}}
-
-Clean a keyword.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{keyword} (\texttt{str}) -- the keyword
-\item
-  \textbf{Return type}
-
-  \texttt{List}{[}\texttt{str}{]}
-\end{itemize}
-
-\hypertarget{classmethod-clean_keywordskeywords_per_item}{%
-\subsubsection{classmethod
-clean\_keywords(keywords\_per\_item)}\label{classmethod-clean_keywordskeywords_per_item}}
-
-Turn a string of keywords per item into a list of cleaned (=normalized)
-keywords.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{keywords\_per\_item} (\texttt{List}{[}\texttt{str}{]}) -- the
-  keywords
-\item
-  \textbf{Return type}
-
-  \texttt{List}{[}\texttt{str}{]}
-\end{itemize}
-
-\hypertarget{classmethod-enrich_with_ysofile_path-save_path}{%
-\subsubsection{classmethod enrich\_with\_yso(file\_path,
-save\_path)}\label{classmethod-enrich_with_ysofile_path-save_path}}
-
-Blah.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
-    including filename without extension
-  \end{itemize}
-\end{itemize}
-
-\hypertarget{classmethod-extract_keywordsfile_path}{%
-\subsubsection{classmethod
-extract\_keywords(file\_path)}\label{classmethod-extract_keywordsfile_path}}
-
-Extract keywords per item from file.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{file\_path} (\texttt{str}) -- complete path to file including
-  filename and extension
-\item
-  \textbf{Return type}
-
-  \texttt{List}{[}\texttt{str}{]}
-\end{itemize}
-
-\hypertarget{classmethod-fetch_ysokeyword}{%
-\subsection{classmethod
-fetch\_yso(keyword)}\label{classmethod-fetch_ysokeyword}}
-
-Fetch the YSO ID for a keyword if any.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{keyword} (\texttt{str}) -- the keyword
-\item
-  \textbf{Return type}
-
-  \texttt{Optional}{[}\texttt{str}{]}
-\end{itemize}
-
-\hypertarget{classmethod-make_countfile_path-save_path}{%
-\subsubsection{classmethod make\_count(file\_path,
-save\_path)}\label{classmethod-make_countfile_path-save_path}}
-
-Count all keywords and their respective IDs per item in file.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
-    including filename and extension
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-make_histogramkeywords}{%
-\subsubsection{classmethod
-make\_histogram(keywords)}\label{classmethod-make_histogramkeywords}}
-
-Make a histogram for keywords.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{keywords} (\texttt{List}{[}\texttt{str}{]}) -- the keywords
-\item
-  \textbf{Return type}
-
-  \texttt{List}{[}\texttt{Dict}{]}
-\end{itemize}
-
-\hypertarget{class-files.analysis}{%
-\subsection{class files.Analysis()}\label{class-files.analysis}}
-
-A collection of data analysis functions.
-
-\hypertarget{classmethod-count_confusionstandard-suggestions}{%
-\subsubsection{classmethod count\_confusion(standard,
-suggestions)}\label{classmethod-count_confusionstandard-suggestions}}
-
-Count the values in the confusion matrix for standard and suggestions.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{standard} (\texttt{list}) -- the standard
-  \item
-    \textbf{suggestions} (\texttt{list}) -- the suggestions
-  \end{itemize}
-\end{itemize}
-
-\hypertarget{classmethod-extract_standarditem-marker}{%
-\subsubsection{classmethod extract\_standard(item,
-marker)}\label{classmethod-extract_standarditem-marker}}
-
-Extract gold standard IDs from item.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{item} (\texttt{dict}) -- the Edoc item
-  \item
-    \textbf{marker} (\texttt{str}) -- the type of ID
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{Optional}{[}\texttt{list}{]}
-\end{itemize}
-
-\hypertarget{classmethod-extract_suggestionsitem-marker-n10}{%
-\subsubsection{classmethod extract\_suggestions(item, marker,
-n=10)}\label{classmethod-extract_suggestionsitem-marker-n10}}
-
-Extract top n Annif suggestion IDs from item.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{item} (\texttt{dict}) -- the Edoc item
-  \item
-    \textbf{marker} (\texttt{str}) --
-    project\_id-abstract-fulltext-limit-threshold
-  \item
-    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
-    extracted, defaults to 10
-  \end{itemize}
-\end{itemize}
-
-\hypertarget{classmethod-get_id_typemarker}{%
-\subsubsection{classmethod
-get\_id\_type(marker)}\label{classmethod-get_id_typemarker}}
-
-Get the ID type from the project ID.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{marker} (\texttt{str}) --
-  project\_id-abstract-fulltext-limit-threshold
-\item
-  \textbf{Return type}
-
-  \texttt{str}
-\end{itemize}
-
-\hypertarget{classmethod-get_sklearn_arrayitem-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10}{%
-\subsubsection{classmethod get\_sklearn\_array(item, project\_id,
-abstract=False, fulltext=False, limit=None, threshold=None,
-n=10)}\label{classmethod-get_sklearn_arrayitem-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10}}
-
-Get Sklearn y\_true and y\_pred for an item.
-
-Available Annif-client project IDs are yso-en, yso-maui-en,
-yso-bonsai-en, yso-fasttext-en, wikidata-en.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{item} (\texttt{dict}) -- sample data set item
-  \item
-    \textbf{project\_id} (\texttt{str}) -- Annif-client project ID
-  \item
-    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
-    indexing, defaults to False
-  \item
-    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
-    indexing, defaults to False
-  \item
-    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
-    limit, defaults to None
-  \item
-    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
-    Annif-client threshold, defaults to None
-  \item
-    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
-    extracted, defaults to 10
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{Optional}{[}\texttt{dict}{]}
-\end{itemize}
-
-\hypertarget{classmethod-make_metricsfile_path-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10-departmentnone}{%
-\subsubsection{classmethod make\_metrics(file\_path, project\_id,
-abstract=False, fulltext=False, limit=None, threshold=None, n=10,
-department=None)}\label{classmethod-make_metricsfile_path-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10-departmentnone}}
-
-Make Sklearn metrics F1, recall, precision for file.
-
-The output is saved as /metrics/metrics\_\{marker\}.json.
-
-Available Annif-client project IDs are yso-en, yso-maui-en,
-yso-bonsai-en, yso-fasttext-en, wikidata-en.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{project\_id} (\texttt{str}) -- Annif-client project ID
-  \item
-    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
-    indexing, defaults to False
-  \item
-    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
-    indexing, defaults to False
-  \item
-    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
-    limit, defaults to None
-  \item
-    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
-    Annif-client threshold, defaults to None
-  \item
-    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
-    extracted per item, defaults to 10
-  \item
-    \textbf{department} (\texttt{Optional}{[}\texttt{str}{]}) --
-    restrict to items from department
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-make_random_samplefile_path-save_path-size}{%
-\subsubsection{classmethod make\_random\_sample(file\_path, save\_path,
-size)}\label{classmethod-make_random_samplefile_path-save_path-size}}
-
-Save a random sample from the population in the file.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
-    including filename and extension
-  \item
-    \textbf{size} (\texttt{int}) -- the sample size
-  \end{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-print_chi_square_fitfile_path}{%
-\subsubsection{classmethod
-print\_chi\_square\_fit(file\_path)}\label{classmethod-print_chi_square_fitfile_path}}
-
-Print chi square goodness of fit.
-
-File must be CSV with first line title; three columns with first column
-categories, second column expected and third column observed values.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \textbf{file\_path} (\texttt{str}) -- complete path to file including
-  filename and extension
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
-
-\hypertarget{classmethod-super_make_metricsfile_path-departmentnone}{%
-\subsubsection{classmethod super\_make\_metrics(file\_path,
-department=None)}\label{classmethod-super_make_metricsfile_path-departmentnone}}
-
-Make metrics for all combinations of Annif projects and parameters in
-enriched Edoc file.
-
-Output files are saved in /metrics/. Joint results are saved in
-/analysis/metrics.json.
-
-\begin{itemize}
-\item
-  \textbf{Parameters}
-
-  \begin{itemize}
-  \item
-    \textbf{file\_path} (\texttt{str}) -- complete path to file
-    including filename and extension
-  \item
-    \textbf{department} (\texttt{Optional}{[}\texttt{str}{]}) --
-    restrict to items from department
-  \end{itemize}
-\end{itemize}
-
-\hypertarget{classmethod-super_make_stats}{%
-\subsubsection{classmethod
-super\_make\_stats()}\label{classmethod-super_make_stats}}
-
-Make metrics for files in /metrics.
-
-Output is saved as /analysis/metrics.json.
-
-\begin{itemize}
-\item
-  \textbf{Return type}
-
-  \texttt{None}
-\end{itemize}
+As mentioned in \protect\hyperlink{introduction}{section
+``Introduction''}, all files, data, and code used in this project is
+available at https://github.com/MHindermann/mas.
 

### 2021-03-09 text/draft.tex
clean up text & docu

@@
 
-!! Say something to the effect that all data and code are available on
-GitHub.
-
-!! In this chapter, the prototype for a machine indexing of Edoc is
-presented. The focus is primarily on practical implementation although
-care is taken to spell out design decisions in as much detail as is
-needed.
-
-Let us start by stating the aim of the prototype. From a functional
-perspective, the prototype takes a subset of the data from Edoc as input
-and provides index terms for each item in this subset as output. In
-order to fulfill this aim we can distinguish a number of steps that need
-to be taken:
+The proof of the pudding is in the creation of a software prototype. The
+prototype must take a subset of the data from Edoc as input and provide
+index terms for each item in this subset as output. In order to fulfill
+this aim we can distinguish five steps corresponding to sections 2 to 6
+below:
 
@@
 \item
-  Understand the Edoc data.\\
-\item
-  Select and construct a sample data set.
-\item
-  Use Annif to index the items in the sample data set.
+  Understand the Edoc data.
+\item
+  Select and construct an Edoc sample data set.
+\item
+  Use Annif to index the items in the Edoc sample data set.
 \item
@@
 
-In the sections below, these steps will be discussed in detail.
+The focus of this project lies primarily on practical implementation of
+the prototype although care is taken to spell out design decisions in as
+much detail as is needed.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  fulltext support
-\item
-  mesh; A gold standard is usually the product of manual indexing by
-  ``information experts, subject experts, or potential or real end
+Answer some questions asked in the proposal. Briefly summarize results.
+Recommend using Out of the box annif for production. sketch
+implementation strategy.
+
+\hypertarget{further-research}{%
+\subsection{Further research}\label{further-research}}
+
+Apart from implementing a production system as discussed above, natural
+next steps to build on this project include:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  mesh. mesh; A gold standard is usually the product of manual indexing
+  by ``information experts, subject experts, or potential or real end
   users'' (Golub et al. 2016, 10). This entails its own host of
@@
   available in repositories distinct from Edoc; call this the
-  ``foreign'' gold standard. -We enrich the sample items with MeSH
+  ``foreign'' gold standard. / We enrich the sample items with MeSH
   keywords from PubMed if available (item needs a PubMed ID and items
@@
   DIR + ``/indexed/indexed\_master\_mesh'')
-\end{itemize}
-
-\hypertarget{further-research}{%
-\subsection{Further research}\label{further-research}}
-
-Apart from implementing a production system as discussed above, natural
-next steps to build on this project include:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  mesh
 \item
@@
 ``Introduction''}, all files, data, and code used in this project is
-available at https://github.com/MHindermann/mas.
+available at https://github.com/MHindermann/mas and will not be
+replicated here.
 

### 2021-03-09 files/__init__.py

@@ -1,5 +1,5 @@
 from __future__ import annotations
-from typing import List, Optional, Dict, Union, Tuple
+from typing import List, Dict, Union
 from json import load, dump
 import csv
 from datetime import datetime
@@ -447,7 +447,7 @@ class Keywords:
     def enrich_with_yso(cls,
                         file_path: str,
                         save_path: str):
-        """ Blah.
+        """ Enrich items in file with YSO IDs if available.
 
         :param file_path: complete path to file including filename and extension
         :param save_path: complete path to save folder including filename without extension

### 2021-03-09 files/__init__.py
html docu test

@@ -633,10 +633,6 @@ class Analysis:
 
         Available Annif-client project IDs are yso-en, yso-maui-en, yso-bonsai-en, yso-fasttext-en, wikidata-en.
 
-        https://scikit-learn.org/stable/modules/generated/sklearn.metrics.f1_score.html
-        https://scikit-learn.org/stable/modules/generated/sklearn.metrics.recall_score.html
-        https://scikit-learn.org/stable/modules/generated/sklearn.metrics.precision_score.html
-
         :param file_path: complete path to file including filename and extension
         :param project_id: Annif-client project ID
         :param abstract: toggle use abstract for indexing, defaults to False

### 2021-03-09 text/draft.tex
docu

@@
 the prototype although care is taken to spell out design decisions in as
-much detail as is needed.
+much detail as is needed. All code written and data generated during the
+process of implementing the prototype is available at
+\url{https://github.com/MHindermann/mas}:
+
+\begin{itemize}
+\tightlist
+\item
+  Text and images available at
+  \href{https://github.com/MHindermann/mas/tree/main/text}{\texttt{/text/}}
+\item
+  Codebase and data available at
+  \href{https://github.com/MHindermann/mas/tree/main/files}{\texttt{/files/}}
+\item
+  Documentation available at
+  \href{https://github.com/MHindermann/mas/tree/main/docs}{\texttt{/docs/}}
+\end{itemize}
 
@@
 less containing 5000 or fewer entries each. These files are called
-\texttt{raw\_master\_\{year\}.json} and saved under \texttt{/raw}.
+\texttt{raw\_master\_\{year\}.json} and saved under
+\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}.
 
@@
 is first uploaded to the University of Basel's research database
-(https://www.forschdb2.unibas.ch) before being automatically fed into
-Edoc. There are explicit rules on how to enter the data as summarized in
-the user manual (Universität Basel, n.d.). However, there is no (or at
-least no systematic) manual or automatic validation of the entered data.
-This means that some data fields are very heterogenous and require
-further parsing (see \protect\hyperlink{gold-standard}{section ``Gold
-standard''}). The data fields that are of interest to the project at
-hand are discussed in more detail in (see
+\url{https://www.forschdb2.unibas.ch} before being automatically fed
+into Edoc. There are explicit rules on how to enter the data as
+summarized in the user manual (Universität Basel, n.d.). However, there
+is no (or at least no systematic) manual or automatic validation of the
+entered data. This means that some data fields are very heterogenous and
+require further parsing (see \protect\hyperlink{gold-standard}{section
+``Gold standard''}). The data fields that are of interest to the project
+at hand are discussed in more detail in (see
 \protect\hyperlink{sample-data-set}{section ``Sample data set''} below).
@@
 example, consider the item
-\texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
-``Blacking Out.'' Without further context, this title could refer
-(amongst others) to a physiological phenomenon, a sudden loss of
-electricity, or a measure taken in wartime. Knowing that the item was
-published by a researcher employed by the Faculty of Business and
-Economics (and not, say, by the Faculty of Medicine) gives us reason to
-exclude the first meaning. However, this idea cannot be implemented with
-the out of the box instance of Annif employed in this chapter (see
+\href{https://edoc.unibas.ch/id/eprint/76510}{\texttt{https://edoc.unibas.ch/id/eprint/76510}}
+which is titled ``Blacking Out.'' Without further context, this title
+could refer (amongst others) to a physiological phenomenon, a sudden
+loss of electricity, or a measure taken in wartime. Knowing that the
+item was published by a researcher employed by the Faculty of Business
+and Economics (and not, say, by the Faculty of Medicine) gives us reason
+to exclude the first meaning. However, this idea cannot be implemented
+with the out of the box instance of Annif employed in this chapter (see
 \protect\hyperlink{machine-indexing}{section ``Machine indexing''}).
@@
 skilled in a certain academic domain, must assign and/or approve each
-item's index terms (!!source). For this reason we try to avoid having to
-produce a standard. One way of doing so is by requiring items in the
-sample data set to have non-empty \texttt{keywords} data field. The
-caveats of this approach are discussed in
-\protect\hyperlink{assessment}{section ``Assessment''}.
+item's index terms. For this reason we try to avoid having to produce a
+standard. One way of doing so is by requiring items in the sample data
+set to have non-empty \texttt{keywords} data field. The caveats of this
+approach are discussed in \protect\hyperlink{assessment}{section
+``Assessment''}.
 
@@
 employ any further restrictions. We can hence construct the sample data
-set by choosing exactly those items from \texttt{/raw} which have
-non-empty data fields \texttt{title}, \texttt{abstract},
+set by choosing exactly those items from
+\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}
+which have non-empty data fields \texttt{title}, \texttt{abstract},
 \texttt{id\_number}, and \texttt{keywords}. We do so by calling
 \texttt{Data.select\_from\_file} iteratively for all files in
-\texttt{/raw}. The resulting file is saved in \texttt{/selected} as
-\texttt{selected\_master.json}.
+\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}.
+The resulting file is saved in
+\href{https://github.com/MHindermann/mas/tree/main/files/sample}{\texttt{/sample/}}
+as \texttt{sample\_master.json}.
 
@@
 
-Of the 68'345 items in \texttt{/raw}, all have a title (non-empty
-\texttt{title} data field), a little more than half of the items have an
-abstract (37'381 items with non-empty \texttt{abstract} data field),
-roughly half of the items have an ID (35'355 items with non-empty
-\texttt{id\_number} data field),\footnote{Note that when using the facet
-  by blank on \texttt{id\_number} in OpenRefine, there are 57'153
-  matches; this is due to the fact that many items with an ID such as
-  DOI have secondary or tertiary IDs such as ISI or PMID.} and less than
-10\% of the items have keywords (6'660 items with non-empty
-\texttt{keywords} data field). The sample data set as requires all the
-above data fields to be non-empty; \texttt{/sample/sample\_master.json}
-has 4'111 items and hence constitutes 6\% of the raw data.
+Of the 68'345 items in
+\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}},
+all have a title (non-empty \texttt{title} data field), a little more
+than half of the items have an abstract (37'381 items with non-empty
+\texttt{abstract} data field), roughly half of the items have an ID
+(35'355 items with non-empty \texttt{id\_number} data field),\footnote{Note
+  that when using the facet by blank on \texttt{id\_number} in
+  OpenRefine, there are 57'153 matches; this is due to the fact that
+  many items with an ID such as DOI have secondary or tertiary IDs such
+  as ISI or PMID.} and less than 10\% of the items have keywords (6'660
+items with non-empty \texttt{keywords} data field). The sample data set
+as requires all the above data fields to be non-empty;
+\texttt{/sample/sample\_master.json} has 4'111 items and hence
+constitutes 6\% of the raw data.
 
@@
 that instead of training a local Annif instance, I will be relying on
-the Annif REST-style API (see https://api.annif.org/).\footnote{This API
-  is specifically intended for testing. For integration into a
+the Annif REST-style API (see \url{https://api.annif.org/}).\footnote{This
+  API is specifically intended for testing. For integration into a
   production system, the Finto AI API is available (see
-  https://ai.finto.fi/v1/ui/).} The advantage of this approach is that
-it is quick and relatively easy to implement. The disadvantage is that
-no custom algorithms or vocabularies can be used. The task of
+  \url{https://ai.finto.fi/v1/ui/}).} The advantage of this approach is
+that it is quick and relatively easy to implement. The disadvantage is
+that no custom algorithms or vocabularies can be used. The task of
 constructing a gold standard (see
@@
 The vocabularies provided by the Annif API are the General Finnish
-Ontology or YSO in short (see https://finto.fi/yso/en/) and Wikidata
-(see https://www.wikidata.org/). Each vocabulary is combined with an
-algorithm or algorithm ensemble respectively and a specific language to
-create a so-called Annif ``project.'' The five projects used in what
-follows are summarized in Table 1. A high-level description of the
-algorithm(s) is given by Suominen (2019, 7--10). Information on
-implementation can be found at the Annif GitHub Wiki (see
-https://github.com/NatLibFi/Annif/wiki).
+Ontology or YSO in short (see \url{https://finto.fi/yso/en/}) and
+Wikidata (see \url{https://www.wikidata.org/}). Each vocabulary is
+combined with an algorithm or algorithm ensemble respectively and a
+specific language to create a so-called Annif ``project.'' The five
+projects used in what follows are summarized in Table 1. A high-level
+description of the algorithm(s) is given by Suominen (2019, 7--10).
+Information on implementation can be found at the Annif GitHub Wiki (see
+\url{https://github.com/NatLibFi/Annif/wiki}).
 
@@
 Machine indexing with Annif was implemented using the annif-client
-Python library (see https://pypi.org/project/annif-client/). The desired
-output is that every item in the Edoc sample data set is assigned
-subject terms by all available Annif API projects (namely,
+Python library (see \url{https://pypi.org/project/annif-client/}). The
+desired output is that every item in the Edoc sample data set is
+assigned subject terms by all available Annif API projects (namely,
 \texttt{yso-en}, \texttt{yso-maui-en}, \texttt{yso-bonsai-en},
@@
 \texttt{/sample/sample\_master.json} for all Annif projects. The output
-is saved in \texttt{/indexed/} as \texttt{indexed\_master.json}.
+is saved in
+\href{https://github.com/MHindermann/mas/tree/main/files/indexed}{\texttt{/indexed/}}
+as \texttt{indexed\_master.json}.
 
@@
 YSO. This process is called ``reconciliation'' (see
-https://docs.openrefine.org/manual/reconciling) and the tool of choice
-for this task is OpenRefine).\footnote{For data refinement I use
-  OpenRefine version 3.4.1 (https://openrefine.org/). Data manipulation
-  in OpenRefine is tracked: the manipulation history of some data can be
-  exported as JSON file and then reproduced (on the same data on a
-  different machine or on different data) by loading said file. I will
-  supply a corresponding manipulation history whenever appropriate. Note
-  that when using OpenRefine with larger files (and there are many such
-  files in this project), the memory allocation to OpenRefine must be
-  manually increased (see
-  https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation
+\url{https://docs.openrefine.org/manual/reconciling}) and the tool of
+choice for this task is OpenRefine).\footnote{For data refinement I use
+  OpenRefine version 3.4.1 (see \url{https://openrefine.org/}). Data
+  manipulation in OpenRefine is tracked: the manipulation history of
+  some data can be exported as JSON file and then reproduced (on the
+  same data on a different machine or on different data) by loading said
+  file. I will supply a corresponding manipulation history whenever
+  appropriate. Note that when using OpenRefine with larger files (and
+  there are many such files in this project), the memory allocation to
+  OpenRefine must be manually increased (see
+  \url{https://docs.openrefine.org/manual/installing/\#increasing-memory-allocation}
   for details). Also note that OpenRefine always counts the number of
@@
 scholarly article is suggested with high confidence (see
-https://github.com/OpenRefine/OpenRefine/wiki/Reconciliation-Service-API
+\url{https://github.com/OpenRefine/OpenRefine/wiki/Reconciliation-Service-API}
 for details). To generalize, suggestions with types whose concepts are
@@
 provides a REST-style API to access the YSO vocabulary directly (see
-https://api.finto.fi/). For each keyword in the list of reference
+\url{https://api.finto.fi/}). For each keyword in the list of reference
 keywords that lacks a YSO identifier, the Finto API is queried; if a
@@
 and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
-(such as indexing consistency, transparency, reproducability) that are
+(such as indexing consistency, transparency, reproducibility) that are
 neglected here.
@@
 the Edoc sample data set might be less representative of the item's
-content than its title. In that case, the observed worse perfomance of
+content than its title. In that case, the observed worse performance of
 the Annif configurations based on title and abstracts would even be
@@
 ``Introduction''}, all files, data, and code used in this project is
-available at https://github.com/MHindermann/mas and will not be
+available at \url{https://github.com/MHindermann/mas} and will not be
 replicated here.

### 2021-03-09 text/draft.tex
update conclusion

@@
 Edoc is the institutional repository of the University of Basel. It runs
-on the EPrints 3 document management system
-(https://github.com/eprints/eprints). Edoc was conceived in 2009 as
+on the EPrints 3 document management system (see
+\url{https://github.com/eprints/eprints}). Edoc was conceived in 2009 as
 repository for electronic dissertations and grew in scope when the
-University of Basel adapted its first open access policy in 2013. Today
-Edoc contains roughly 68'000 items, most of them journal articles
-without full text support. Even though descriptive and administrative
-metadata are collected for each item, this does not include subject
-terms. The lack of subject indexing hampers the repository's usability
-and potential with respect to the topic-based monitoring of research
-output and, to a lesser extent, information retrieval. The goal of this
-project is to remedy this situation with the help of machine indexing.
-
-!! More precisely, this project aims to provide a roadmap for indexing
-the elements of Edoc with Annif (Suominen, 2018) -- an open source tool
-for automated subject indexing and classification -- and BARTOC FAST
-(Hindermann and Ledl, 2020), a federated asynchronous search tool that
-covers concepts of thousands of knowledge organization systems like
-thesauri, classifications etc.
-
-!! The goal of this thesis is to investigate to what extent machine
-indexing can be used to ameliorate institutional repositories.
+University of Basel adapted its first open access policy in 2013. In
+early 2021, Edoc contained roughly 68'000 items, most of them journal
+articles without full text support. Even though descriptive and
+administrative metadata are collected for each item, this does not
+include subject terms. The lack of subject indexing hampers the
+repository's usability and potential with respect to the topic-based
+monitoring of research output and, to a lesser extent, information
+retrieval. The goal of this project is to remedy this situation with the
+help of machine indexing.
 
@@
 process of implementing the prototype is available at
-\url{https://github.com/MHindermann/mas}:
+\url{https://github.com/MHindermann/mas} and comes in three categories:
 
@@
 per item are counted. To do so, we call \texttt{Keywords.make\_count} on
-\texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
-output as \texttt{/analysis/keywords\_counted.json}:
+\texttt{/indexed/indexed\_master.json} and save the output as
+\texttt{/analysis/keywords\_counted.json}:
 
@@
 
-In \protect\hyperlink{general-results}{section ``General results''} I
+In \protect\hyperlink{general-results}{subsection ``General results''} I
 have identified and discussed the overall best Annif configerations.
-However, in \protect\hyperlink{analysis}{section ``Analysis''}, I had
-noted the caveat that the performance of Annif might vary according to
-department due to systematic biases in constructing the Edoc sample data
-set. In this section I will therefore assess the performance of the
-various Annif configurations per department.
+However, in \protect\hyperlink{sample-data-set}{section ``Sample data
+set''}, I had noted the caveat that the performance of Annif might vary
+according to department due to systematic biases in constructing the
+Edoc sample data set. In this section I will therefore assess the
+performance of the various Annif configurations per department.
 
@@
 
-\hypertarget{recommendation}{%
-\subsection{Recommendation}\label{recommendation}}
-
-Answer some questions asked in the proposal. Briefly summarize results.
-Recommend using Out of the box annif for production. sketch
+!! improve data collection of keywords
+
+!! Answer some questions asked in the proposal. Briefly summarize
+results. Recommend using Out of the box annif for production. sketch
 implementation strategy.
-
-\hypertarget{further-research}{%
-\subsection{Further research}\label{further-research}}
 
@@
 \item
-  mesh. mesh; A gold standard is usually the product of manual indexing
-  by ``information experts, subject experts, or potential or real end
-  users'' (Golub et al. 2016, 10). This entails its own host of
-  epistemic problems relating to objectivity and consistency of the
-  assigned subject terms. Most importantly, however, the construction of
-  a gold standard from scratch is very expensive. It is therefore not an
-  option for the project at hand. Rather, I will construct what could be
-  called derivative gold standards by reusing indexing data that is
-  already available. Here we can distinguish two distinct kinds of
-  derivative gold standards: first, I will construct a derivative gold
-  standard based on the author keywords available in the sample data
-  set; call this the ``derivative'' gold standard. Second, I will
-  construct a derivative gold standard based on indexing metadata
-  available in repositories distinct from Edoc; call this the
-  ``foreign'' gold standard. / We enrich the sample items with MeSH
-  keywords from PubMed if available (item needs a PubMed ID and items
-  needs to be indexed with MeSH on PubMed, 1653 items match this
-  requirement); the resulting file is indexed\_master\_mesh.json. Like
-  so: Data.enrich\_with\_mesh(DIR + ``/indexed/indexed\_master.json,''
-  DIR + ``/indexed/indexed\_master\_mesh'')
-\item
-  full text
-\item
-  german vocabulary
-\item
-  select domain specific vocabularies with bartoc suggest
+  In response to the result that increasing the text basis to titles and
+  abstracts does not increase performance discussed in
+  \protect\hyperlink{assessment}{section ``Assessment''}, add full text
+  support and evaluate the performance by increasing the text basis even
+  further. To do this, \texttt{Data.enrich\_with\_annif} must be amended
+  to fetch and parse the full text PDFs. For an item in the sample data
+  set, the link to the full text is constructed from the data fields
+  \texttt{offical\ url} and \texttt{documents\ -\ main}. Initial tests
+  using the Tika Python library for parsing were promising.
+\item
+  Originally I had intended to undertake an additional performance test
+  based on a gold standard distinct from the derivative gold standard
+  constructed in \protect\hyperlink{gold-standard}{section ``Gold
+  standard''}. In order to do so, items in the Edoc sample data set were
+  enriched with MeSH terms (see
+  \url{https://www.nlm.nih.gov/mesh/meshhome.html}) retrieved from
+  PubMed (if they had a PubMed ID). This was achieved by calling
+  \texttt{Data.enrich\_with\_mesh} on
+  \texttt{/indexed/indexed\_master.json}. However, the Annif API does
+  not include a configuration with a MeSH vocabulary, and there is no
+  concordance between MeSH and either Wikidata or YSO (see
+  \url{https://coli-conc.gbv.de/cocoda/app/concordances.html}).
+  Therefore, the MeSH terms obtained from PubMed would have to be
+  reconciled with Wikidata and YSO in a very time-consuming manner,
+  yielding again only a derivative gold standard. As a way forward, it
+  would be more effective to train a local instance of Annif on the
+  already obtained MeSh data.
+\item
+  As shown in \protect\hyperlink{assessment}{section ``Assessment''},
+  the performance of Annif configurations varies with department. It is
+  hence plausible that some (subsets of) items in Edoc require
+  domain-specific vocabularies that are not available in Annif. These
+  vocabularies can be identified using BARTOC FAST (Hindermann and Ledl
+  2020); the implementation is straightforward with my bartocsuggest
+  Python library that already includes an Annif wrapper (see
+  \url{https://pypi.org/project/bartocsuggest/}).
+\item
+  An issue that has been neglected in this project is the fact that Edoc
+  is a multilingual repository containing more than 3'324 items in
+  German (roughly 5\% of Edoc) and 273 items in other languages (less
+  than 0.5\% of Edoc).\footnote{The Edoc sample data set only contains
+    53 non-English (inclduding 48 German) items; the negligence is hence
+    well justified.} Here it would be interesting to train a local
+  instance of Annif with GND similar in spirit to Nagelschmidt
+  (12.11.2020) and compare its perfomance to other machine indexing
+  tools such as DA-3 (Beckmann et al. 2019) which are currently
+  informally evaluated at the University Library Basel.
 \end{enumerate}
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Beckmann.2019}{}%
+Beckmann, Regine, Imma Hinrichs, Melanie Janßen, Gérard Milmeister, and
+Peter Schäuble. 2019. {``Digitale Assistent DA-3.''} \emph{O-Bib. Das
+Offene Bibliotheksjournal} 6 (3): 1--20.
+\url{https://doi.org/10.5282/O-BIB/2019H3S1-20}.
+
 \leavevmode\hypertarget{ref-Gantert.2016}{}%
@@
 
+\leavevmode\hypertarget{ref-Hindermann.2020}{}%
+Hindermann, Maximilian, and Andreas Ledl. 2020. {``BARTOC FAST: A
+Federated Asynchronous Search Tool for Remote Vocabulary Access.''} In
+\emph{Knowledge Organization at the Interface}, edited by Marianne
+Lykke, Tanja Svarre, Mette Skov, Daniel Martínez-Ávila, and
+International Society for Knowledge Organziation International Society
+for Knowledge Organziation, 200--206. Advances in Knowledge
+Organization. Baden-Baden: {Ergon -- ein Verlag in der Nomos
+Verlagsgesellschaft}. \url{https://doi.org/10.5771/9783956507762-200}.
+
 \leavevmode\hypertarget{ref-Louis.2013}{}%

### 2021-03-12 text/text.tex
refactor latex

--- 2021-03-09 text/draft.tex
@@
 second, \texttt{1942-2020.json} is too big to be handled by standard
-editors requiring special editors such as Oxygen. For these reasons
+editors requiring special editors. For these reasons
 \texttt{1942-2020.json} was split into smaller files that are easier
@@
 descriptive metadata is undertaken by the person who uploads the item
-which is in most cases one of the item's authors. The Note that an item
-is first uploaded to the University of Basel's research database
+which is (in most cases) one of the item's authors. Note that an item is
+first uploaded to the University of Basel's research database
 \url{https://www.forschdb2.unibas.ch} before being automatically fed
@@
 There are a number of constraints for selecting the sample data set
-pertaining to an items's text, evaluability and the data set's scope.
+pertaining to an items's text, evaluability, and the data set's scope.
 
 The first constraint stems from Annif, the machine indexing framework
-that will be used. Put simply, machine indexing assigns index terms to a
-text based on training data. The training data consists of a set of
-texts, a vocabulary, and function from vocabulary to texts. In this
-context we mean by ``text'' a sequence of words in a natural language
-and by ``vocabulary'' a set of words. Intuitively, the training data
-consists of pairs of text and subject terms that meet some standard. The
-training data and the vocabulary are already supplied by Annif, we only
-need to provide a text for each item that we want to be assigned index
-terms. Therefore, we only select items with text.
+that will be used (see \protect\hyperlink{machine-indexing}{section
+``Machine indexing''} for more details). Put simply, machine indexing
+assigns index terms to a text based on training data. The training data
+consists of a set of texts, a vocabulary, and function from vocabulary
+to texts. In this context we mean by ``text'' a sequence of words in a
+natural language and by ``vocabulary'' a set of words. Intuitively, the
+training data consists of pairs of text and subject terms that meet some
+standard. The training data and the vocabulary are already supplied by
+Annif, we only need to provide a text for each item that we want to be
+assigned index terms. Therefore, we only select items with text.
 
@@
 Taking into account the third constraint simply means that we do not
-employ any further restrictions. We can hence construct the sample data
-set by choosing exactly those items from
+employ any further restrictions. We can hence construct the Edoc sample
+data set by choosing exactly those items from
 \href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}
@@
   as ISI or PMID.} and less than 10\% of the items have keywords (6'660
-items with non-empty \texttt{keywords} data field). The sample data set
-as requires all the above data fields to be non-empty;
+items with non-empty \texttt{keywords} data field). The Edoc sample data
+set as requires all the above data fields to be non-empty;
 \texttt{/sample/sample\_master.json} has 4'111 items and hence
@@
 indexing is currently evaluated at different libraries, for example at
-the German National Library (Nagelschmidt 12.11.2020). As stated in
+the German National Library (see Nagelschmidt 12.11.2020). As stated in
 section \protect\hyperlink{introduction}{section ``Introduction''}, in
@@
 description of the algorithm(s) is given by Suominen (2019, 7--10).
-Information on implementation can be found at the Annif GitHub Wiki (see
+Information on the implementation of the algorithm(s) can be found at
+the Annif GitHub Wiki (see
 \url{https://github.com/NatLibFi/Annif/wiki}).
@@
 In this section I will construct a derivative gold standard in order to
-assess the quality of machine indexing the sample data set with Annif.
+assess the quality of machine indexing the Edoc sample data set with
+Annif.
 
@@
 
-In a first step, the keywords must be extracted from the sample data set
-\texttt{/sample/sample\_master.json}. Recall that we mandated a
+In a first step, the keywords must be extracted from the Edoc sample
+data set \texttt{/sample/sample\_master.json}. Recall that we mandated a
 non-empty \texttt{keywords} data field for an item to be selected from
@@
 
-In second step, a list of all single keywords must be created. In order
-to do so, let us consider now in more detail the exact information
+In a second step, a list of all single keywords must be created. In
+order to do so, let us consider now in more detail the exact information
 extracted from the \texttt{keywords} data fields as per
@@
 be broken into their component keywords and then parsed again. The
-reason for this is that Annif only assigns flat keywords and not keyword
-chains.
+reason for this is that Annif only assigns flat (i.e., non-hierarchical)
+keywords and not keyword chains.
 
@@
 of view: when it comes to subject indexing, some terms are required, but
-more is usually worse. Items with too few or too many keywords will be
-discussed in more detail in section
+more is usually not better but worse. Items with too few or too many
+keywords will be discussed in more detail in section
 \protect\hyperlink{assessment}{section ``Assessment''}
@@
 \texttt{/keywords/keywords\_reference.json} and saving the output as
-\texttt{/keywords/keywords\_reference\_master.json}
+\texttt{/keywords/keywords\_reference\_master.json} like so:
 
@@
 adequate. This problem can be amended by imposing further constraints on
-the sample data set and such a solution is discussed in section {[}!!
-section{]}.
+the Edoc sample data set and such a solution is discussed in
+\protect\hyperlink{conclusion-and-outlook}{section ``Conclusion and
+outlook''}.
 
@@
 Precision and recall are standard metrics for indexing quality (e.g.,
-Gantert 2016, 197) whereby the F1 score plays are more prominent role in
+Gantert 2016, 197) whereby the F1-score plays are more prominent role in
 the assessment of machine indexing (e.g., Suominen 2019, 11--14; Toepfer
@@
 
-The above scoring metrics were implemented using the scikit-learn
+The above scoring metrics were implemented using the scikit-learn Python
 machine learning library (Pedregosa et al. 2011).
@@
   The maximum number of suggestions per item. Since we required 10
-  suggestions per item, we can choose between 1-10 suggestions.
+  suggestions per item, we can choose between 1 to 10 suggestions.
 \end{enumerate}
@@
 \caption{Distribution of weighted F1-scores per class of project of
-Annif configuration (left) and per class of text basis of Annif
-configuration (right). \texttt{wikidata} (min = 0.239, Q1 = 0.355, M =
-0.415, Q3 = 0.492, max = 0.517) outperforms any YSO configuration.
+Annif configuration (left), and per class of text basis of Annif
+configuration (right). \texttt{wikidata-en} (min = 0.239, Q1 = 0.355, M
+= 0.415, Q3 = 0.492, max = 0.517) outperforms any YSO configuration.
 \texttt{yso-bonsai-en}, \texttt{yso-en} and \texttt{yso-fasttext-en} are
@@
 configuration with a weighted F1-score of 0.517 is \texttt{wikidata-en}
-with a maximum number of 4 suggestions per item; the text basis (title
+with a maximum number of 4 suggestions per item; its text basis (title
 or abstract and title) does not matter.
@@
 Let us now look at the results. First consider the distribution of the
-performance scores across departments as shown in Figure 11. We can see
+performance scores across departments as shown in Figure 10. We can see
 that there are striking differences in variability between departments.
@@
 Let us now consider the best performing Annif configurations per
-department as summarized in Figure 12. It is evident that only two of
+department as summarized in Figure 11. It is evident that only two of
 the ten departments (namely Associated and Central Services) have as
@@
 
-In this section, ..
+The main take home from this project is that the out of the box Annif
+API is suitable to index an institutional repository such as Edoc.
 

### 2021-03-12 text/text.tex
add conclusion

@@
 \texttt{Keywords.extract\_keywords} with the sample data set as argument
-and save the output as \texttt{keywords/keywords\_extracted.json} like
+and save the output as \texttt{/keywords/keywords\_extracted.json} like
 so:
@@
 \NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ Keywords.clean\_keywords(keywords\_extracted)}
-\NormalTok{Utility.save\_json(keywords\_clean, }\StringTok{"keywords/keywords\_clean.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords\_clean, }\StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ Keywords.make\_histogram(keywords\_clean)}
-\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"/keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
 \end{Highlighting}
@@
 \includegraphics{images/keywords_clean_histogram_abc.pdf}
-\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
+\caption{In \texttt{/keywords/keywords\_clean\_histogram.json}, the
 distribution of keywords is strongly skewed right (min = Q1 = M = Q3 =
@@
 \NormalTok{keywords\_reference\_new }\OperatorTok{=}\NormalTok{ Keywords.enrich\_with\_yso(keywords\_reference)}
-\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"keywords/keywords\_reference\_master.json"}\NormalTok{)}
+\NormalTok{Utility.save\_json(keywords\_histogram, }\StringTok{"/keywords/keywords\_reference\_master.json"}\NormalTok{)}
 \end{Highlighting}
@@
 In this section I will assess the quality of the sample data set's
-indexing by Annif based on the gold standard.
+indexing by Annif based on the derivative gold standard.
 
@@
 The main take home from this project is that the out of the box Annif
-API is suitable to index an institutional repository such as Edoc.
-
-!! improve data collection of keywords
-
-!! Answer some questions asked in the proposal. Briefly summarize
-results. Recommend using Out of the box annif for production. sketch
-implementation strategy.
+API is suitable to index an institutional repository such as Edoc. This
+is based on the performance of the Annif API in indexing the Edoc sample
+data set measured against the derivative gold standard constructed from
+cleaned and reconciled Edoc author keywords. With the prototype in
+place, the next step now concerns the implementation of a production
+system. The function \texttt{Data.enrich\_with\_annif} can of course be
+called to index all Edoc data available at \texttt{/raw/}. It would also
+be relatively straightforward to implement indexing with Annif for items
+newly added to Edoc respectively the University of Basel's research
+database. An alternative and perhaps more sustainable approach would be
+to improve the data quality by amending the process and requirements for
+data entry. Generally speaking, authors should be required to choose
+index terms from a controlled vocabulary or from a set of controlled
+vocabularies, and the entered data should be automatically validated.
+One way to implement this would be via the Skosmos recommendations
+feature of the BARTOC Skomos instance (see Waeber and Ledl 2019).
 
 Apart from implementing a production system as discussed above, natural
-next steps to build on this project include:
+next steps to improve upon this project include:
 
@@
 
+Finally, I had initially {[}monitoring,,,{]}.
+
 \hypertarget{appendix}{%
@@
 
+\leavevmode\hypertarget{ref-Waeber.2019}{}%
+Waeber, Jonas, and Andreas Ledl. 2019. {``A Semantic Web SKOS Vocabulary
+Service for Open Knowledge Organization Systems.''} In \emph{Metadata
+and Semantic Research}, edited by Emmanouel Garoufallou, Fabio Sartori,
+Rania Siatri, and Marios Zervas, 846:3--12. Communications in Computer
+and Information Science, 1865-0929. Cham, Switzerland: Springer.
+\url{https://doi.org/10.1007/978-3-030-14401-2\%7B/textunderscore\%20\%7D1}.
+
 \end{CSLReferences}

### 2021-03-12 text/titlepage/titlepage.tex
add conclusion

@@
 	\textbf{\LARGE Machine indexing of institutional repositories: indexing Edoc with Annif as proof of concept}\\[2cm]
-	\orcidicon{0000-0002-9337-4655} Dr.\ Maximilian G.\ Hindermann\\
+	Dr.\ Maximilian G.\ Hindermann \orcidicon{0000-0002-9337-4655}\\
 	Spalentorweg 46, CH-4051 Basel\\
@@
 	\flushleft
-	\orcidicon{0000-0003-1952-1933} Silke Bellanger, Referentin\\[.25cm]
-	\orcidicon{0000-0002-0629-0446} Dr.\ Andreas Ledl, Ko-Referent\\
+	Silke Bellanger, Referentin \orcidicon{0000-0003-1952-1933}\\[.25cm]
+	Dr.\ Andreas Ledl, Ko-Referent \orcidicon{0000-0002-0629-0446}\\
 	%Prof.\ Marco J.\ Nathan\\[.25cm]

### 2021-03-15 text/abstract/abstract.tex
tex structure
update conclusion
add conclusion
add abstract

@@
 
-bla bla bla
+The potential of some institutional repositories is hampered by the lack of subject indexing.
+I argue that this situation can be amended with the help of machine indexing.
+As proof of concept I show that Edoc --- the University of Basel's repository --- can be successfully indexed using the Annif-client Python library.
+In order to do so, I assess the performance of hundreds of Annif configurations in assigning subject terms to a sample data set against a gold standard constructed from cleaned and reconciled author keywords.
+
+\newpage
+
+\emph{"Never spend 6 minutes doing something by hand when you can spend 6 hours failing to automate it."}
+
+Zhuowei Zhang

### 2021-03-18 text/text.tex
add abstract
fix typos

@@
 first uploaded to the University of Basel's research database
-\url{https://www.forschdb2.unibas.ch} before being automatically fed
+(\url{https://www.forschdb2.unibas.ch}) before being automatically fed
 into Edoc. There are explicit rules on how to enter the data as
@@
 ``Gold standard''}). The data fields that are of interest to the project
-at hand are discussed in more detail in (see
-\protect\hyperlink{sample-data-set}{section ``Sample data set''} below).
+at hand are discussed in more detail in
+\protect\hyperlink{sample-data-set}{section ``Sample data set''} below.
 
@@
 
-In this section, I will explain how the sample data set is selected and
+In this section, I will explain how the sample data set was selected and
 constructed. ``Selection'' hereby means the task of specifying a subset
@@
 \texttt{Data.select\_from\_file} iteratively for all files in
-\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}.
-The resulting file is saved in
+\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}
+using the aforementioned data fields as parameters. The resulting file
+is saved in
 \href{https://github.com/MHindermann/mas/tree/main/files/sample}{\texttt{/sample/}}
@@
 items with non-empty \texttt{keywords} data field). The Edoc sample data
-set as requires all the above data fields to be non-empty;
+set requires all the above data fields to be non-empty;
 \texttt{/sample/sample\_master.json} has 4'111 items and hence
@@
 the German National Library (see Nagelschmidt 12.11.2020). As stated in
-section \protect\hyperlink{introduction}{section ``Introduction''}, in
-this project I am interested in using Annif out of the box. This means
-that instead of training a local Annif instance, I will be relying on
-the Annif REST-style API (see \url{https://api.annif.org/}).\footnote{This
+\protect\hyperlink{introduction}{section ``Introduction''}, in this
+project I am interested in using Annif out of the box. This means that
+instead of training a local Annif instance, I will be relying on the
+Annif REST-style API (see \url{https://api.annif.org/}).\footnote{This
   API is specifically intended for testing. For integration into a
@@
 projects used in what follows are summarized in Table 1. A high-level
-description of the algorithm(s) is given by Suominen (2019, 7--10).
-Information on the implementation of the algorithm(s) can be found at
+description of the algorithm(s) is given by Suominen (2019, 7--10);
+information on the implementation of the algorithm(s) can be found at
 the Annif GitHub Wiki (see
@@
 As explained in \protect\hyperlink{machine-indexing}{section ``Machine
-indexing''}, Annif assigns index terms from a controlled vocabulary. If
-we want to assess the quality of the indexing via a gold standard, we
+indexing''}, Annif assigns subject terms from a controlled vocabulary.
+If we want to assess the quality of the indexing via a gold standard, we
 must therefore ensure that the gold standard makes use of the vocabulary
@@
 Second, systematic biases were identified and removed. The most
-prevalent bias was an due to a suggestion's type. As stated above, the
+prevalent bias was due to a suggestion's type. As stated above, the
 reconciliation service API was not constrained by type but had access to
@@
   would be more effective to train a local instance of Annif on the
-  already obtained MeSh data.
+  already obtained MeSH data.
 \item
@@
 
-Finally, I had initially {[}monitoring,,,{]}.
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-As mentioned in \protect\hyperlink{introduction}{section
-``Introduction''}, all files, data, and code used in this project is
-available at \url{https://github.com/MHindermann/mas} and will not be
-replicated here.
-
 \hypertarget{bibliography}{%
-\section{Bibliography}\label{bibliography}}
+\section*{Bibliography}\label{bibliography}}
+\addcontentsline{toc}{section}{Bibliography}
 
@@
 \end{CSLReferences}
+
+\hypertarget{appendix}{%
+	\section{Appendix}\label{appendix}}
+
+See \url{https://github.com/MHindermann/mas}.
